### 2014-07-16 docs/server_guide/build/latex/crds_server.tex
More work on CRDS Server guide.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@1559 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

% Generated by Sphinx.
\def\sphinxdocclass{report}
\documentclass[letterpaper,10pt,english]{sphinxmanual}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{\nobreakspace}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{times}
\usepackage[Bjarne]{fncychap}
\usepackage{longtable}
\usepackage{sphinx}
\usepackage{multirow}

\usepackage{enumitem}
\setlistdepth{15}

\usepackage{amsmath}
\DeclareUnicodeCharacter{00A0}{\nobreakspace}

% In the parameters section, place a newline after the Parameters
% header
\usepackage{expdlist}
\let\latexdescription=\description
\def\description{\latexdescription{}{} \breaklabel}

% Make Examples/etc section headers smaller and more compact
\makeatletter
\titleformat{\paragraph}{\normalsize\py@HeaderFamily}%
            {\py@TitleColor}{0em}{\py@TitleColor}{\py@NormalColor}
\titlespacing*{\paragraph}{0pt}{1ex}{0pt}

% Fix footer/header
\@ifundefined{chaptermark}{%
\newcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\thechapter.\ #1}}{}}
}{%
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\thechapter.\ #1}}{}}
}

\@ifundefined{chaptermark}{%
\newcommand{\sectionmark}[1]{\markright{\MakeUppercase{\thesection.\ #1}}}
}{%
\renewcommand{\sectionmark}[1]{\markright{\MakeUppercase{\thesection.\ #1}}}
}

\@ifundefined{TSR}{}{%
\renewcommand{\py@HeaderFamily}{\rmfamily\bfseries}
\definecolor{TitleColor}{rgb}{0,0,0}
\renewcommand{\appendix}{\par
  \setcounter{section}{0}%
  \inapptrue%
  \renewcommand\thesection{\@Alph\c@section}}
}

\makeatother

% Make the pages always arabic, and don't do any pages without page
% numbers
\pagenumbering{arabic}
\pagestyle{plain}

\title{CRDS Server Documentation}
\date{July 16, 2014}
\release{1.1}
\author{STScI}
\newcommand{\sphinxlogo}{\includegraphics{stsci_logo.pdf}\par}
\renewcommand{\releasename}{Release}
\makeindex

\makeatletter
\def\PYG@reset{\let\PYG@it=\relax \let\PYG@bf=\relax%
    \let\PYG@ul=\relax \let\PYG@tc=\relax%
    \let\PYG@bc=\relax \let\PYG@ff=\relax}
\def\PYG@tok#1{\csname PYG@tok@#1\endcsname}
\def\PYG@toks#1+{\ifx\relax#1\empty\else%
    \PYG@tok{#1}\expandafter\PYG@toks\fi}
\def\PYG@do#1{\PYG@bc{\PYG@tc{\PYG@ul{%
    \PYG@it{\PYG@bf{\PYG@ff{#1}}}}}}}
\def\PYG#1#2{\PYG@reset\PYG@toks#1+\relax+\PYG@do{#2}}

\def\PYG@tok@gd{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\def\PYG@tok@gu{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\def\PYG@tok@gt{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.25,0.82}{##1}}}
\def\PYG@tok@gs{\let\PYG@bf=\textbf}
\def\PYG@tok@gr{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\def\PYG@tok@cm{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@vg{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@m{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@mh{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@cs{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\colorbox[rgb]{1.00,0.94,0.94}{##1}}}
\def\PYG@tok@ge{\let\PYG@it=\textit}
\def\PYG@tok@vc{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@il{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@go{\def\PYG@tc##1{\textcolor[rgb]{0.19,0.19,0.19}{##1}}}
\def\PYG@tok@cp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@gi{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\def\PYG@tok@gh{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\def\PYG@tok@ni{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
\def\PYG@tok@nl{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
\def\PYG@tok@nn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\def\PYG@tok@no{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
\def\PYG@tok@na{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@nb{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@nc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\def\PYG@tok@nd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
\def\PYG@tok@ne{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@nf{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
\def\PYG@tok@si{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
\def\PYG@tok@s2{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@vi{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@nt{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
\def\PYG@tok@nv{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@s1{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@gp{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\def\PYG@tok@sh{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@ow{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@sx{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\def\PYG@tok@bp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@c1{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@kc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@c{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@mf{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@err{\def\PYG@bc##1{\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{##1}}}
\def\PYG@tok@kd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@ss{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
\def\PYG@tok@sr{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
\def\PYG@tok@mo{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@mi{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@kn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@o{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\def\PYG@tok@kr{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@s{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@kp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@w{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\def\PYG@tok@kt{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
\def\PYG@tok@sc{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@sb{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@k{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@se{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@sd{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}

\def\PYGZbs{\char`\\}
\def\PYGZus{\char`\_}
\def\PYGZob{\char`\{}
\def\PYGZcb{\char`\}}
\def\PYGZca{\char`\^}
\def\PYGZsh{\char`\#}
\def\PYGZpc{\char`\%}
\def\PYGZdl{\char`\$}
\def\PYGZti{\char`\~}
% for compatibility with earlier versions
\def\PYGZat{@}
\def\PYGZlb{[}
\def\PYGZrb{]}
\makeatother

\begin{document}

\maketitle
\tableofcontents
\phantomsection\label{index::doc}

\chapter{Introduction}
\label{server_guide:introduction}\label{server_guide::doc}\label{server_guide:crds-server-guide}
This guide is intended to introduce the CRDS servers for the purposes of maintenance and emergency backup for Todd.

Historical Institute contacts for the CRDS servers include:
\begin{itemize}
\item {} 
Todd Miller:    yours truly,  primary CRDS and (sole) CRDS server application developer.

\item {} 
Patrick Taylor: web proxies, ssl support, and server rc/reboot script coordination

\item {} 
Thomas Walker:  initial VM creation, file systems, and Isilon storage setup.

\end{itemize}

\chapter{Servers}
\label{server_guide:servers}

\section{CRDS pseudo-user and group}
\label{server_guide:crds-pseudo-user-and-group}
The CRDS servers run as the no-login user ``crds''.  The CRDS servers are maintained by getting sudo
access to the crds user and the equivalent of ``su crds'' from a normal user account.   The CRDS
crds\_server script contains the following:

\begin{Verbatim}[commandchars=\\\{\}]
ssh -A -t \$1.stsci.edu /usr/bin/sudo /bin/su - crds
\end{Verbatim}

and is invoked like this:

\begin{Verbatim}[commandchars=\\\{\}]
\% crds\_server plhstcrdsv1
\# crds\_server \textless{}VM-hostname\textgreater{}
\end{Verbatim}

The ssh first logs into your normal user account on the server VM, then su's you to CRDS.

Server maintainers need to get membership in group crdsoper and ``sudo su crds'' access on
the appropriate server VMs.

Members of DSB share the crdsoper group and use it to modify the CRDS server file delivery
directory described below.

\section{Virtual Machines and URLs}
\label{server_guide:virtual-machines-and-urls}
The CRDS servers exist on virtual machines,  run Apache servers and Django via mod\_wsgi,
are backed by memcached as a memory caching optimization for frequent traffic.  Currently
there are 6 VMs and servers:  (hst, jwst) x (dev, test, ops):

\begin{tabulary}{\linewidth}{|L|L|L|L|L|}
\hline
\textbf{
observatory
} & \textbf{
use
} & \textbf{
host/vm
} & \textbf{
direct port
} & \textbf{
url
}\\\hline

hst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\\hline

hst
 & 
dev
 & 
dlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
\\\hline

hst
 & 
test
 & 
tlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
\\\hline

hst
 & 
ops
 & 
plhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
\\\hline

jwst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\\hline

jwst
 & 
dev
 & 
dljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
\\\hline

jwst
 & 
test
 & 
tljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
\\\hline

jwst
 & 
ops
 & 
pljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
\\\hline
\end{tabulary}

For debug purposes the servers can be accessed by bypassing the proxy using VM-based URLs such
as \href{https://plhstcrdsv1.stsci.edu:8001/}{https://plhstcrdsv1.stsci.edu:8001/}.  These direct URLs are visible on site only.  Only the OPS
server URLs will be visible off site.

See CRDS\_server/sources/site\_config.py to verify this information.

\chapter{Server File Systems}
\label{server_guide:server-file-systems}

\section{/home/crds}
\label{server_guide:home-crds}
The VMs and servers share a common /home/crds directory which has potential as a single point failure.  In particular,
critical shell rc scripts (.setenv) are shared by all servers and must be updated with extreme care because
any error instantly affects all 6 servers.  Consequently, .setenv should be kept as simple as reasonably
possible.  /home/crds also houses rc\_script.

/home/crds is useful for communicating information between VMs during setup and maintenance.

\section{Server Static File Storage}
\label{server_guide:server-static-file-storage}
The CRDS server code and support files (Python stack, logs, monitor\_reprocessing dir) are stored on
a private VM-unique volume named after the host,  e.g.  /crds/data1.  This serves as the
./configure --prefix directory for a small number of packages not contained in the crds\_stack subdirectory.
Files within this directory tree are logically executable or in some way secret,  sensitive with respect
to server security.   Most files/subdirs are located in a subdirectory named after the host,
e.g. /crds/data1/plhstcrdsv1.

\subsection{Server Runtime Directories}
\label{server_guide:server-runtime-directories}
A number of subdirectories are used to store files related to running Apache, logging, or backups under
e.g. /crds/data1/dlhstcrdsv1/server.

\subsubsection{conf}
\label{server_guide:conf}
Apache config files are installed here at e.g. /crds/data1/dlhstcrdsv1/server/conf.  Files ssl.conf and httpd.conf.

\subsubsection{logs}
\label{server_guide:logs}
There are a number of Apache logs kept at e.g. /crds/data1/dlhstcrdsv1/server/logs.  These logs record requests to
Apache and stderr output from Django views not visible to end users.

\subsubsection{db\_backups}
\label{server_guide:db-backups}
The output of the CRDS\_server/tools/backup\_server script is kept here in dated subdirectories,
e.g. /crds/data1/dlhstcrdsv1/server/db\_backups/2014-05-30-033327.  These contain a backup of the CRDS server database,
catalog files, deliveries files, all mappings, the server CRDS cach config directory, and an VM rpm listing.
For use with restore\_server,  these files would need to be copied to differently named locations in \$HOME/backups
which only record the results of the last backup.

\subsubsection{wsgi-scripts}
\label{server_guide:wsgi-scripts}
The mod\_wsgi script which bridges from Apache to Django,  crds.wsgi,  is kept here,
e.g. /crds/data1/dlhstcrdsv1/server/wsgi-scripts.  Potentially other django or non-django WSGI scripts
would go here as well.

\subsubsection{run}
\label{server_guide:run}
The running Apache process id is stored here.   The id of memcached should be stored here as well but isn't.

\subsection{Database files}
\label{server_guide:database-files}
Files required to support operations with databases are stored in a top level static file system
subdirectory,  e.g. /crds/data1/database.   These files are secret,  effectively mode 700, and maintained
manually as part of database setup.  They're referred to by site-specific database configurations.

\subsection{CRDS}
\label{server_guide:crds}
The checkout of the CRDS core library source code installed with the CRDS server is located in the static file tree
under the subdirectory CRDS and visited using the alias ``crds''.  e.g.  /crds/data1/plhstcrdsv1/CRDS

\subsection{CRDS\_server}
\label{server_guide:crds-server}
The checkout of the CRDS server source code is located in the static file tree under the subdirectory CRDS\_server
and visited using the alias ``server''.  e.g. /crds/data1/plhstcrdsv1/CRDS\_server

\subsubsection{host}
\label{server_guide:host}
The CRDS\_server/host subdirectory is on the PATH.  It contains scripts related to cron jobs,  affected datasets
reprocessing, stack building,  server utilities, etc.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/host

\subsubsection{tools}
\label{server_guide:tools}
The CRDS\_server/tools directory contains more complicated scripts related to server backup, restore, mirroring,
consistency checking, server initialization, user and group maintenance, etc.   The tools directory is not on the
PATH and contains more eclectic scripts developed in an unplanned manner,  basically capturing whatever I needed
to do repeatedly or had to Google.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/tools

\subsubsection{servers}
\label{server_guide:id1}
This directory contains the Apache and mod\_wsgi configuration files.  e.g. /crds/data1/plhstcrdsv1/CRDS\_server/servers

\subsubsection{sources}
\label{server_guide:sources}
This directory contains the Django server and application source code.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/sources
\begin{itemize}
\item {} \begin{description}
\item[{\emph{sources/configs} contains site specific django configuration and database configuration files.  The appropriate files}] \leavevmode
are copied to sources/site\_config.py and sources/crds\_database.py at install time.   Those are then
imported into more generic configuration files sources/config.py and sources/settings.py.   The site
specific files are intended to contain the minimal information required to differentiate servers.

\end{description}

\item {} 
\emph{sources/urls.py}     defines most of the site URLs for all applications.

\item {} 
\emph{sources/settings.py} fairly standard Django settings.py

\item {} 
\emph{sources/templates}  contains web template base classes

\item {} 
\emph{sources/static}     contains most CRDS static files,  particularly Javascript and CSS.

\item {} 
\emph{sources/interactive}  is the primary web application for CRDS browsing and file submission.

\item {} 
\emph{sources/jsonapi}     is the JSONRPC application which supports web services in the crds.client api.

\item {} \begin{description}
\item[{\emph{sources/jpoll}    application supports the Javascript logging + done polling system used for long running views,}] \leavevmode
particularly file submissions which can exceed proxy timeouts and run too long to leave a human
without info.

\end{description}

\item {} 
\emph{sources/locking}     application for database based locks used by CRDS web logins for exclusive access to an instrument.

\item {} 
\emph{sources/fileupload}  application supports the fancy file submission file upload dialogs for file submissions.

\item {} \begin{description}
\item[{\emph{sources/stats}      application mostly defunct django-level request logging to database,  superceded by Apache}] \leavevmode
logging.  Some parameter capture not present in current Apache configuration.

\end{description}

\end{itemize}

\subsection{crds\_stacks}
\label{server_guide:crds-stacks}
The crds\_stacks subdirectory contains stock python stacks and source code.  The CRDS server Python stack is built
from source contained in the installer3 subdirectory.  An automatic nightly build and reinstall of the stack occurs on the
dev and test servers so it's possible to upgrade all the non-ops servers by updating the installer3 repo.  The
master copy of the CRDS server installer3 repo is contained in /eng/ssb/crds/installer3.   Independent checkouts
of the repo are contained in the stacks file store for each VM.   e.g. /crds/data1/plhstcrdsv1/crds\_stacks

\subsection{monitor\_reprocessing}
\label{server_guide:monitor-reprocessing}
Output from the monitor\_reprocessing cron job is stored in dated subdirectories here.  Also the file old\_context.txt
which records the last known operational context against which changes are measured.  Changed old\_context.txt will
trigger an affected datasets calculation as will changing the operational context on the web site.

\section{Server Dynamic File Storage}
\label{server_guide:server-dynamic-file-storage}
For operating,  the CRDS servers require a certain amount of dynamic storage use for purposes like:
\begin{itemize}
\item {} 
holding pending archive deliveries  (deliveries, catalogs)

\item {} 
uploading files (uploads, ingest, ingest\_ssb)

\end{itemize}

The server dynamic file storage is located on the Isilon file server at:
\begin{quote}

/ifs/crds/\textless{}obsevatory\textgreater{}/\textless{}use\textgreater{}/server\_files,    e.g. /ifs/crds/hst/ops/server\_files.
\end{quote}

Since this area is actively written as a consequence of users accessing the web site,  it is kept distinct from the
code and files required to run the server.

\subsection{Catalog Directory}
\label{server_guide:catalog-directory}
Files submitted to the archive generate .cat file lists which are stored permanently in the catalogs directory.
Any file in CRDS is also stored in the server file cache,  so given the .cat file list the delivery can be recreated
by regenerating file links in the deliveries directory.  The catalogs directory is an internal CRDS server data store
which records file lists from past deliveries.

\subsection{Deliveries Directory}
\label{server_guide:deliveries-directory}
The deliveries directory is cross-mounted between the CRDS server VM and CRDS-archive-pipeline machines,  not
necessarily under the same path name.

Files submitted to the archive are placed in the CRDS delivery directory along with a numbered catalog file which
lists the submitted files one per line.   Unlike more CRDS directories,  the delivery directory is cross-mounted
to pipeline machines which handle archiving.  As part of the protocol with the CRDS archiving pipeline,  the catalog
file is renamed to indicate processing status.  When the catalog is finally deleted,  CRDS assumes that archiving
is successful.   See crds.server.interactive.models for more info on the delivery naming protocol.  Note that files
in the delivery directory are linked to the same inode as the CRDS file cache copy of the file,  or,  in the case
of the .cat delivery file lists, to the permanent copy in the catalogs directory.  For references,  linking avoids
substantial I/O overheads associated with multi-gigabyte JWST references.  For catalogs,  linked or not,  like named
file lists should have the same contents in catalogs and deliveries.

\subsection{Uploads Directory}
\label{server_guide:uploads-directory}
The uploads directory is the default Django file upload directory for simple file uploads.

\subsection{Ingest Directory}
\label{server_guide:ingest-directory}
The ingest directory tree contains per-submitter subdirectories which are written to by the Django-file-upload
muli-file upload application used on file submission pages.  The user's guide gives instructions enabling submitters
to copy files directly into their per-user subdirectories as an upload bypass for telecommuters.  (This is a work
around for the situation in which a VPN user winds up transparently downloading and then explicitly uploading
references submitted via the web site;  instead,  a submitter places the file directly into their own ingest
directory keeping the file onsite,  then proceeds with the submission on the web server normally.)

\subsection{Ingest SSB Directory}
\label{server_guide:ingest-ssb-directory}
The ingest\_ssb directory tree is the historical generation and/or drop-off point for the files generated by the
jwst\_gentools.   Ingested files are then submitted to the web site.   The server does not directly access this
directory,  it shares space with it.

\section{Server File Cache}
\label{server_guide:server-file-cache}
Each CRDS server (test or ops) has a full copy (\textasciitilde{}2T allocation) of all operational and historical (CRDS-only)
reference files.   The dev servers have a smaller allocation which is generally linked to /grp/crds
(synced from ops servers) rather than internally stored.  The Isilon CRDS cache storage (i.e. CRDS\_PATH for servers)
is located similarly to dynamic file storage:
\begin{quote}

e.g. /ifs/crds/jwst/test/file\_cache
\end{quote}

The server file cache config area is generally updated transparently by running cronjobs.   The server file\_cache
and delivery areas are updated as a result of file submissions and archive activity.  Once global Isilon archive storage
becomes available, cache space can be reclaimed by symlinking the CRDS cache path to the global storage rather than
maintaining an internal copy;  there should be a lag of a couple weeks to a month between submission and reclamation
during which the potentially transient file is fully stored in the CRDS server.   Because the CRDS server caches also
contain unconfirmed and unarchived files,  they are currently read protected from anyone except crds.crdsoper.

See the User's manual in the ? on the web sites for more info on the CRDS cache.

\chapter{RC scripts}
\label{server_guide:rc-scripts}
The RC scripts are kept with the server source code in the directory ``hosts'' under the names dot\_setenv and
rc\_script.

\section{.setenv}
\label{server_guide:setenv}
The CRDS user runs under /bin/tcsh and executes .setenv for CRDS-server specific initializations.   Note that
\$HOME/.setenv is shared across all CRDS servers and should be modified with extreme caution.

\section{\$HOME/rc\_script}
\label{server_guide:home-rc-script}
The /home/crds/rc\_script is executed to restart the servers,  or shut them down,  whenever the server is rebooted.

\chapter{Cron Jobs}
\label{server_guide:cron-jobs}
Use shell command:

\begin{Verbatim}[commandchars=\\\{\}]
\% crontab -l
\end{Verbatim}

to dump the current crontab and observe the jobs.   Cronjobs currently produce .log files in the CRDS\_server directory.

To change the cronjobs modify \$\{CRDS\}/CRDS\_server/host/crontab and then do:

\begin{Verbatim}[commandchars=\\\{\}]
\% crontab host/crontab
\end{Verbatim}

Note that systems on the same subversion branch on which a crontab is modified and committed will automatically pick
up and use the new crontab during the nightly cron job.

See ``man cron'' or Google for more info on maintaining the cron table and crontab syntax.

\section{nightly.cron.job}
\label{server_guide:nightly-cron-job}
CRDS\_server/hosts/nifghtl directory and executes every night at 3:05 am.  The dev and test versions
of the nightly cron fully rebuild and reinstall the CRDS servers,  with the exceptions of database secret setup,
cron jobs, and .setenv rc\_script scripts.   The nightly cronjob on all servers captures diagnostic information about
the server,  including server configuration, disk quotas and usage, subversion status for detecting uncommitted
changes and observing branch and revision, and cache consistency and orphan file checking.   All of the servers
currently update subversion although the OPS (and often TEST) servers are typically on a static branch.   The dev
and test servers also restart.  Output from the nightly cron is sent to the MAILTO variable defined in the
CRDS\_server/host/crontab file,  currently \href{mailto:jmiller@stsci.edu}{jmiller@stsci.edu}.

\section{monitor\_reprocessing}
\label{server_guide:id2}
Every 5 minutes CRDS\_server/host/monitor\_reprocessing looks for changes in the CRDS operational context and
does an ``affected datasets'' context-to-context bestrefs comparison when the context changes.   This generates
an e-mail to the \$CRDS\_AFFECTED\_DATASETS\_RECIPIENTS addresses set up by the .setenv file.   bestrefs can require
from 20 seconds to 4-8 hours depending on the number of datasets potentially affected as determined by file
differences.

\section{clear\_expired\_locks}
\label{server_guide:clear-expired-locks}
Somewhat dubious,  this falls into the category of periodic server maintenance,  removing expired instrument locking
records from the server locking database.   Every 5 minutes.  Datatbase locks are considered expired when the current
time exceeds the start time of the lock plus the lock's duration;  since this is an asynchronous event,  the expired
lock records sits around in the database until scrubbed out.   In theory the expired locks are replaceable anyway
but this  routine makes sure they're not sitting around in the database causing confusion.  This does not produce e-mail.

\section{sync\_ops\_to\_grp}
\label{server_guide:sync-ops-to-grp}
Every 10 minutes \emph{sync\_ops\_to\_grp} runs crds.sync to publish the crds ops server to the \textbf{/grp/crds/cache} global readonly
Central Store file cache CRDS currently uses as default for OPUS 2014.3.   This does not produce e-mail.

\chapter{Maintenance Commands}
\label{server_guide:maintenance-commands}
Maintenance commands are typically run from the \textbf{\$CRDS/CRDS\_server directory},  the root of the CRDS\_server checkout.

The default Python environment does not include the CRDS server packages directory.   Many of the shell scripts
described below are either generated by the \$\{CRDS\}/crds\_server/install script or are dependent on scripts and
config files that are generated.   Hence, this section will only make sense in a CRDS server environment which has
been initialized at least once.

\section{Installing the Server Application}
\label{server_guide:installing-the-server-application}
Running the ./install script will perform many actions including regenerating the environment definition script
\emph{\$\{CRDS\}/CRDS\_server/env.csh}.  Primarily ./install installs the \emph{crds} client and \emph{crds.server} packages into
a server specific python directory which is added to PYTHONPATH automatically in \emph{env.csh}.  In addition ./install
instantiates some Apache configuration file templates and copies them to the appropriate installation directories.

The install script is typically run like this:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./install [hst\textbar{}jwst]  [django\textbar{}dev\textbar{}test\textbar{}prod]  \textbar{}\& tee install.\textless{}observatory\textgreater{}.\textless{}use\textgreater{}.err
\end{Verbatim}

For example:

\begin{Verbatim}[commandchars=\\\{\}]
\% server   \# alias to cd to server source directory
\% ./install hst dev  \textbar{}\& tee install.hst.dev.err
\end{Verbatim}

Running ./install explicitly is required to generate \emph{env.csh} for the first time.  Afterward,  env.csh essentially
knows this server is for ``hst dev''.

\section{Starting and Stopping the Server}
\label{server_guide:starting-and-stopping-the-server}
The CRDS server can be started and stopped like this:

\begin{Verbatim}[commandchars=\\\{\}]
\% server   \# alias to cd to server source directory
\% ./run
\% ./stop
\end{Verbatim}

\section{Re-installing the CRDS Server}
\label{server_guide:re-installing-the-crds-server}
Once the CRDS server has been initialized, the server can be stopped, updated/re-installed, and retarted with
the \emph{rerun} command:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./rerun
\end{Verbatim}

This process does not affect the server Python stack.

\section{Running Server Tests}
\label{server_guide:running-server-tests}
The CRDS server unit tests (\textbf{NOT ADVISABLE FOR OPS}) can be run like this:

\begin{Verbatim}[commandchars=\\\{\}]
\% server   \# alias to cd to server source directory
\% ./runtests
\end{Verbatim}

additional parameters can be passed to runtests,  for example to select specific tests:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./runtests interactive.tests.Hst.test\_index
\end{Verbatim}

Runtests should not be executed on operational or in-test servers because it has side effects which interfere with
server operation.   Runtests has been modified to switch to a backup port during execution,  but the version of
code necessary will only be deployed with OPUS 2014.3 so it is not yet in operations.

The server unit tests are ponderous.  Eventually you may \emph{\textless{}control-c\textgreater{}} and leave behind a junk test
database which blocks subsequent testing.  That can generally cleaned up,  with \textbf{extreme caution},  as follows
for e.g. hst dev:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./manage dbshell
mysql\textgreater{} drop database test\_crds\_hst\_dev;
\end{Verbatim}

It should be noted that the server unit tests typically do run on the dev and test servers in the nightly
cronjob, generally making them available without waiting on the following day.

\section{CRDS catalog initializaton}
\label{server_guide:crds-catalog-initializaton}
Historically the CRDS server catalogs were initialized many times from existing CDBS and JWST references and
the initial CRDS rules set.  \emph{./init} is rarely used anymore but may still be useful for setting up a Django local
test environment, typically called a ``dev'' server except in CRDS the ``dev'' server is an actual VM so Django dev
servers are referred to as ``django'' servers.

For the most part the ./init script is tasked with installing the server's initial copy of CRDS rules and initializing
the CRDS file catalog (the crds.server.interactive.models Django database with 19000 CDBS references and CRDS rules):

\begin{Verbatim}[commandchars=\\\{\}]
\% ./init [hst\textbar{}jwst] [django\textbar{}dev\textbar{}test\textbar{}ops]
\textless{}enter password for test user\textgreater{}
\end{Verbatim}

\textbf{NOTE:}  At this stage \emph{./init} should not be run on the OPS servers.   For operational servers it
has effectively been superceded by \textbf{tools/restore\_server} and \textbf{tools/mirror\_server}.

\section{Starting the server}
\label{server_guide:starting-the-server}
The \emph{./run} script starts Apache (many httpd processes) and memcached after which the CRDS server should definitely
be abvailable on it's private port (typically 8001).   The web proxy is provided by an independent system which
is rarely-if-ever unavailable:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./run
\end{Verbatim}

\section{Updating and Restarting}
\label{server_guide:updating-and-restarting}
Performing a server update often revolves around stopping the server,  changing and reinstalling the Django
application, and restarting the server:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./rerun
\end{Verbatim}

This works by sequentially invoking other more basic scripts: ./stop, ./install, ./run.

\emph{./rerun} produces a log file of the voluminous install output as install.\textless{}observatory\textgreater{}.\textless{}usecase\textgreater{}.err.  If things
aren't working coherently,  check the install...err file to verify that no setup functions failed,  as might
happen for a Python syntax error.

\section{Running Server Self-tests}
\label{server_guide:running-server-self-tests}
The server self-tests exercise most but not all of the Django interactive view code,  JSONRPC code, and basic database
interface to DADSOPS.   Although the interactive (web view) self tests run in a Django test database,  the JSONRPC
tests simply ivoke the CRDS client routines to call to the server and verify results.   Hence,  the JSONRPC code
is effectively tested against a live server,  exercising it just like a normal user.  In addition,  the Django
caching interface is not mocked during testing,  so memcached effects impact the live server.   Consequently,  for
running tests on dev, test, or ops servers,  runtests moves the server to the ``backup port'' where it normally hides
during server restoration or mirroring.   Self-tests are typically run like this:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./runtests   \# (in second terminal window if using a Django dev local server)
\end{Verbatim}

\textbf{NOTE:}    without special arrangements,  server self-tests should not be run on the operational servers.
Self-tests are normally run on the dev and test servers during the nightly cron job at 3 am.

\section{Django Management Commands}
\label{server_guide:django-management-commands}
Django has a manage.py module which is frequently referenced for server maintenance activities.   In CRDS this is
wrapped as:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./manage \textless{}additional parameters to manage.py\textgreater{}
\end{Verbatim}

\section{Command Line Server Debug}
\label{server_guide:command-line-server-debug}
An Ipython shell can be started in either of these equivalent ways:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./manage shell
\end{Verbatim}

This shell can be useful for debugging and/or maintaining Django models, view code, JSONRPC routines, or
the database interface to the DADSOPS dataset catalog database (HST).

This shell executes in the same directory/context as the CRDS server,  so it provides the same interactive
environment in which server Django code normally executes.   Consequently server modules and packages tend to
import and function normally for interactive debug;  this happens in a shell processs,  not an Apache process,
so the principle coupling to a running server would be the database and file system... and potentially memcached.

\section{CRDS Catalog Database SQL Commands}
\label{server_guide:crds-catalog-database-sql-commands}
The CRDS reference and rules catalog is implemented as a Django model in crds.server.interactive.models.  Typically
it is accessed by using the models module, classes, and functions.  Nevertheless,  the Django models can be accessed
directly with SQL like this:

\begin{Verbatim}[commandchars=\\\{\}]
\% ./manage dbshell  \# to open a SQL prompt to the CRDS server database
...
mysql\textgreater{} ... SQL commands ...
\end{Verbatim}

\textbf{NOTE}:  the CRDS Catalog is in a Django database which is distinct from the DADSOPS dataset catalog that
CRDS uses to find matching parameters and dataset ids.

\section{Nightly Backup}
\label{server_guide:nightly-backup}
All 6 servers run a nightly backup job at 3 am EST.   The backup dumps the Django database and attempts to capture
transient or unique information in the file system.   The backups make a full copy of all CRDS rules.   The backups
do not contain any references,  and in particular,  no transient references in the process of submission or
confirmation.   Nevertheless,  the backups are extremely useful and appear to be capable of restoring
``yesterday's quiescent server''.

Making a backup is done as follows:

\begin{Verbatim}[commandchars=\\\{\}]
\% tools/backup\_server
\end{Verbatim}

backup\_server results in the generation of backup files which are placed in \textbf{\$\{CRDS\}/server/db\_backups} in a dated
subdirectory with dated names,  and also globally in \$\{HOME\}/backups with generic names.   Both locations should be
considered secret and hidden using file permissions.   Dated backups are persistent,  the backups in \$\{HOME\}/backups
are overwritten every time backup\_server is run.   There are unique files for each server.   The files in
\$\{CRDS\}/server/db\_backups are only visible on that VM.

\section{Restoring Nightly Backups}
\label{server_guide:restoring-nightly-backups}
A relatively recent addition is the tools/restore\_server script.   It is quite simple to restore the nightly backup
of a server:

\begin{Verbatim}[commandchars=\\\{\}]
\% tools/restore\_server
\end{Verbatim}

Conceptually,  restore server reloads the server database and restores the delivery directories and catalogs,  and
removes any reference or rules files orphaned by the database restoration,  those added to the cache since the backup
was made.

As a matter of implementation,  server restoration is handled by mirroring a server to itself.

During the process of restoration,  the server is moved to a hidden backup port and will be seen as temporarily
unavailble through the proxy.

restore\_server utilizes the backup files in \$\{HOME\}/backups,  nominally the ones from the last time backup\_server was
executed.   There is currently no automatic process for appropriately copying the dated backup files from
\$\{CRDS\}/server/db\_backups to \$\{HOME\}/backups so they can be used in server mirroring or restoration.

\textbf{IMPORTANT:}  restore\_server should only be used on the OPS server under duress.   Prior to restoring the OPS server,
review the restore\_server / mirror\_server and attempt to mirror the OPS server down to a DEV server,  then test the
mirrored DEV server both interactively and with runtests.

\section{Server Mirroring}
\label{server_guide:server-mirroring}
The term \emph{server mirroring} is given to the process of transferring the server database and file system state from one
VM and server to another,  effectively making the destination server a copy of the source server.

Typical mirroring flows would be to copy the HST OPS server down to the TEST or DEV server,  or TEST down to DEV.

Server mirroring leverages (nightly or dynamic) server backups by restoring them to different servers.  Afterward,
the sync tool is run to synchronize the destination cache with the source server.   Subsequently,  the tools/orphan\_files
script is run to verify destination server file system consistency with the destination server file catalog.

mirror\_server does not safeguard against it,  but it is almost certainly an error to run mirror\_server on an
OPS VM,  which in all likelihood replaces OPS state with something inferior.   There is one exception:  \emph{restore\_server}
will mirror the OPS server to itself by running \emph{mirror\_server} internally in order to revert OPS to its state at the
time of the nightly backup.

For example,  to copy the test server (hst-crds-test, tlhstcrdsv1) down to the dev server (hst-crds-dev, dlhstcrdsv1),
perform these steps.  First, optionally, on the source server:

\begin{Verbatim}[commandchars=\\\{\}]
\# login tlhstcrdsv1
\% server
\% tools/backup\_server
\end{Verbatim}

That puts required backup files in global (cross-server) \$\{HOME\}/backups.  If this steps is omitted,  the files in
\$\{HOME\}/backups should correspond to the server state at the time of the last backup,  nominally 3 am.  If you're trying
to mirror a change on the test server that you just made,  then immediately backing up the test server is required so
that the change is recorded in the current backup.

Second, on the destination server:

\begin{Verbatim}[commandchars=\\\{\}]
\# login dlhstcrdsv1
\% server
\% tools/mirror\_server hst test https://hst-crds-test.stsci.edu \textbar{}\& tee mirror\_server.hst.test.err
\end{Verbatim}

where the parameters to mirror\_server specify the \emph{source} server and the destination is implicitly the
server of the current login.

Server mirroring requires the source server to be online and available.   The destination server is moved
to a backup port so that it is unavailable while it transitions through various inconsistent states.

\renewcommand{\indexname}{Index}
\printindex
\end{document}

### 2014-07-17 docs/server_guide/build/latex/crds_server.tex
More server_guide work.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@1563 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 \DeclareUnicodeCharacter{00A0}{\nobreakspace}
+\usepackage{cmap}
 \usepackage[T1]{fontenc}
@@
 \usepackage{multirow}
-
-\usepackage{enumitem}
-\setlistdepth{15}
 
@@
 \title{CRDS Server Documentation}
-\date{July 16, 2014}
+\date{July 17, 2014}
 \release{1.1}
@@
 
-\def\PYG@tok@gd{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
-\def\PYG@tok@gu{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
-\def\PYG@tok@gt{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.25,0.82}{##1}}}
-\def\PYG@tok@gs{\let\PYG@bf=\textbf}
-\def\PYG@tok@gr{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
-\def\PYG@tok@cm{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
-\def\PYG@tok@vg{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\def\PYG@tok@m{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\def\PYG@tok@mh{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\def\PYG@tok@cs{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\colorbox[rgb]{1.00,0.94,0.94}{##1}}}
-\def\PYG@tok@ge{\let\PYG@it=\textit}
-\def\PYG@tok@vc{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\def\PYG@tok@il{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\def\PYG@tok@go{\def\PYG@tc##1{\textcolor[rgb]{0.19,0.19,0.19}{##1}}}
-\def\PYG@tok@cp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@gi{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
-\def\PYG@tok@gh{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
-\def\PYG@tok@ni{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
-\def\PYG@tok@nl{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
-\def\PYG@tok@nn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
-\def\PYG@tok@no{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
-\def\PYG@tok@na{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@nb{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@nc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
-\def\PYG@tok@nd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
-\def\PYG@tok@ne{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@nf{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
-\def\PYG@tok@si{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
-\def\PYG@tok@s2{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@vi{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\def\PYG@tok@nt{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
-\def\PYG@tok@nv{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\def\PYG@tok@s1{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@gp{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
-\def\PYG@tok@sh{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@ow{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@sx{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
-\def\PYG@tok@bp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@c1{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
-\def\PYG@tok@kc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@c{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
-\def\PYG@tok@mf{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\def\PYG@tok@err{\def\PYG@bc##1{\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{##1}}}
-\def\PYG@tok@kd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@ss{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
-\def\PYG@tok@sr{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
-\def\PYG@tok@mo{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\def\PYG@tok@mi{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\def\PYG@tok@kn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@o{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\def\PYG@tok@kr{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@s{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@kp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@w{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
-\def\PYG@tok@kt{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
-\def\PYG@tok@sc{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@sb{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@k{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\def\PYG@tok@se{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\def\PYG@tok@sd{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@gd\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
+\expandafter\def\csname PYG@tok@gu\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
+\expandafter\def\csname PYG@tok@gt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
+\expandafter\def\csname PYG@tok@gs\endcsname{\let\PYG@bf=\textbf}
+\expandafter\def\csname PYG@tok@gr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
+\expandafter\def\csname PYG@tok@cm\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
+\expandafter\def\csname PYG@tok@vg\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\expandafter\def\csname PYG@tok@m\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\expandafter\def\csname PYG@tok@mh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\expandafter\def\csname PYG@tok@cs\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\colorbox[rgb]{1.00,0.94,0.94}{\strut ##1}}}
+\expandafter\def\csname PYG@tok@ge\endcsname{\let\PYG@it=\textit}
+\expandafter\def\csname PYG@tok@vc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\expandafter\def\csname PYG@tok@il\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\expandafter\def\csname PYG@tok@go\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.20,0.20,0.20}{##1}}}
+\expandafter\def\csname PYG@tok@cp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@gi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
+\expandafter\def\csname PYG@tok@gh\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
+\expandafter\def\csname PYG@tok@ni\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
+\expandafter\def\csname PYG@tok@nl\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
+\expandafter\def\csname PYG@tok@nn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
+\expandafter\def\csname PYG@tok@no\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
+\expandafter\def\csname PYG@tok@na\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@nb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@nc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
+\expandafter\def\csname PYG@tok@nd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
+\expandafter\def\csname PYG@tok@ne\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@nf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
+\expandafter\def\csname PYG@tok@si\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
+\expandafter\def\csname PYG@tok@s2\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@vi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\expandafter\def\csname PYG@tok@nt\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
+\expandafter\def\csname PYG@tok@nv\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\expandafter\def\csname PYG@tok@s1\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@gp\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
+\expandafter\def\csname PYG@tok@sh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@ow\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@sx\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
+\expandafter\def\csname PYG@tok@bp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@c1\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
+\expandafter\def\csname PYG@tok@kc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@c\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
+\expandafter\def\csname PYG@tok@mf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\expandafter\def\csname PYG@tok@err\endcsname{\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
+\expandafter\def\csname PYG@tok@kd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@ss\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
+\expandafter\def\csname PYG@tok@sr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
+\expandafter\def\csname PYG@tok@mo\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\expandafter\def\csname PYG@tok@mi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\expandafter\def\csname PYG@tok@kn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@o\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PYG@tok@kr\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@s\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@kp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@w\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
+\expandafter\def\csname PYG@tok@kt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
+\expandafter\def\csname PYG@tok@sc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@sb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@k\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\expandafter\def\csname PYG@tok@se\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\expandafter\def\csname PYG@tok@sd\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
 
@@
 \def\PYGZca{\char`\^}
+\def\PYGZam{\char`\&}
+\def\PYGZlt{\char`\<}
+\def\PYGZgt{\char`\>}
 \def\PYGZsh{\char`\#}
@@
 \def\PYGZdl{\char`\$}
+\def\PYGZhy{\char`\-}
+\def\PYGZsq{\char`\'}
+\def\PYGZdq{\char`\"}
 \def\PYGZti{\char`\~}
@@
 \item {} 
-Todd Miller:    yours truly,  primary CRDS and (sole) CRDS server application developer.
+Todd Miller:    primary CRDS and CRDS server application developer.
 
@@
 \label{server_guide:crds-pseudo-user-and-group}
-The CRDS servers run as the no-login user ``crds''.  The CRDS servers are maintained by getting sudo
-access to the crds user and the equivalent of ``su crds'' from a normal user account.   The CRDS
-crds\_server script contains the following:
+The CRDS servers run as the no-login user ``crds''.  The CRDS  crds\_server script contains the following:
 
 \begin{Verbatim}[commandchars=\\\{\}]
-ssh -A -t \$1.stsci.edu /usr/bin/sudo /bin/su - crds
+\PYGZpc{} ssh \PYGZhy{}A \PYGZhy{}t \PYGZdl{}1.stsci.edu /usr/bin/sudo /bin/su \PYGZhy{} crds
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% crds\_server plhstcrdsv1
-\# crds\_server \textless{}VM-hostname\textgreater{}
+\PYGZpc{} crds\PYGZus{}server plhstcrdsv1
+\PYGZsh{} crds\PYGZus{}server \PYGZlt{}VM\PYGZhy{}hostname\PYGZgt{}
 \end{Verbatim}
 
-The ssh first logs into your normal user account on the server VM, then su's you to CRDS.
+The ssh first logs into your normal user account on the server VM, then su's you to CRDS.   It is not possible
+to directly login to the crds user.
 
@@
 Members of DSB share the crdsoper group and use it to modify the CRDS server file delivery
-directory described below.
+directory described below or copy files directly to their ingest directories.
 
@@
 \hline
-\textbf{
+\textsf{\relax 
 observatory
-} & \textbf{
+} & \textsf{\relax 
 use
-} & \textbf{
+} & \textsf{\relax 
 host/vm
-} & \textbf{
+} & \textsf{\relax 
 direct port
-} & \textbf{
+} & \textsf{\relax 
 url
-}\\\hline
-
+}\\
+\hline
 hst
@@
 \href{http://localhost:8000}{http://localhost:8000}
-\\\hline
+\\
 
@@
 \href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
-\\\hline
+\\
 
@@
 \href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
-\\\hline
+\\
 
@@
 \href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
-\\\hline
+\\
 
@@
 \href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
-\\\hline
+\\
 
@@
 \href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
-\\\hline
+\\
 
@@
 \href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
-\\\hline
-\end{tabulary}
+\\
+\hline\end{tabulary}
 
@@
 
+\chapter{Mailing Lists}
+\label{server_guide:mailing-lists}
+The following CRDS mailing lists are defined on behalf of CRDS:
+
+\begin{tabulary}{\linewidth}{|L|L|L|}
+\hline
+\textsf{\relax 
+mailing list
+} & \textsf{\relax 
+moderator
+} & \textsf{\relax 
+purpose
+}\\
+\hline
+\href{mailto:crds@stsci.edu}{crds@stsci.edu}
+ & 
+mcmaster
+ & 
+comm between INS and CRDS team, also accidental use
+\\
+
+\href{mailto:crds\_team@stsci.edu}{crds\_team@stsci.edu}
+ & 
+mcmaster
+ & 
+comm within CRDS delivery team, DSB, archive, pipelines
+\\
+
+\href{mailto:crds\_datamng@stsci.edu}{crds\_datamng@stsci.edu}
+ & 
+mcmaster
+ & 
+common destination for affected datasets output
+\\
+
+\href{mailto:crds-servers@stsci.edu}{crds-servers@stsci.edu}
+ & 
+jmiller
+ & 
+little used,  new source address for affected datasets,  server details + news
+\\
+
+\href{mailto:crds\_hst\_ops\_reprocessing@stsci.edu}{crds\_hst\_ops\_reprocessing@stsci.edu}
+ & 
+jmiller
+ & 
+affected datasets output list, hst ops
+\\
+
+\href{mailto:crds\_hst\_test\_reprocessing@stsci.edu}{crds\_hst\_test\_reprocessing@stsci.edu}
+ & 
+jmiller
+ & 
+affected datasets output list, hst test
+\\
+
+\href{mailto:crds\_jwst\_ops\_reprocessing@stsci.edu}{crds\_jwst\_ops\_reprocessing@stsci.edu}
+ & 
+jmiller
+ & 
+affected datasets output list, jwst ops
+\\
+
+\href{mailto:crds\_jwst\_test\_reprocessing@stsci.edu}{crds\_jwst\_test\_reprocessing@stsci.edu}
+ & 
+jmiller
+ & 
+affected datasets output list, jwst test
+\\
+\hline\end{tabulary}
+
+These are all closed lists.  Most critical are crds\_team and crds\_datamng.   The reprocessing lists are intended and/or used to drive
+automated systems so be careful with traffic on those.
+
 \chapter{Server File Systems}
@@
 
-\section{/home/crds}
-\label{server_guide:home-crds}
+\section{Cross-Server Shared Home (/home/crds)}
+\label{server_guide:cross-server-shared-home-home-crds}
 The VMs and servers share a common /home/crds directory which has potential as a single point failure.  In particular,
 critical shell rc scripts (.setenv) are shared by all servers and must be updated with extreme care because
-any error instantly affects all 6 servers.  Consequently, .setenv should be kept as simple as reasonably
-possible.  /home/crds also houses rc\_script.
+any error instantly affects all 6 servers.
 
 /home/crds is useful for communicating information between VMs during setup and maintenance.
+
+The RC scripts are version controlled with the server source code in the directory ``hosts'' under the names dot\_setenv
+and rc\_script.
+
+\subsection{.setenv}
+\label{server_guide:setenv}
+The CRDS user runs under /bin/tcsh and executes .setenv for CRDS-server specific initializations.   Note that
+\$HOME/.setenv is shared across all CRDS servers and should be modified with extreme caution.   The environment
+variables defined to differentiate the 6 CRDS servers are,  for example for JWST DEV:
+
+\begin{Verbatim}[commandchars=\\\{\}]
+CRDS\PYGZus{}PROJECT        jwst
+CRDS\PYGZus{}USECASE        dev
+CRDS\PYGZus{}SERVER         dljwstcrdsv1
+CRDS                /crds/data1/dljwstcrdsv1
+PATH                /crds/data1/dljwstcrdsv1/CRDS\PYGZus{}server/host   /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11/bin
+CRDS\PYGZus{}STACK          /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
+CRDS\PYGZus{}AFFECTED...    jmiller@stsci.edu eisenhamer@stsci.edu
+CRDS\PYGZus{}IFS            /ifs/crds/jwst/dev
+CRDS\PYGZus{}FILE\PYGZus{}CACHE     /ifs/crds/jwst/dev/file\PYGZus{}cache
+CRDS\PYGZus{}SERVER\PYGZus{}FILES   /ifs/crds/jwst/dev/server\PYGZus{}files
+META\PYGZus{}PREFIX         /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
+\end{Verbatim}
+
+Additional environment variables, particularly those related to server installation, are defined in
+\$\{CRDS\}/CRDS\_server/env.csh.
+
+META\_PREFIX is roughly equivalent to /usr/local,  the common value passed to --prefix in ./configure,  etc.,
+for building the server Python stack.
+
+\subsection{.alias}
+\label{server_guide:alias}
+CRDS augments the standard .alias file with these aliases for moving around the file system:
+
+\begin{Verbatim}[commandchars=\\\{\}]
+\PYGZsh{}  Source code areas
+alias crds       \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZdq{}
+alias server     \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZus{}server\PYGZdq{}
+alias stack      \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}STACK\PYGZcb{}\PYGZdq{}
+alias installer \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/crds\PYGZus{}stacks/installer3/build\PYGZdq{}
+
+\PYGZsh{} Server maintenance areas
+alias logs       \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/server/logs\PYGZdq{}
+alias backups    \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/server/db\PYGZus{}backups\PYGZdq{}
+
+\PYGZsh{} CRDS code area
+alias libpython  \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/python/lib/python\PYGZdq{}
+
+\PYGZsh{} Server working data files areas
+alias deliveries \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/deliveries\PYGZdq{}
+alias catalogs   \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/catalogs\PYGZdq{}
+alias ingest     \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/ingest\PYGZdq{}
+alias file\PYGZus{}cache \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}FILE\PYGZus{}CACHE\PYGZcb{}\PYGZdq{}
+
+\PYGZsh{} Isilon and VM file systems
+alias ifs        \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}IFS\PYGZcb{}\PYGZdq{}
+alias data1      \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}\PYGZdq{}
+\end{Verbatim}
+
+\subsection{rc\_script}
+\label{server_guide:rc-script}
+The /home/crds/rc\_script is executed to restart the servers,  or shut them down,  whenever the server is rebooted.
 
@@
 
-\subsection{Server Runtime Directories}
-\label{server_guide:server-runtime-directories}
+\subsection{server runtime directory}
+\label{server_guide:server-runtime-directory}
 A number of subdirectories are used to store files related to running Apache, logging, or backups under
@@
 
-\subsubsection{conf}
-\label{server_guide:conf}
+\subsubsection{conf subdirectory}
+\label{server_guide:conf-subdirectory}
 Apache config files are installed here at e.g. /crds/data1/dlhstcrdsv1/server/conf.  Files ssl.conf and httpd.conf.
 
-\subsubsection{logs}
-\label{server_guide:logs}
+\subsubsection{logs subdirectory}
+\label{server_guide:logs-subdirectory}
 There are a number of Apache logs kept at e.g. /crds/data1/dlhstcrdsv1/server/logs.  These logs record requests to
@@
 
-\subsubsection{db\_backups}
-\label{server_guide:db-backups}
+\subsubsection{db\_backups subdirectory}
+\label{server_guide:db-backups-subdirectory}
 The output of the CRDS\_server/tools/backup\_server script is kept here in dated subdirectories,
@@
 
-\subsubsection{wsgi-scripts}
-\label{server_guide:wsgi-scripts}
+\subsubsection{wsgi-scripts subdirectory}
+\label{server_guide:wsgi-scripts-subdirectory}
 The mod\_wsgi script which bridges from Apache to Django,  crds.wsgi,  is kept here,
@@
 
-\subsubsection{run}
-\label{server_guide:run}
-The running Apache process id is stored here.   The id of memcached should be stored here as well but isn't.
+\subsubsection{run subdirectory}
+\label{server_guide:run-subdirectory}
+The running Apache process id is stored here.   The id of memcached should be stored here as well but isn't stored.
 
-\subsection{Database files}
-\label{server_guide:database-files}
+\subsection{database directory}
+\label{server_guide:database-directory}
 Files required to support operations with databases are stored in a top level static file system
@@
 
-\subsection{CRDS}
-\label{server_guide:crds}
+\subsection{CRDS client source directory}
+\label{server_guide:crds-client-source-directory}
 The checkout of the CRDS core library source code installed with the CRDS server is located in the static file tree
-under the subdirectory CRDS and visited using the alias ``crds''.  e.g.  /crds/data1/plhstcrdsv1/CRDS
+under the subdirectory CRDS and visited using the alias ``crds''.  e.g.  /crds/data1/plhstcrdsv1/CRDS.  Typically
+the server uses the core library and utilities directly,  but the server is also responsible for testing the client
+JSONRPC services.
 
-\subsection{CRDS\_server}
-\label{server_guide:crds-server}
+\subsection{CRDS\_server source directory}
+\label{server_guide:crds-server-source-directory}
 The checkout of the CRDS server source code is located in the static file tree under the subdirectory CRDS\_server
@@
 
-\subsubsection{host}
-\label{server_guide:host}
-The CRDS\_server/host subdirectory is on the PATH.  It contains scripts related to cron jobs,  affected datasets
-reprocessing, stack building,  server utilities, etc.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/host
+\subsubsection{sources directory}
+\label{server_guide:sources-directory}
+This directory contains the Django server and application source code.
 
-\subsubsection{tools}
-\label{server_guide:tools}
-The CRDS\_server/tools directory contains more complicated scripts related to server backup, restore, mirroring,
-consistency checking, server initialization, user and group maintenance, etc.   The tools directory is not on the
-PATH and contains more eclectic scripts developed in an unplanned manner,  basically capturing whatever I needed
-to do repeatedly or had to Google.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/tools
-
-\subsubsection{servers}
-\label{server_guide:id1}
-This directory contains the Apache and mod\_wsgi configuration files.  e.g. /crds/data1/plhstcrdsv1/CRDS\_server/servers
-
-\subsubsection{sources}
-\label{server_guide:sources}
-This directory contains the Django server and application source code.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/sources
+e.g. /crds/data1/plhstcrdsv1/CRDS\_server/sources
 \begin{itemize}
 \item {} \begin{description}
-\item[{\emph{sources/configs} contains site specific django configuration and database configuration files.  The appropriate files}] \leavevmode
+\item[{\emph{sources/configs}}] \leavevmode
+contains site specific django configuration and database configuration files.  The appropriate files
 are copied to sources/site\_config.py and sources/crds\_database.py at install time.   Those are then
@@
 
-\item {} 
-\emph{sources/urls.py}     defines most of the site URLs for all applications.
+\item {} \begin{description}
+\item[{\emph{sources/urls.py}}] \leavevmode
+defines most of the site URLs for all applications.
 
-\item {} 
-\emph{sources/settings.py} fairly standard Django settings.py
-
-\item {} 
-\emph{sources/templates}  contains web template base classes
-
-\item {} 
-\emph{sources/static}     contains most CRDS static files,  particularly Javascript and CSS.
-
-\item {} 
-\emph{sources/interactive}  is the primary web application for CRDS browsing and file submission.
-
-\item {} 
-\emph{sources/jsonapi}     is the JSONRPC application which supports web services in the crds.client api.
+\end{description}
 
 \item {} \begin{description}
-\item[{\emph{sources/jpoll}    application supports the Javascript logging + done polling system used for long running views,}] \leavevmode
+\item[{\emph{sources/settings.py}}] \leavevmode
+fairly standard Django settings.py
+
+\end{description}
+
+\item {} \begin{description}
+\item[{\emph{sources/templates}}] \leavevmode
+contains web template base classes.  many applications also contain a \emph{templates} subdirectory.
+
+\end{description}
+
+\item {} \begin{description}
+\item[{\emph{sources/static}}] \leavevmode
+contains most CRDS static files,  particularly Javascript and CSS.
+
+\end{description}
+
+\item {} \begin{description}
+\item[{\emph{sources/interactive}}] \leavevmode
+is the primary web application for CRDS browsing and file submission.
+
+\end{description}
+
+\item {} \begin{description}
+\item[{\emph{sources/jsonapi}}] \leavevmode
+is the JSONRPC application which supports web services in the crds.client api.
+
+\end{description}
+
+\item {} \begin{description}
+\item[{\emph{sources/jpoll}}] \leavevmode
+application supports the Javascript logging + done polling system used for long running views,
 particularly file submissions which can exceed proxy timeouts and run too long to leave a human
@@
 
-\item {} 
-\emph{sources/locking}     application for database based locks used by CRDS web logins for exclusive access to an instrument.
+\item {} \begin{description}
+\item[{\emph{sources/locking}}] \leavevmode
+application for database based locks used by CRDS web logins for exclusive access to an instrument.
 
-\item {} 
-\emph{sources/fileupload}  application supports the fancy file submission file upload dialogs for file submissions.
+\end{description}
 
 \item {} \begin{description}
-\item[{\emph{sources/stats}      application mostly defunct django-level request logging to database,  superceded by Apache}] \leavevmode
+\item[{\emph{sources/fileupload}}] \leavevmode
+application supports the fancy file submission file upload dialogs for file submissions.
+
+\end{description}
+
+\item {} \begin{description}
+\item[{\emph{sources/stats}}] \leavevmode
+application mostly defunct django-level request logging to database,  superceded by Apache
 logging.  Some parameter capture not present in current Apache configuration.
@@
 
-\subsection{crds\_stacks}
-\label{server_guide:crds-stacks}
-The crds\_stacks subdirectory contains stock python stacks and source code.  The CRDS server Python stack is built
-from source contained in the installer3 subdirectory.  An automatic nightly build and reinstall of the stack occurs on the
-dev and test servers so it's possible to upgrade all the non-ops servers by updating the installer3 repo.  The
-master copy of the CRDS server installer3 repo is contained in /eng/ssb/crds/installer3.   Independent checkouts
-of the repo are contained in the stacks file store for each VM.   e.g. /crds/data1/plhstcrdsv1/crds\_stacks
+\subsubsection{host directory}
+\label{server_guide:host-directory}
+The CRDS\_server/host subdirectory is on the PATH.  It contains scripts related to cron jobs,  affected datasets
+reprocessing, stack building,  server utilities, etc.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/host
 
-\subsection{monitor\_reprocessing}
-\label{server_guide:monitor-reprocessing}
+\subsubsection{tools directory}
+\label{server_guide:tools-directory}
+The CRDS\_server/tools directory contains more complicated scripts related to server backup, restore, mirroring,
+consistency checking, server initialization, user and group maintenance, etc.   The tools directory is not on the
+PATH and contains more eclectic scripts developed in an unplanned manner,  basically capturing whatever I needed
+to do repeatedly or had to Google.   e.g. /crds/data1/plhstcrdsv1/CRDS\_server/tools
+
+\subsubsection{servers directory}
+\label{server_guide:servers-directory}
+e.g. /crds/data1/plhstcrdsv1/CRDS\_server/servers
+
+This directory contains the Apache and mod\_wsgi configuration files which are copied by ./install to their CRDS
+server installation directories.
+
+\subsection{crds\_stacks directory}
+\label{server_guide:crds-stacks-directory}
+e.g. /crds/data1/plhstcrdsv1/crds\_stacks
+
+The crds\_stacks subdirectory contains mostly stock python stack binaries and source code,  supporting third party packages
+for the server application.  The CRDS server Python stack is built from source contained in the installer3 subdirectory.
+Binaries are output to parallel subdirectories,  e.g. crds\_11.
+
+An automatic nightly build and reinstall of the stack occurs on the dev and test servers so it's possible to upgrade all
+the non-ops servers by updating the central installer3 repo at /eng/ssb/crds/installer3.
+
+Independent checkouts of the repo are contained in the stacks file store for each VM. The purpose of individual VMs is
+to facilitate independent configuration and test of Linux, the Python stack, and the CRDS server on each distinct VM.
+The OPS servers are configured for manual updates.
+
+\subsection{monitor\_reprocessing directory}
+\label{server_guide:monitor-reprocessing-directory}
 Output from the monitor\_reprocessing cron job is stored in dated subdirectories here.  Also the file old\_context.txt
@@
 
-\subsection{Catalog Directory}
-\label{server_guide:catalog-directory}
+\subsection{catalogs subdirectory}
+\label{server_guide:catalogs-subdirectory}
 Files submitted to the archive generate .cat file lists which are stored permanently in the catalogs directory.
@@
 
-\subsection{Deliveries Directory}
-\label{server_guide:deliveries-directory}
+\subsection{deliveries subdirectory}
+\label{server_guide:deliveries-subdirectory}
 The deliveries directory is cross-mounted between the CRDS server VM and CRDS-archive-pipeline machines,  not
@@
 
-\subsection{Uploads Directory}
-\label{server_guide:uploads-directory}
+\subsection{uploads subdirectory}
+\label{server_guide:uploads-subdirectory}
 The uploads directory is the default Django file upload directory for simple file uploads.
 
-\subsection{Ingest Directory}
-\label{server_guide:ingest-directory}
+\subsection{ingest subdirectory}
+\label{server_guide:ingest-subdirectory}
 The ingest directory tree contains per-submitter subdirectories which are written to by the Django-file-upload
@@
 
-\subsection{Ingest SSB Directory}
-\label{server_guide:ingest-ssb-directory}
+\subsection{ingest\_ssb subdirectory}
+\label{server_guide:ingest-ssb-subdirectory}
 The ingest\_ssb directory tree is the historical generation and/or drop-off point for the files generated by the
@@
 
-\section{Server File Cache}
-\label{server_guide:server-file-cache}
-Each CRDS server (test or ops) has a full copy (\textasciitilde{}2T allocation) of all operational and historical (CRDS-only)
-reference files.   The dev servers have a smaller allocation which is generally linked to /grp/crds
-(synced from ops servers) rather than internally stored.  The Isilon CRDS cache storage (i.e. CRDS\_PATH for servers)
-is located similarly to dynamic file storage:
+\section{Server File Private Cache}
+\label{server_guide:server-file-private-cache}
+The Isilon CRDS cache storage (i.e. CRDS\_PATH for servers) is located similarly to dynamic file storage:
 \begin{quote}
@@
 \end{quote}
+
+Each CRDS server (test or ops) has a full copy (\textasciitilde{}2T allocation) of all operational and historical (CRDS-only)
+reference files. The dev servers have a smaller allocation which is generally linked to /grp/crds
+(synced from ops servers) rather than internally stored.
 
@@
 
-\chapter{RC scripts}
-\label{server_guide:rc-scripts}
-The RC scripts are kept with the server source code in the directory ``hosts'' under the names dot\_setenv and
-rc\_script.
-
-\section{.setenv}
-\label{server_guide:setenv}
-The CRDS user runs under /bin/tcsh and executes .setenv for CRDS-server specific initializations.   Note that
-\$HOME/.setenv is shared across all CRDS servers and should be modified with extreme caution.
-
-\section{\$HOME/rc\_script}
-\label{server_guide:home-rc-script}
-The /home/crds/rc\_script is executed to restart the servers,  or shut them down,  whenever the server is rebooted.
-
 \chapter{Cron Jobs}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% crontab -l
+\PYGZpc{} crontab \PYGZhy{}l
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% crontab host/crontab
+\PYGZpc{} crontab \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZus{}server/host/crontab
 \end{Verbatim}
@@
 \section{monitor\_reprocessing}
-\label{server_guide:id2}
+\label{server_guide:monitor-reprocessing}
 Every 5 minutes CRDS\_server/host/monitor\_reprocessing looks for changes in the CRDS operational context and
@@
 \label{server_guide:maintenance-commands}
-Maintenance commands are typically run from the \textbf{\$CRDS/CRDS\_server directory},  the root of the CRDS\_server checkout.
+Maintenance commands are typically run from the root of the CRDS\_server checkout.   Changing to the CRDS\_server source
+directory can be done like this:
 
-The default Python environment does not include the CRDS server packages directory.   Many of the shell scripts
-described below are either generated by the \$\{CRDS\}/crds\_server/install script or are dependent on scripts and
-config files that are generated.   Hence, this section will only make sense in a CRDS server environment which has
-been initialized at least once.
+\begin{Verbatim}[commandchars=\\\{\}]
+\PYGZpc{} server \PYGZsh{} cd to the CRDS\PYGZus{}server source code checkout
+\PYGZpc{} pwd
+/crds/data1/dljwstcrdsv1/CRDS\PYGZus{}server
+\end{Verbatim}
+
+From here on,  we'll assume commands are executed from this directory.
+
+The default Python environment does not include the CRDS server packages directory.   Additional environment variables
+required to run the server and some scripts are sourced like this:
+
+\begin{Verbatim}[commandchars=\\\{\}]
+\PYGZpc{} source env.csh
+\end{Verbatim}
 
@@
 \label{server_guide:installing-the-server-application}
-Running the ./install script will perform many actions including regenerating the environment definition script
-\emph{\$\{CRDS\}/CRDS\_server/env.csh}.  Primarily ./install installs the \emph{crds} client and \emph{crds.server} packages into
+Running the \emph{./install} script will perform many actions including regenerating the environment definition script
+\emph{env.csh}.  Primarily \emph{./install} installs the \emph{crds} (core + client) and \emph{crds.server} packages into
 a server specific python directory which is added to PYTHONPATH automatically in \emph{env.csh}.  In addition ./install
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% ./install [hst\textbar{}jwst]  [django\textbar{}dev\textbar{}test\textbar{}prod]  \textbar{}\& tee install.\textless{}observatory\textgreater{}.\textless{}use\textgreater{}.err
+\PYGZpc{} ./install [hst\textbar{}jwst]  [django\textbar{}dev\textbar{}test\textbar{}prod]  \textbar{}\PYGZam{} tee install.\PYGZlt{}observatory\PYGZgt{}.\PYGZlt{}use\PYGZgt{}.err
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% server   \# alias to cd to server source directory
-\% ./install hst dev  \textbar{}\& tee install.hst.dev.err
+\PYGZpc{} ./install hst dev  \textbar{}\PYGZam{} tee install.hst.dev.err
 \end{Verbatim}
@@
 knows this server is for ``hst dev''.
+
+\section{CRDS Catalog Initialization}
+\label{server_guide:crds-catalog-initialization}
+Historically the CRDS server catalogs were initialized many times from existing CDBS and JWST references and
+the initial CRDS rules set.  \emph{./init} is rarely used anymore but may still be useful for setting up a Django local
+test environment, dubbed the ``django'' usecase.
+
+For the most part the ./init script is tasked with installing the server's initial copy of CRDS rules and initializing
+the CRDS file catalog (the crds.server.interactive.models Django database with 19000 CDBS references and CRDS rules):
+
+\begin{Verbatim}[commandchars=\\\{\}]
+\PYGZpc{} server   \PYGZsh{} alias to cd to server source directory
+\PYGZpc{} ./init [hst\textbar{}jwst] [django\textbar{}dev\textbar{}test\textbar{}ops]
+\PYGZlt{}enter password for test user\PYGZgt{}
+\end{Verbatim}
+
+\textbf{NOTE:}  At this stage \emph{./init} should not be run on the OPS servers.   For VM-based servers it
+has effectively been superceded by \emph{tools/restore\_server} and \emph{tools/mirror\_server}.
 
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% server   \# alias to cd to server source directory
-\% ./run
-\% ./stop
+\PYGZpc{} ./run
+\PYGZpc{} ./stop
 \end{Verbatim}
 
-\section{Re-installing the CRDS Server}
-\label{server_guide:re-installing-the-crds-server}
-Once the CRDS server has been initialized, the server can be stopped, updated/re-installed, and retarted with
-the \emph{rerun} command:
+The \emph{./run} script starts Apache (many httpd processes) and memcached after which the CRDS server should definitely
+be abvailable on it's private port (typically 8001).   The web proxy is provided by an independent system which
+is rarely-if-ever unavailable,  but which has historically had a random lag of about 1 minute to (by appearances)
+connect with the just started Apache.
+
+\section{Updating and Restarting}
+\label{server_guide:updating-and-restarting}
+Performing a server update generally revolves around stopping the server,  changing and reinstalling the Django
+application, and restarting the server.   This is encapsulated in the \emph{./rerun} script:
 
 \begin{Verbatim}[commandchars=\\\{\}]
-\% ./rerun
+\PYGZpc{} ./rerun
 \end{Verbatim}
 
-This process does not affect the server Python stack.
+This works by sequentially invoking other more basic scripts: ./stop, ./install, ./run.
+
+\emph{./rerun} produces a log file of the voluminous install output as install.\textless{}observatory\textgreater{}.\textless{}usecase\textgreater{}.err.  If things
+aren't working coherently,  check the install...err file to verify that no setup functions failed,  as might
+happen for a Python syntax error or database schema change.
+
+\textbf{NOTE:}  rerunning the server is an integral part of taking the sever offline and switching to the hidden backup port.
+Consequently,  activities such as running tests and mirroring should also be viewed as reinstalling the Django
+application.   The reinstall is innocuous because any differences in application source code should be very tightly
+controlled, related to switching ports only.   However,  it's still a significant hidden side effect to be aware of
+because it has obvious implications when performed on an dirty code base.
 
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% server   \# alias to cd to server source directory
-\% ./runtests
+\PYGZpc{} ./runtests
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% ./runtests interactive.tests.Hst.test\_index
+\PYGZpc{} ./runtests interactive.tests.Hst.test\PYGZus{}index
 \end{Verbatim}
@@
 
-The server unit tests are ponderous.  Eventually you may \emph{\textless{}control-c\textgreater{}} and leave behind a junk test
-database which blocks subsequent testing.  That can generally cleaned up,  with \textbf{extreme caution},  as follows
-for e.g. hst dev:
-
-\begin{Verbatim}[commandchars=\\\{\}]
-\% ./manage dbshell
-mysql\textgreater{} drop database test\_crds\_hst\_dev;
-\end{Verbatim}
+\textbf{NOTE:}    without special arrangements,  server self-tests should not be run on the operational servers.
+Self-tests are normally run on the dev and test servers during the nightly cron job at 3 am.
 
@@
 
-\section{CRDS catalog initializaton}
-\label{server_guide:crds-catalog-initializaton}
-Historically the CRDS server catalogs were initialized many times from existing CDBS and JWST references and
-the initial CRDS rules set.  \emph{./init} is rarely used anymore but may still be useful for setting up a Django local
-test environment, typically called a ``dev'' server except in CRDS the ``dev'' server is an actual VM so Django dev
-servers are referred to as ``django'' servers.
-
-For the most part the ./init script is tasked with installing the server's initial copy of CRDS rules and initializing
-the CRDS file catalog (the crds.server.interactive.models Django database with 19000 CDBS references and CRDS rules):
-
-\begin{Verbatim}[commandchars=\\\{\}]
-\% ./init [hst\textbar{}jwst] [django\textbar{}dev\textbar{}test\textbar{}ops]
-\textless{}enter password for test user\textgreater{}
-\end{Verbatim}
-
-\textbf{NOTE:}  At this stage \emph{./init} should not be run on the OPS servers.   For operational servers it
-has effectively been superceded by \textbf{tools/restore\_server} and \textbf{tools/mirror\_server}.
-
-\section{Starting the server}
-\label{server_guide:starting-the-server}
-The \emph{./run} script starts Apache (many httpd processes) and memcached after which the CRDS server should definitely
-be abvailable on it's private port (typically 8001).   The web proxy is provided by an independent system which
-is rarely-if-ever unavailable:
-
-\begin{Verbatim}[commandchars=\\\{\}]
-\% ./run
-\end{Verbatim}
-
-\section{Updating and Restarting}
-\label{server_guide:updating-and-restarting}
-Performing a server update often revolves around stopping the server,  changing and reinstalling the Django
-application, and restarting the server:
-
-\begin{Verbatim}[commandchars=\\\{\}]
-\% ./rerun
-\end{Verbatim}
-
-This works by sequentially invoking other more basic scripts: ./stop, ./install, ./run.
-
-\emph{./rerun} produces a log file of the voluminous install output as install.\textless{}observatory\textgreater{}.\textless{}usecase\textgreater{}.err.  If things
-aren't working coherently,  check the install...err file to verify that no setup functions failed,  as might
-happen for a Python syntax error.
-
-\section{Running Server Self-tests}
-\label{server_guide:running-server-self-tests}
 The server self-tests exercise most but not all of the Django interactive view code,  JSONRPC code, and basic database
@@
 
-\begin{Verbatim}[commandchars=\\\{\}]
-\% ./runtests   \# (in second terminal window if using a Django dev local server)
-\end{Verbatim}
-
-\textbf{NOTE:}    without special arrangements,  server self-tests should not be run on the operational servers.
-Self-tests are normally run on the dev and test servers during the nightly cron job at 3 am.
-
 \section{Django Management Commands}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% ./manage \textless{}additional parameters to manage.py\textgreater{}
+\PYGZpc{} ./manage \PYGZlt{}additional parameters to manage.py\PYGZgt{}
 \end{Verbatim}
@@
 \label{server_guide:command-line-server-debug}
-An Ipython shell can be started in either of these equivalent ways:
+An Ipython shell which runs in a context similar to the CRDS server can be started like this:
 
 \begin{Verbatim}[commandchars=\\\{\}]
-\% ./manage shell
+\PYGZpc{} ./manage shell
+In [1]:
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% ./manage dbshell  \# to open a SQL prompt to the CRDS server database
+\PYGZpc{} ./manage dbshell  \PYGZsh{} to open a SQL prompt to the CRDS server database
 ...
-mysql\textgreater{} ... SQL commands ...
+mysql\PYGZgt{} ... SQL commands ...
+\end{Verbatim}
+
+The server unit tests are ponderous.  Eventually you may \emph{\textless{}control-c\textgreater{}} and leave behind a junk test
+database which blocks subsequent testing.  That can generally cleaned up,  with \textbf{caution},  as follows
+for e.g. hst dev:
+
+\begin{Verbatim}[commandchars=\\\{\}]
+\PYGZpc{} ./manage dbshell
+mysql\PYGZgt{} drop database test\PYGZus{}crds\PYGZus{}hst\PYGZus{}dev;
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% tools/backup\_server
+\PYGZpc{} tools/backup\PYGZus{}server
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\% tools/restore\_server
+\PYGZpc{} tools/restore\PYGZus{}server
 \end{Verbatim}
@@
 For example,  to copy the test server (hst-crds-test, tlhstcrdsv1) down to the dev server (hst-crds-dev, dlhstcrdsv1),
-perform these steps.  First, optionally, on the source server:
+perform these steps.
+
+First, optionally, on the source server:
 
 \begin{Verbatim}[commandchars=\\\{\}]
-\# login tlhstcrdsv1
-\% server
-\% tools/backup\_server
+\PYGZsh{} login tlhstcrdsv1
+\PYGZpc{} server
+\PYGZpc{} tools/backup\PYGZus{}server
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\# login dlhstcrdsv1
-\% server
-\% tools/mirror\_server hst test https://hst-crds-test.stsci.edu \textbar{}\& tee mirror\_server.hst.test.err
+\PYGZsh{} login dlhstcrdsv1
+\PYGZpc{} server
+\PYGZpc{} tools/mirror\PYGZus{}server hst test https://hst\PYGZhy{}crds\PYGZhy{}test.stsci.edu \textbar{}\PYGZam{} tee mirror\PYGZus{}server.hst.test.err
 \end{Verbatim}

### 2014-07-17 docs/server_guide/build/latex/crds_server.tex
More server_guide.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@1564 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
-e.g. /ifs/crds/jwst/test/file\_cache
+e.g. /ifs/crds/jwst/test/file\_cache/\{config,mappings,references\}/\{hst,jwst\}
 \end{quote}
@@
 Each CRDS server (test or ops) has a full copy (\textasciitilde{}2T allocation) of all operational and historical (CRDS-only)
-reference files. The dev servers have a smaller allocation which is generally linked to /grp/crds
+reference files and rules. The dev servers have a smaller allocation which is generally linked to /grp/crds
 (synced from ops servers) rather than internally stored.

### 2014-07-18 docs/server_guide/build/latex/crds_server.tex
More server_guide
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@1570 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 \DeclareUnicodeCharacter{00A0}{\nobreakspace}
-\usepackage{cmap}
 \usepackage[T1]{fontenc}
@@
 \usepackage{multirow}
+
+\usepackage{enumitem}
+\setlistdepth{15}
 
@@
 \title{CRDS Server Documentation}
-\date{July 17, 2014}
+\date{July 18, 2014}
 \release{1.1}
@@
 
-\expandafter\def\csname PYG@tok@gd\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
-\expandafter\def\csname PYG@tok@gu\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
-\expandafter\def\csname PYG@tok@gt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
-\expandafter\def\csname PYG@tok@gs\endcsname{\let\PYG@bf=\textbf}
-\expandafter\def\csname PYG@tok@gr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
-\expandafter\def\csname PYG@tok@cm\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
-\expandafter\def\csname PYG@tok@vg\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\expandafter\def\csname PYG@tok@m\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\expandafter\def\csname PYG@tok@mh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\expandafter\def\csname PYG@tok@cs\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\colorbox[rgb]{1.00,0.94,0.94}{\strut ##1}}}
-\expandafter\def\csname PYG@tok@ge\endcsname{\let\PYG@it=\textit}
-\expandafter\def\csname PYG@tok@vc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\expandafter\def\csname PYG@tok@il\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\expandafter\def\csname PYG@tok@go\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.20,0.20,0.20}{##1}}}
-\expandafter\def\csname PYG@tok@cp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@gi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
-\expandafter\def\csname PYG@tok@gh\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
-\expandafter\def\csname PYG@tok@ni\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
-\expandafter\def\csname PYG@tok@nl\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
-\expandafter\def\csname PYG@tok@nn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
-\expandafter\def\csname PYG@tok@no\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
-\expandafter\def\csname PYG@tok@na\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@nb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@nc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
-\expandafter\def\csname PYG@tok@nd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
-\expandafter\def\csname PYG@tok@ne\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@nf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
-\expandafter\def\csname PYG@tok@si\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
-\expandafter\def\csname PYG@tok@s2\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@vi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\expandafter\def\csname PYG@tok@nt\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
-\expandafter\def\csname PYG@tok@nv\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
-\expandafter\def\csname PYG@tok@s1\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@gp\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
-\expandafter\def\csname PYG@tok@sh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@ow\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@sx\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
-\expandafter\def\csname PYG@tok@bp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@c1\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
-\expandafter\def\csname PYG@tok@kc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@c\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
-\expandafter\def\csname PYG@tok@mf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\expandafter\def\csname PYG@tok@err\endcsname{\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
-\expandafter\def\csname PYG@tok@kd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@ss\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
-\expandafter\def\csname PYG@tok@sr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
-\expandafter\def\csname PYG@tok@mo\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\expandafter\def\csname PYG@tok@mi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
-\expandafter\def\csname PYG@tok@kn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@o\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PYG@tok@kr\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@s\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@kp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@w\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
-\expandafter\def\csname PYG@tok@kt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
-\expandafter\def\csname PYG@tok@sc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@sb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@k\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
-\expandafter\def\csname PYG@tok@se\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
-\expandafter\def\csname PYG@tok@sd\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@gd{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
+\def\PYG@tok@gu{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
+\def\PYG@tok@gt{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.25,0.82}{##1}}}
+\def\PYG@tok@gs{\let\PYG@bf=\textbf}
+\def\PYG@tok@gr{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
+\def\PYG@tok@cm{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
+\def\PYG@tok@vg{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\def\PYG@tok@m{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\def\PYG@tok@mh{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\def\PYG@tok@cs{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\colorbox[rgb]{1.00,0.94,0.94}{##1}}}
+\def\PYG@tok@ge{\let\PYG@it=\textit}
+\def\PYG@tok@vc{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\def\PYG@tok@il{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\def\PYG@tok@go{\def\PYG@tc##1{\textcolor[rgb]{0.19,0.19,0.19}{##1}}}
+\def\PYG@tok@cp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@gi{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
+\def\PYG@tok@gh{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
+\def\PYG@tok@ni{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
+\def\PYG@tok@nl{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
+\def\PYG@tok@nn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
+\def\PYG@tok@no{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
+\def\PYG@tok@na{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@nb{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@nc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
+\def\PYG@tok@nd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
+\def\PYG@tok@ne{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@nf{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
+\def\PYG@tok@si{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
+\def\PYG@tok@s2{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@vi{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\def\PYG@tok@nt{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
+\def\PYG@tok@nv{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
+\def\PYG@tok@s1{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@gp{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
+\def\PYG@tok@sh{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@ow{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@sx{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
+\def\PYG@tok@bp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@c1{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
+\def\PYG@tok@kc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@c{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
+\def\PYG@tok@mf{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\def\PYG@tok@err{\def\PYG@bc##1{\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{##1}}}
+\def\PYG@tok@kd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@ss{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
+\def\PYG@tok@sr{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
+\def\PYG@tok@mo{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\def\PYG@tok@mi{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
+\def\PYG@tok@kn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@o{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\def\PYG@tok@kr{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@s{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@kp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@w{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
+\def\PYG@tok@kt{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
+\def\PYG@tok@sc{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@sb{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@k{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
+\def\PYG@tok@se{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
+\def\PYG@tok@sd{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
 
@@
 \def\PYGZca{\char`\^}
-\def\PYGZam{\char`\&}
-\def\PYGZlt{\char`\<}
-\def\PYGZgt{\char`\>}
 \def\PYGZsh{\char`\#}
@@
 \def\PYGZdl{\char`\$}
-\def\PYGZhy{\char`\-}
-\def\PYGZsq{\char`\'}
-\def\PYGZdq{\char`\"}
 \def\PYGZti{\char`\~}
@@
 This guide is intended to introduce the CRDS servers for the purposes of maintenance and emergency backup for Todd.
+Additional documentation about using CRDS and the servers can be located on the servers under the question mark icon
+at the top right each page.
 
@@
 Todd Miller:         primary CRDS and CRDS server application developer.
+
+\item {} 
+Pey-Lian Lim:        intial JWST cloned references and rules, jwst\_gentools branch
+
+\item {} 
+Jonathan Eisenhamer  table differencing and reprocessing implications
 
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ssh \PYGZhy{}A \PYGZhy{}t \PYGZdl{}1.stsci.edu /usr/bin/sudo /bin/su \PYGZhy{} crds
+\% ssh -A -t \$1.stsci.edu /usr/bin/sudo /bin/su - crds
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} crds\PYGZus{}server plhstcrdsv1
-\PYGZsh{} crds\PYGZus{}server \PYGZlt{}VM\PYGZhy{}hostname\PYGZgt{}
+\% crds\_server plhstcrdsv1
+\# crds\_server \textless{}VM-hostname\textgreater{}
 \end{Verbatim}
@@
 \hline
-\textsf{\relax 
+\textbf{
 observatory
-} & \textsf{\relax 
+} & \textbf{
 use
-} & \textsf{\relax 
+} & \textbf{
 host/vm
-} & \textsf{\relax 
+} & \textbf{
 direct port
-} & \textsf{\relax 
+} & \textbf{
 url
-}\\
-\hline
+}\\\hline
+
 hst
@@
 \href{http://localhost:8000}{http://localhost:8000}
-\\
+\\\hline
 
@@
 \href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
-\\
+\\\hline
 
@@
 \href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
-\\
+\\\hline
 
@@
 \href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
-\\
+\\\hline
 
@@
 \href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
-\\
+\\\hline
 
@@
 \href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
-\\
+\\\hline
 
@@
 \href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
-\\
-\hline\end{tabulary}
+\\\hline
+\end{tabulary}
 
@@
 
-See CRDS\_server/sources/site\_config.py to verify this information.
+See CRDS\_server/sources/site\_config.py to verify server configuration.
+
+\section{CRDS Client Configuration Scripts}
+\label{server_guide:crds-client-configuration-scripts}
+Configuring the client to work with various CRDS servers can be accomplished using scripts define in the CRDS client
+under trunk/envs:
+
+\begin{tabulary}{\linewidth}{|L|L|L|L|}
+\hline
+\textbf{
+Script
+} & \textbf{
+CRDS\_SERVER\_URL
+} & \textbf{
+CRDS\_PATH
+} & \textbf{
+Purpose
+}\\\hline
+
+default
+ & 
+\href{https://crds-serverless-mode.stsci.edu}{https://crds-serverless-mode.stsci.edu}
+ & 
+readonly /grp/crds/cache
+ & 
+Default no env, serverless jwst ops
+\\\hline
+
+env-forwarded.csh
+ & 
+\href{https://localhost:8001}{https://localhost:8001}
+ & 
+\$HOME/crds\_cache\_forwarded
+ & 
+ssh port forwarded private server
+\\\hline
+
+env-local.csh
+ & 
+\href{https://localhost:8000}{https://localhost:8000}
+ & 
+\$HOME/crds\_cache\_local
+ & 
+Django development server
+\\\hline
+
+hst-crds-dev.csh
+ & 
+\href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
+ & 
+\$HOME/crds\_cache\_dev
+ & 
+Connected hst dev local cache
+\\\hline
+
+hst-crds-test.csh
+ & 
+\href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
+ & 
+\$HOME/crds\_cache\_test
+ & 
+Connected hst test local cache
+\\\hline
+
+hst-crds-ops.csh
+ & 
+\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
+ & 
+\$HOME/crds\_cache\_ops
+ & 
+Connected hst ops local cache
+\\\hline
+
+jwst-crds-dev.csh
+ & 
+\href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
+ & 
+\$HOME/crds\_cache\_dev
+ & 
+Connected jwst dev local cache
+\\\hline
+
+jwst-crds-test.csh
+ & 
+\href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
+ & 
+\$HOME/crds\_cache\_test
+ & 
+Connected jwst test local cache
+\\\hline
+
+jwst-crds-ops.csh
+ & 
+\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
+ & 
+\$HOME/crds\_cache\_ops
+ & 
+Connected jwst ops local cache
+\\\hline
+
+crds-readonly.csh
+ & 
+\href{https://crds-serverless-mode.stsci.edu}{https://crds-serverless-mode.stsci.edu}
+ & 
+readonly /grp/crds/cache
+ & 
+Disconnected, complete ops cache
+\\\hline
+
+hst-crds-readonly.csh
+ & 
+\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
+ & 
+readonly /grp/crds/hst
+ & 
+Connected, complete ops cache
+\\\hline
+
+jwst-crds-readonly.csh
+ & 
+\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
+ & 
+readonly /grp/crds/jwst
+ & 
+Connected, complete ops cache
+\\\hline
+\end{tabulary}
+
+At present only connected clients can resolve symbolic/date-based contexts other than -operational.
+
+Even without env settings,  many tools can guess the appropriate cache and ops server url based on files.
 
@@
 \hline
-\textsf{\relax 
+\textbf{
 mailing list
-} & \textsf{\relax 
+} & \textbf{
 moderator
-} & \textsf{\relax 
+} & \textbf{
 purpose
-}\\
-\hline
+}\\\hline
+
 \href{mailto:crds@stsci.edu}{crds@stsci.edu}
@@
 comm between INS and CRDS team, also accidental use
-\\
+\\\hline
 
@@
 comm within CRDS delivery team, DSB, archive, pipelines
-\\
+\\\hline
 
@@
 common destination for affected datasets output
-\\
+\\\hline
 
@@
 little used,  new source address for affected datasets,  server details + news
-\\
+\\\hline
 
@@
 affected datasets output list, hst ops
-\\
+\\\hline
 
@@
 affected datasets output list, hst test
-\\
+\\\hline
 
@@
 affected datasets output list, jwst ops
-\\
+\\\hline
 
@@
 affected datasets output list, jwst test
-\\
-\hline\end{tabulary}
+\\\hline
+\end{tabulary}
 
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-CRDS\PYGZus{}PROJECT        jwst
-CRDS\PYGZus{}USECASE        dev
-CRDS\PYGZus{}SERVER         dljwstcrdsv1
+CRDS\_PROJECT        jwst
+CRDS\_USECASE        dev
+CRDS\_SERVER         dljwstcrdsv1
 CRDS                /crds/data1/dljwstcrdsv1
-PATH                /crds/data1/dljwstcrdsv1/CRDS\PYGZus{}server/host   /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11/bin
-CRDS\PYGZus{}STACK          /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
-CRDS\PYGZus{}AFFECTED...    jmiller@stsci.edu eisenhamer@stsci.edu
-CRDS\PYGZus{}IFS            /ifs/crds/jwst/dev
-CRDS\PYGZus{}FILE\PYGZus{}CACHE     /ifs/crds/jwst/dev/file\PYGZus{}cache
-CRDS\PYGZus{}SERVER\PYGZus{}FILES   /ifs/crds/jwst/dev/server\PYGZus{}files
-META\PYGZus{}PREFIX         /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
+PATH                /crds/data1/dljwstcrdsv1/CRDS\_server/host   /crds/data1/dljwstcrdsv1/crds\_stacks/crds\_11/bin
+CRDS\_STACK          /crds/data1/dljwstcrdsv1/crds\_stacks/crds\_11
+CRDS\_AFFECTED...    jmiller@stsci.edu eisenhamer@stsci.edu
+CRDS\_IFS            /ifs/crds/jwst/dev
+CRDS\_FILE\_CACHE     /ifs/crds/jwst/dev/file\_cache
+CRDS\_SERVER\_FILES   /ifs/crds/jwst/dev/server\_files
+META\_PREFIX         /crds/data1/dljwstcrdsv1/crds\_stacks/crds\_11
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZsh{}  Source code areas
-alias crds       \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZdq{}
-alias server     \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZus{}server\PYGZdq{}
-alias stack      \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}STACK\PYGZcb{}\PYGZdq{}
-alias installer \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/crds\PYGZus{}stacks/installer3/build\PYGZdq{}
-
-\PYGZsh{} Server maintenance areas
-alias logs       \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/server/logs\PYGZdq{}
-alias backups    \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/server/db\PYGZus{}backups\PYGZdq{}
-
-\PYGZsh{} CRDS code area
-alias libpython  \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/python/lib/python\PYGZdq{}
-
-\PYGZsh{} Server working data files areas
-alias deliveries \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/deliveries\PYGZdq{}
-alias catalogs   \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/catalogs\PYGZdq{}
-alias ingest     \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/ingest\PYGZdq{}
-alias file\PYGZus{}cache \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}FILE\PYGZus{}CACHE\PYGZcb{}\PYGZdq{}
-
-\PYGZsh{} Isilon and VM file systems
-alias ifs        \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}IFS\PYGZcb{}\PYGZdq{}
-alias data1      \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}\PYGZdq{}
+\#  Source code areas
+alias crds       "cd \$\PYGZob{}CRDS\PYGZcb{}/CRDS"
+alias server     "cd \$\PYGZob{}CRDS\PYGZcb{}/CRDS\_server"
+alias stack      "cd \$\PYGZob{}CRDS\_STACK\PYGZcb{}"
+alias installer "cd \$\PYGZob{}CRDS\PYGZcb{}/crds\_stacks/installer3/build"
+
+\# Server maintenance areas
+alias logs       "cd \$\PYGZob{}CRDS\PYGZcb{}/server/logs"
+alias backups    "cd \$\PYGZob{}CRDS\PYGZcb{}/server/db\_backups"
+
+\# CRDS code area
+alias libpython  "cd \$\PYGZob{}CRDS\PYGZcb{}/python/lib/python"
+
+\# Server working data files areas
+alias deliveries "cd \$\PYGZob{}CRDS\_SERVER\_FILES\PYGZcb{}/deliveries"
+alias catalogs   "cd \$\PYGZob{}CRDS\_SERVER\_FILES\PYGZcb{}/catalogs"
+alias ingest     "cd \$\PYGZob{}CRDS\_SERVER\_FILES\PYGZcb{}/ingest"
+alias file\_cache "cd \$\PYGZob{}CRDS\_FILE\_CACHE\PYGZcb{}"
+
+\# Isilon and VM file systems
+alias ifs        "cd \$\PYGZob{}CRDS\_IFS\PYGZcb{}"
+alias data1      "cd \$\PYGZob{}CRDS\PYGZcb{}"
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} crontab \PYGZhy{}l
+\% crontab -l
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} crontab \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZus{}server/host/crontab
+\% crontab \$\PYGZob{}CRDS\PYGZcb{}/CRDS\_server/host/crontab
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} server \PYGZsh{} cd to the CRDS\PYGZus{}server source code checkout
-\PYGZpc{} pwd
-/crds/data1/dljwstcrdsv1/CRDS\PYGZus{}server
+\% server \# cd to the CRDS\_server source code checkout
+\% pwd
+/crds/data1/dljwstcrdsv1/CRDS\_server
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} source env.csh
+\% source env.csh
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./install [hst\textbar{}jwst]  [django\textbar{}dev\textbar{}test\textbar{}prod]  \textbar{}\PYGZam{} tee install.\PYGZlt{}observatory\PYGZgt{}.\PYGZlt{}use\PYGZgt{}.err
+\% ./install [hst\textbar{}jwst]  [django\textbar{}dev\textbar{}test\textbar{}prod]  \textbar{}\& tee install.\textless{}observatory\textgreater{}.\textless{}use\textgreater{}.err
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./install hst dev  \textbar{}\PYGZam{} tee install.hst.dev.err
+\% ./install hst dev  \textbar{}\& tee install.hst.dev.err
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} server   \PYGZsh{} alias to cd to server source directory
-\PYGZpc{} ./init [hst\textbar{}jwst] [django\textbar{}dev\textbar{}test\textbar{}ops]
-\PYGZlt{}enter password for test user\PYGZgt{}
+\% server   \# alias to cd to server source directory
+\% ./init [hst\textbar{}jwst] [django\textbar{}dev\textbar{}test\textbar{}ops]
+\textless{}enter password for test user\textgreater{}
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./run
-\PYGZpc{} ./stop
+\% ./run
+\% ./stop
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./rerun
+\% ./rerun
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./runtests
+\% ./runtests
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./runtests interactive.tests.Hst.test\PYGZus{}index
+\% ./runtests interactive.tests.Hst.test\_index
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./manage \PYGZlt{}additional parameters to manage.py\PYGZgt{}
+\% ./manage \textless{}additional parameters to manage.py\textgreater{}
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./manage shell
+\% ./manage shell
 In [1]:
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./manage dbshell  \PYGZsh{} to open a SQL prompt to the CRDS server database
+\% ./manage dbshell  \# to open a SQL prompt to the CRDS server database
 ...
-mysql\PYGZgt{} ... SQL commands ...
+mysql\textgreater{} ... SQL commands ...
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} ./manage dbshell
-mysql\PYGZgt{} drop database test\PYGZus{}crds\PYGZus{}hst\PYGZus{}dev;
+\% ./manage dbshell
+mysql\textgreater{} drop database test\_crds\_hst\_dev;
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} tools/backup\PYGZus{}server
+\% tools/backup\_server
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZpc{} tools/restore\PYGZus{}server
+\% tools/restore\_server
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZsh{} login tlhstcrdsv1
-\PYGZpc{} server
-\PYGZpc{} tools/backup\PYGZus{}server
+\# login tlhstcrdsv1
+\% server
+\% tools/backup\_server
 \end{Verbatim}
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PYGZsh{} login dlhstcrdsv1
-\PYGZpc{} server
-\PYGZpc{} tools/mirror\PYGZus{}server hst test https://hst\PYGZhy{}crds\PYGZhy{}test.stsci.edu \textbar{}\PYGZam{} tee mirror\PYGZus{}server.hst.test.err
+\# login dlhstcrdsv1
+\% server
+\% tools/mirror\_server hst test https://hst-crds-test.stsci.edu \textbar{}\& tee mirror\_server.hst.test.err
 \end{Verbatim}
@@
 to a backup port so that it is unavailable while it transitions through various inconsistent states.
+
+\chapter{Delivery Troubleshooting}
+\label{server_guide:delivery-troubleshooting}
+This section discusses possible operational failure modes and how to handle them.   There are some comaratively simple
+problems which may be addressable on an emergency basis.   As a general rule,  for seemingly complex or uncertain
+procedures,  first mirror the OPS server to the DEV server,  then perfom the procedure on the DEV server,  then
+apply the proven procedure to the OPS server.   For improved certainty,  switch the DEV server to the OPS server
+source code branches (CRDS and CRDS\_server),  rerun,  and then perform the procedure on the DEV server.
+
+\section{Remedy by Backup}
+\label{server_guide:remedy-by-backup}
+For some failure modes it may be desirable to restore the server to the nightly backup for the previous day.  See
+\emph{restore\_server} above.
+
+\textbf{NOTE:}  requires server database and file store changes,  restart.
+
+This approach might be particularly effective for temporarily bypassing failed deliveries
+by one instrument so that others can proceed,  and also for cleaning up new or failed CRDS rules which are known to
+be non-viable.   If failed CRDS rules have already been transferred to the archive,  either removing them from the
+archive must be coordinated with DSB and the CRDS Archiving Pipeline,  or restore\_server should not be performed and
+the files should be Marked Bad in CRDS instead.   See the CRDS user's guide (on the server) for information about
+marking files as bad.
+
+\section{Rmap or Context Fix Required}
+\label{server_guide:rmap-or-context-fix-required}
+Potentially a best references assignment error could be detected which requires a rules fix.
+
+\textbf{NOTE:} should be possible without OPS server changes.
+
+The procedure for fixing rules should basically be:
+\begin{enumerate}
+\setcounter{enumi}{-1}
+\item {} 
+Mirror OPS to DEV server and work using the DEV server.
+
+\item {} 
+Sync or download a copy of the rmap file requiring changes.
+
+\item {} 
+Correct the rules and test locally using elevated verbosity.  --verbose or --verbosity=100 or something in between.
+
+\item {} 
+Upload the modified rmap using Submit Mappings and check ``Generate Context'' to create new instrument and pipeline
+mappings which include the new context.
+
+\item {} 
+DEV servers do not archive and rules are immediately sync'able and useable.   Sync to a local cache and test.
+
+\item {} 
+When satisfied that the DEV server is working,  repeat for the OPS server.  Very possibly the original fixed
+copy of the .rmap is directly submissible to OPS.
+
+\item {} 
+When the OPS systems have successfully archived the new rules,  test them by syncing and running bestrefs.
+The default readonly cache at /grp/crds/cache should sync within 15 minutes of archiving.
+
+\item {} 
+Inform \href{mailto:crds\_team@stsci.edu}{crds\_team@stsci.edu} that you think the new rules are working and should either receive a second
+opinion or be made operational by the pipeline,  basically Richard Spencer performing Set Context on the
+web site.
+
+\end{enumerate}
+
+Context fixes (imap's and pmap's) need to be performed manually,  typically without automatic renaming.   New Context
+files are still submitted using Submit Mappings,  but without file renaming or context generation.
+
+\section{Improper Reference File Constraint}
+\label{server_guide:improper-reference-file-constraint}
+Valid reference files may be rejected due to overly stringent or incorrect matching parameter constraints.
+
+\textbf{NOTE:} requires OPS server file updates, reinstall, and restsart.
+
+The synposis of the fix is to modify the appropriate .tpn and/or \_ld.tpn file in crds.hst.tpns and update and
+restart the server.
+
+It's possible that the reference file constraints defined in the CRDS observatory packages will be overly stringent
+causing the submission of a valid file to fail.   For HST,  reference constraints are defined in the crds/hst/tpns
+directory and define two phases of reference file symbolism.   The first phase,  defined by .tpn files for each
+instrument-specific type,  defines reference parameters as they appear in the reference file.  The second phase,
+defined by \_ld.tpn files,  define reference parameters as expanded in rmaps by rules in crds.hst.substitutions.
+In this scenario,  errors or missing values in the .tpn's need to be fixed.
+
+\section{Improper Reference Parameter Expansion}
+\label{server_guide:improper-reference-parameter-expansion}
+Valid reference files may be inserted into their corresponding .rmap incorrectly,  most probably identified
+by certify warnings about new match tuples in the updated .rmap.
+
+\textbf{NOTE:} requires OPS server file updates, reinstall, and restsart.
+
+The synposis for the fix is to modify substutions.dat in crds.hst,  reinstall the server, and restart.
+
+For HST, reference file matching parameters define where the reference is inserted into .rmaps.
+During the reference insertion process,  reference file parameters are expanded using context-sensitive expansion
+rules defined in crds/hst/substitutions.dat.  Deficiencies in those rules will result in references being added
+to the wrong rmap matching paths.   The short term fix would be to modify substitions.dat,  manually test the rmap
+update proces, the resulting rmap, and finally adjusted best references.
+
+\section{Table Row Change Warnings}
+\label{server_guide:table-row-change-warnings}
+Submission of a new table reference file may result in certify warnings due to comparison with the old version
+of the table and deletion of rows.
+
+\textbf{NOTE:}  make it clear warnings are approximate, tripwires, then verify file differences and confirm or cancel.
+
+It should be noted that the warnings are approximate and advisory,  not  definitive.   With that in mind,  verify with
+the submitters and/or reference developers that the noted differences are not a problem,  then proceed with
+confirmation or rejection.  Row modifications may be perceived by certify as deletions and additions rather than as
+replacements.
 

### 2015-10-02 sources/interactive/common.py
Switched display_result to unprivileged uuid instead of authenticated-only id
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2115 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -25,6 +25,9 @@ LIST_GLOB_RE = re.compile(complete_re(r"[A-Za-z0-9_\.\*\+\(\)\-\[\]]{1,128}"))
 INSTRUMENT_RE = re.compile(complete_re(r"[A-Za-z0-9_]{1,64}"))
 FIELD_RE = re.compile(complete_re(r"[A-Za-z0-9_]{1,64}"))
 
+UUID_RE_STR = r"[A-Za-z0-9]{8}\-[A-Za-z0-9]{4}\-[A-Za-z0-9]{4}\-[A-Za-z0-9]{4}\-[A-Za-z0-9]{12}"
+UUID_RE = re.compile(complete_re(UUID_RE_STR))
+
 # ===================================================================
 
 def capture_output(func):

### 2015-10-02 sources/interactive/models.py

@@ -1553,8 +1553,10 @@ class RepeatableResultBlob(BlobModel):
     class Meta:
         db_table = TABLE_PREFIX + "_results" # rename SQL table
         
-    repr_list = unicode_list = ["id","page_template"]
+    repr_list = unicode_list = ["id","name", "page_template"]
 
+    unicode_list = ["id", "name", "page_template"]
+    
     blob_fields = dict(
         # User supplied fields
         parameters_enc = BlobField(
@@ -1563,11 +1565,10 @@ class RepeatableResultBlob(BlobModel):
             r"\w+\.html", "HTML template which will be rendered using parameter dictionary", ""),
     )
 
-    unicode_list = ["id", "page_template"]
-    
     @classmethod
     def new(cls, page_template, parameters):
         self = cls()
+        self.name= uuid.uuid4()
         self.page_template = page_template
         if "disposition" not in parameters:
             parameters["disposition"] = ""  # confirm/cancelled has happened (not)
@@ -1575,6 +1576,10 @@ class RepeatableResultBlob(BlobModel):
         self.save()
         return self
     
+    @property
+    def uuid(self):
+        return self.name
+
     @property
     def parameters(self):
         """return garbage-can dict of page template parameters"""
@@ -1595,7 +1600,7 @@ class RepeatableResultBlob(BlobModel):
     @property
     def repeatable_url(self):
         "Return the URL which can be used to display this persistent result."
-        return "/display_result/" + str(self.id)
+        return "/display_result/" + str(self.uuid)
 
 # =============================================================================
 

### 2015-10-02 sources/interactive/views.py

@@ -715,14 +715,12 @@ def index(request):
 
 @error_trap("base.html")
 @log_view
-@login_required
 def display_result(request, results_id):
     """Render the repeatable result with `results_id`.  Handle the /display_result/ URL."""
-    results_id = int(results_id)
     try:
-        result = models.RepeatableResultBlob.get(results_id)
+        result = models.RepeatableResultBlob.load(results_id)
     except Exception, exc:
-        raise CrdsError("Error loading result " + str(results_id) + " : " + str(exc))
+        raise CrdsError("Error loading result", results_id, ":", str(exc))
     pars = result.parameters
     pars["results_id"] = results_id  # needed to implement "disposition", confirmed or cancelled.
     return crds_render(request, result.page_template, pars)

### 2015-10-02 sources/urls.py

@@ -8,7 +8,7 @@ import crds.server.jsonapi.views
 import crds.server.interactive.views
 
 from crds.server import settings, config
-
+from crds.server.interactive.common import UUID_RE_STR
 from crds.config import FILE_RE_STR
 
 # XXX Cached views must be completely defined by the URL
@@ -89,7 +89,7 @@ urlpatterns = patterns('',
     url(r'^display_context_history/$', 
         crds.server.interactive.views.display_context_history),
                          
-    url(r'^display_result/(?P<results_id>\d+)$', 
+    url(r'^display_result/(?P<results_id>{0})$'.format(UUID_RE_STR), 
         'crds.server.interactive.views.display_result'),
                        
     url(r'^edit_context_history/(?P<history_id>\d+)/{0}/$'.format(FILE_RE_STR), 

### 2015-10-03 sources/configs/database.b5it.jwst.py
Switched to B5/6 I&T MySQL servers for Django
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2118 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -6,8 +6,8 @@ DATABASES = {
         'NAME': 'crds_jwst_b5it',
         'USER': 'jwstcrds',                      # Not used with sqlite3.
         'PASSWORD': DBWORD,              # Not used with sqlite3.
-        'HOST': 'tanops.stsci.edu',             # Set to empty string for localhost. Not used with sqlite3.
-        'PORT': '33306',                      # Set to empty string for default. Not used with sqlite3.
+        'HOST': 'iljwdmsbcrdsdbv.stsci.edu',             # Set to empty string for localhost. Not used with sqlite3.
+        'PORT': '3306',                      # Set to empty string for default. Not used with sqlite3.
         "OPTIONS": {
            'init_command': 'SET storage_engine=INNODB;',
         },

### 2015-10-03 sources/configs/database.b6it.jwst.py

@@ -6,8 +6,8 @@ DATABASES = {
         'NAME': 'crds_jwst_b6it',
         'USER': 'jwstcrds',                      # Not used with sqlite3.
         'PASSWORD': DBWORD,              # Not used with sqlite3.
-        'HOST': 'tanops.stsci.edu',             # Set to empty string for localhost. Not used with sqlite3.
-        'PORT': '33306',                      # Set to empty string for default. Not used with sqlite3.
+        'HOST': 'iljwdmsbcrdsdbv.stsci.edu',             # Set to empty string for localhost. Not used with sqlite3.
+        'PORT': '3306',                      # Set to empty string for default. Not used with sqlite3.
         "OPTIONS": {
            'init_command': 'SET storage_engine=INNODB;',
         },

### 2015-10-04 sources/jsonapi/tests.py
Updated min reference  count for HST test.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2119 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -299,7 +299,7 @@ class ServiceApiBase(object):
     def test_client_get_reference_names(self):
         references = client.get_reference_names(self.pmap)
         self.failUnless(self.min_reference_count < len(references))
-        
+
 # ===========================================================================
 # ===========================================================================
 
@@ -310,7 +310,7 @@ if server_config.observatory == "hst":
         pmap1 = "hst_0001.pmap"
         pmap_date = "hst-2013-07-04T00:00:00"
         imap = "hst_wfc3.imap"
-        min_reference_count = 30000
+        min_reference_count = 20000
 
         observatory = server_config.observatory
         

### 2015-10-04 sources/jsonapi/tests.py
Corrected HST min reference names len.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2120 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -310,7 +310,7 @@ if server_config.observatory == "hst":
         pmap1 = "hst_0001.pmap"
         pmap_date = "hst-2013-07-04T00:00:00"
         imap = "hst_wfc3.imap"
-        min_reference_count = 20000
+        min_reference_count = 14000
 
         observatory = server_config.observatory
         

### 2015-10-04 docs/paper/crds.tex
partially completed translation to latex, included screenshots
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2121 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

%% This is file `elsarticle-template-2-harv.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%%
%% $Id: elsarticle-template-2-harv.tex 155 2009-10-08 05:35:05Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-2-harv.tex $
%%

%%\documentclass[preprint,authoryear,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:

%% Astronomy & Computing uses 5p
%% \documentclass[final,authoryear,5p,times]{elsarticle}
\documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
\usepackage{gensymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

\usepackage[pdftex,pdfpagemode={UseOutlines},bookmarks,bookmarksopen,colorlinks,linkcolor={blue},citecolor={green},urlcolor={red}]{hyperref}
%% Draft mode for editing
%\usepackage[pdftex,pdfpagemode={UseOutlines},bookmarks,bookmarksopen,colorlinks,linkcolor={blue},citecolor={green},urlcolor={red},draft]{hyperref}

% \usepackage{hypernat}

\usepackage{tikz}
\usetikzlibrary{arrows,calc}
\newcommand{\tikzmark}[1]{%
  \tikz[overlay,remember picture] \node (#1) {};}

\usepackage{breakurl}

\usepackage{listings}

\usepackage{caption}

\lstset{
  basicstyle=\ttfamily,
  showstringspaces=false,
  stringstyle=\color{red},
  morecomment=[l]{/},
  commentstyle=\color{blue},
}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon (default)
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   authoryear - selects author-year citations (default)
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%   longnamesfirst  -  makes first citation full author list
%%
%% \biboptions{longnamesfirst,comma}

% \biboptions{}

\journal{Astronomy \& Computing}

%% Upright single quotes in verbatim fields make FITS header examples
%% much more readable
\usepackage{upquote}

%% For draft use color package to indicate open questions that need
%% clarification
\usepackage{color}

%\defcitealias{2015Jenness}{Paper~II}
%\defcitealias{2014Kitaeff}{Paper~III}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{The Calibration Reference Data System}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[stsci]{Perry~Greenfield}
\ead{perry@stsci.edu}
\author[stsci]{J.~Miller}

\cortext[cor1]{Corresponding author}
\address[stsci]{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

\begin{abstract}
%% Text of abstract

We describe a software architecture and implementation for using rules to
determine which calibration files are appropriate for use in calibrating a
given observation. This new system replaces what had been previously used for
the Hubble Space Telescope (HST) calibration pipelines, a system called the
Calibration Database System (CDBS), and will be used for the James Webb Space
Telescope (JWST) calibration pipelines, and is currently being used for HST calibration pipelines. . The approach used for this can be
easily generalized for use in similar applications that need a rules-based
system for selecting the appropriate file for a given case; we give some
examples of such generalizations that will likely be used for JWST. The core
functionality of the Calibration Reference Data System is available under an
Open Source license.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

FITS \sep
File formats \sep
Standards \sep
World Coordinate System

\end{keyword}

\end{frontmatter}

% \newcommand{\ascl}[1]{\href{http://www.ascl.net/#1}{ascl:#1}}
\newcommand{\aspconf}{ASP Conf.\ Ser}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\jrasc}{JRASC}
\newcommand{\qjras}{QJRAS}
\newcommand{\mnras}{MNRAS}
\newcommand{\pasp}{PASP}
\newcommand{\pasa}{PASA}
\newcommand{\apjs}{ApJS}

%% main text
\section{Introduction}

When running automatic calibration pipelines one important capability needed is
the ability to identify automatically the appropriate calibration files that
should be used when calibrating the data. The kinds of calibration files are
typically numerous, and there may be many that have to be applied to a specific
dataset. Examples are dark current, bias, flat field, photometric, and
geometric distortions, among many others. Typically calibration files depend on
particular observing modes or parameters, or may be time variable.
Calibration files also differ across instruments both in purpose and specific 
instantiations of a particular reference type.

\section{Prior Solution}

The system that was used for the Hubble Space Telescope (HST) was called the
Calibration Database System (CDBS). It was used successfully for many
years. The experience with it revealed that there were some limitations that
proved to constrain its capabilities, and as a result, a newer system that
removed these constraints was sought. We will briefly describe the design of
CDBS at a high level and the constraints that it posed. This provides the
necessary background for discussing the design goals of CRDS.

The basic design of CDBS was centered around a database that contained
information on each reference file (the generic STScI term for files used to
calibrate data whether they be flat fields, darks, or file containing
appropriate parameters to use in calibration). Typically the database contained
information about the relevant observational parameters (mostly instrument mode
settings and date of applicability). At the highest level, the basic approach
was to run a program for each new dataset being processed (or reprocessed as
the case may be) that essentially performed a query on the database for each
type of reference file needed. The result of the query was a specific reference
filename that would then be set as the value of a particular keyword in the
dataset's header for use by the calibration pipeline.

The calibration pipelines retrieved the names of the appropriate reference
files from the dataset's header, and used those to open that reference file
for use in calibration. The reference files were kept in a standard location in
the pipeline processing system. The program that updated the headers with the
selected references files was called ``bestref.''

In reality, there was much more to CDBS than what has been briefly
described. The system handled the addition of new reference files, first by
validating the files met certain requirements, and then the archiving of those
submitted files. The process for submitting new files involved a good number of
manual steps and checks. One goal of the replacement system was to streamline
the submission process somewhat.

The most critical aspect of the validation requirements for reference files
concerned the keyword values used to match datasets to the appropriate
references.  Unlike dataset parameter keywords which describe a specific
instrument configuration for one observation, reference file keywords
circumscribe range of parameter values for which the reference applies.  In
CDBS, ranges of parameter values were often represented by intermediate values
which expand into the discrete values used to define specific instrument
configurations.  As part of submitting reference files, the intermediate values
were combinatorially exploded into database rows which represented each
possible application of a reference to some discrete instrument parameter
configuration.  As an example, a dataset APERTURE keyword would describe the
specific aperture an instrument was configured to use for one observation. In
contrast, the same APERTURE keyword specified in a reference file would
describe, indirectly, the combined set of different specific APERTUREs that
reference file was capable of supporting.  When multiple parameters were used
to match datasets to references, the number of distinct rows in the CDBS
database was equal to the product of the number of specific values supported by
a particular reference for each parameter.

Furthermore, there were occasions for which standard SQL queries were
insufficient for achieving the desired selection results. In such cases,
software was run to generate custom queries to get around such limitations.

CDBS was used for 24 years of HST's operation. During that period, upgrades and
enhancements were made to how it worked, but for the most part, the design did
not change in any major way.

\section{Limitations in CDBS}

Twenty four years provides a long time to learn about what could be
improved. This section highlights what issues proved the most problematic in
using CDBS.

\begin{enumerate}
\item Difficulty testing new reference files. The use of a database essentially
limited the system to one set of rules for selecting reference files. Once a
reference file was delivered to the system, effectively the rules for selection
were modified in the operation system immediately. There were occasions when
reference files were deemed to have passed functional testing (i.e., they
performed the correct calibration for the designated cases), but were submitted
with incorrect information about which modes or dates that they should be used
for. As a result, the operational pipeline would only discover that there was a
problem when processing real data, thus resulting in dealing with correcting
mis-processed data (or in some cases, failure to even process). Problems in the
operational pipeline are significant disruptions. In the last few years, a test
version of the database was created so that tests could be performed, but that
introduces synchronization and management issues to make sure what is being
tested corresponds to the previous operational version. Furthermore, if
multiple deliveries are in progress from different instruments, it introduces a
coordination issue to make sure they are either all completed together or in
sequence, which can prove constraining to the needs of each instrument as far
as testing goes.

\item Difficulty in undoing mistakes. A delivery of a file with mistaken
parameters could be difficult to undo. No reference file could be removed from
the database for various reasons. In a number of cases, particularly if the
date that it was targeted for was incorrect, it could seriously corrupt the
selection logic. To take the most common error case: Files often had a
``useafter'' date associated with them that indicated that it should be used for
a date after the specified one *if no other file had a later date that was
still before the date of the observation*. If one submitted a file intended to
be used for data after 2000-01-01 but mistakenly provided
1999-01-01 then two new file submissions are required to correct the problem.
One to resubmit the new file with the correct date; the second to resubmit the file
intended to be used after 1999-01-01 so that its useafter date is one second after
the mistaken submission.

There are other cases where one mistaken submission may require a series of
resubmissions of already submitted files to correct for the effect of the wrong
submission. One such example is if one mistakenly supplies a``wildcard'' for a
parameter that should only apply to one case. In this event, all the other
reference files intended for each of the other possible parameter values must
be resubmitted. This makes the potential effects of mistakes serious and thus
requires extreme care in submission.

\item Difficulty in supporting remote usage by astronomers. 
Using the bestref facility remotely
requires providing a web service so that remote processing can get the most up
to date recommendations on the best reference file to use. There is one serious
drawback in this though. Frequently the versions of the calibration software in
the operations pipeline have not yet been publicly released, and there are
times when the latest reference files require the latest software. Such a web
service has the potential of recommending reference files that either are
inappropriate for previous versions of the calibration pipeline software, or
simply will not work with previous versions. As a result, this service was not
provided.

\item Difficulty in allowing customized variants of selection rules. Sometimes
observers or teams have specialized calibration files that they wish to
substitute in place of the standard ones. There was no simple way of allowing a
team to run a customized version of CDBS to support this. The entrenched
software requirements were too numerous (when one develops a system to run in
only one environment, dependencies on that environment easily become entrenched
in the system). Even if no customization was desired, it makes running the
calibration pipeline remotely at another institution very difficult since there
is no simple way to get the the most recent recommendations.

\item Difficulty in providing remote pipelines a consistent bestref
environment. There are times observers *do not* want changing references files
if they wish comparison to previously computed results. They want the same
rules applied, even if they aren't the very best version.
As a ``single state'' database expressing only the current best reference
assignment rules, reproducing historical results in CDBS was difficult or
impossible.

\item Difficulty in understanding what the effective rules are. The exact
selection rules are embodied in a database with a history of transactions for
which many supersede previous ones. One really only knows the net effect by
running queries on the database for specific cases, even when something quite
simple could summarize what is desired for the current situation. The net
effect of this is that people do not really understand what the rules are, and
that they are not what was intended. Finding mistakes in this situation can be
quite difficult. And once found, can be difficult to rectify.

\item Difficulty in adding new kinds of selection rules. The database schema
effectively constrains what kinds of rules can be used. More complex rules
either lead to horrendously complex queries, or custom software to generate
custom queries. The use of the custom software/queries ends up making the system
even more opaque.
\end{enumerate}

\section{The Crux of a Different Approach}

It became apparent that many of the limitations ultimately came down to the
dependence on a database as the repository for the selection rules. This has a
number of drawbacks in this particular application:

\begin{enumerate}
\item Databases are effectively one state systems. Yes, one can deal with
multiple states but usually at great complexity.
\item Databases do not make it simple to distribute software since installing,
administering and maintaining a database elsewhere is a major task, and keeping
them synchronized to the master copy is yet a greater complexity
\item Once established, changing the structure of database is difficult,
particularly with a systems used in operations.
\end{enumerate}

Is it in fact necessary to use a database to hold the rules? In reviewing all
the previous and anticipated cases for HST and JWST, it did not appear that a
database was necessary for selection rules, and that a simpler and more
flexible approach could be chosen. Indeed, all that appears to be needed is to
encompass a version of the rules in a simple text file. In doing so there are a
number of immediate benefits:

\begin{enumerate}
\item the rules are explicit
\item multiple versions of these rules may exist without conflict, and used in
different contexts simultaneously without confusion.
\item these rule files may be easily distributed so that remote users can run the
``bestref'' functionality remotely without needing to install or administer
complex software.
\item the rules are easily customized, even by hand if necessary if
users wish to.
\end{enumerate}

\section{High level organization of CRDS}

The software for CRDS can be considered to be in one of three categories:

\begin{enumerate}
\item supporting the bestref functionality
\item supporting submitting new reference files and all the issues that
go with that
\item Supporting format, semantic, and parameter constraint checking for both
references and rules files.  Capability to detect typos, duplicate lines, and
grammatical errors in rules files.   Capability to analyze basic properties
such duplicate or deleted rows,  by pseudo-mode, for supported tables files.
\item providing utilities for making CRDS useful in operations, for instrument
scientists that must generate and monitor reference files, and end users.
\end{enumerate}

Each of these will be described in a separate section. Since most of the design
is centered around the first category, most of the description will be centered
around that.

\section{Bestref Functionality}

\subsection{Design}

The system is centered around rules files that describe (for one version) 
how reference files should be selected for a single type of
reference file. In a general sense, the file consists of a header of sorts that
describes information about what kind of reference file that it is applied to,
what the relevant information from the dataset is needed to make that
selection, and other bookkeeping information. Following that header are the
rules. Generally these are nested sets of criteria that are used to
successively narrow down the selection until a single result is determined. It
is important to understand that there is no intrinsic limit to what structures
can be supported. If more complex cases arise, new structures can be added to
the library to support these. The following lists existing and possible kinds
of selections structures. Those that already are supported are marked with an
`*'. The ones that are not supported are intended to illustrate possible
extensions that are not purely hypothetical. The following examples of files
will illustrate specifically these structures.

\begin{enumerate}
\item matching on sets of discrete parameter values. That is, the item associated
with this specific set of parameters is selected if the parameter values are
matched according to one of several matching approaches. An item may be a file
name, or a nested set of rules that will be evaluated in turn.  
There are a number of different parameter match types, literal, or-glob,
pure regex, between, not, relational, etc.  In the case of multiple parameters,
each parameter is matched across all match cases using a process of elimination
(winnowing) which successively narrows the possible match cases.

\item matching on a sequence of dates. This corresponds to the useafter mechanism
in CDBS. Normally these items will be sorted in date/time order, and the
date/time of the observation is used to select the appropriate item in the list
using a binary search.

\item matching software version requirements. This structure indicates selection
based on versions of the software which item should be selected. It may use
specific versions, or relative (e.g., any version before or up to the specified
version, or any version after the specified version).

\item getting bracketing files. This is useful if some sort of interpolation
between reference files is desired, in which case a pair of results is
returned.

\item matching on ranges of non-discrete values. For example, this may select a
file if an observational parameter is in the specified range. Normally, this
would be a one-dimensional selection, though even more complex multidimensional
volumes could be constructed if need be.
\end{enumerate}

\subsection{Examples}

xxx example 1 (highlighting a \& b)

\begin{figure*}
\centering
\begin{verbatim}
selector = Match({
    ('MIRIFULONG', 'FAST', 'FULL') : UseAfter({
        '2015-01-27 12:05:34' 'jwst_miri_dark_0029.fits',
        '2015-03-22 00:29:01' 'jwst_miri_dark_0032.fits',
        '2015-04-07 09:14:00' 'jwst_miri_dark_0047.fits',
        ...
        }),
    ('MIRIFUSHORT', 'SLOW', 'FULL') : UseAfter({
        '2015-01-25 12:06:34' 'jwst_miri_dark_0099.fits',
        '2015-03-21 00:28:01' 'jwst_miri_dark_0101.fits',
        '2015-04-08 09:13:00' 'jwst_miri_dark_0127.fits',
        ...
        }),
        ...
})
\end{verbatim}
\caption{xxx}
\end{figure*}

xxx example 2 adding c
\begin{figure}
\begin{verbatim}
selector = SelectVersion({
   '<3.1':    'jwst_miri_flat_0065.fits',
   '<5':      'jwst_miri_flat_0073.fits',
   'default': 'jwst_miri_flat_123.fits',
})
\end{verbatim}
\end{figure}

xxx example 3 illustrating d

\begin{figure}
\begin{verbatim}
selector = Bracket({
    1.2: "cref_flatfield_120.fits",
    1.5: "cref_flatfield_124.fits",
    5.0: "cref_flatfield_137.fits",
})
\end{verbatim}
\end{figure}

Here, a parameter value of 1.3 returns the value:

\begin{verbatim}
('cref_flatfield_120.fits', 'cref_flatfield_124.fits')
\end{verbatim}

xxxx example 4 illustrating e

\begin{verbatim}
selector = Match({
    ('WFC', 'N/A', 'BETWEEN 1220 1530', 'FR782N') :  "hst_wfc3_flatfile_0027.fits",
    ('WFC', 'N/A', 'BETWEEN 1530 1690', 'FR782N') :  "hst_wfc3_flatfile_0028.fits",
    ...
})
\end{verbatim}

Here a wavelength of 1300 (between 1220 and 1530) results in the partial match
of

\begin{verbatim}
'hst_wfc3_flatfile_0027.fits' and eliminates 
"hst_wfc3_flatfile_0028.fits"
\end{verbatim}

as a candidate.   Since BETWEEN can be used in an arbitrary Match parameter
slot,  potentially multiple times,  volumes can be described, and also
described in concert with other types of match syntax for other parameters
such as wildcard matching or regular expressions.

XXXXXXX I think the capabilities of (e) are actually folded into Match()
described in (a),  where each individual parameter of a match case can use
one of several match syntaxes.   Further,  there is no requirement that the
match expressions of the same parameter use the same method across all cases,
and indeed it is common to use N/A which is a specialized kind of match.

\begin{verbatim}
XXXX I documented all this stuff here:

XXXX   https://jwst-crds.stsci.edu/static/users_guide/rmap_syntax.html#selectors
\end{verbatim}

XXXX By far the most common match syntax used is the literal-value-or-glob,
including the degenerate case of a single literal value.  Unlike CDBS which had
discrete rows for every combination of discrete parameter values, CRDS
summarizes the combinatorial explosion of parameter possibilities into a single
concise multi-parameter expression by virtue of the matching syntax.  It is far
more comprehensible to look at one multi-parameter match expression with
or-globs than it is to scan 60 or 100 simple rows in the CDBS database.
Another common match expression is N/A.  BETWEEN has also been used.

\subsection{Hierarchical Organization}

The system is based on these files (which we refer to rmap files since they
indicate the mapping to reference files) but also involves a hierarchy of
related files that are called context files, which provide a nested 
organizational structure corresponding to the functions at different levels. Essentially context files are
text files that define a set of related files that are to be used for
that configuration.
Instrument context files collect all the rmap files for that
instrument. This file effectively defines the versions of all the rmap files
for each reference file types that comprise the version of recommendations in
effect for that instrument. In the example of the instrument context file
below, one can see that each distinct rmap file has a unique name. If anything
is changed in an rmap file, it gets a new name

xxx example of instrument context file

Likewise, there is a pipeline context file that lists the instrument context
files that define the versions in effect for the pipeline being run. As with
rmap files, instrument context files all have unique names. Any change of
content results in a new name for an instrument context file. Finally, the same
is true for pipeline context files. The net result is that a pipeline context
file deterministically identifies all the rules in use for a pipeline.

Note that one can run any number of pipeline environments, and each may use a
completely different pipeline context if need be, each of which will have some
sort of different rules for how reference files are selected.

xxx example of pipeline context file

This hierarchy is designed to match that for JWST and as such is currently
designed around the current levels of hierarchy. It is a possible generalization
that would allow it to deal with arbitrary levels of heirarchy, perhaps
different in number depending on the branch taken. Achieving that would
take significant modifications but is possible.

\subsection{Practicality and Restrictions of this design}

This approach assumes that the number of matching rules is reasonable for a
text file (e.g., fewer than 10,000 lines or so). It also assumes that the
number of versions of such files is reasonably bound (again, not more than a
few thousand). The most likely driver for the number of rules files versions is
the addition or modification of new reference files as a function of time. This has
been the case for HST, where it is not uncommon to generate new dark files for
every day. For a mission that may last a decade or more we are looking at
approximately 3-4 thousand if updated daily. In fact, HST updates the
configuration more infrequently (e.g., once a week even if there is a reference
file for each day).

In cases where updates are much more frequent, and the system that uses
them must be reconfigured after each update, CRDS may not be practical. This
may be the case where new calibration files are obtained every few minutes and
automatically turned into reference files for immediate use by a calibration
pipeline.

\subsection{Language independence}

This implementation has been done completely in Python. Although the rmap files
have a Python flavor to them (arguably it is more of a JSON flavor), nothing
requires this functionality to be performed in Python. To date Python has
proven fast enough to generate the bestref functionality, even for recomputing it
for large numbers of exposures, as is needed to determine which datasets must
be reprocessed as a result of changes to the configuration.

\section{Adding and updating reference files, rmaps and contexts}

While the design of the system is very much centered around how reference file
recommendations are made, that is hardly the only important aspect of the
system. How does one submit new files and ensure the integrity of the system as
the content evolves?

One of the important goals for CRDS was to streamline the process of submitting
new files while ensuring that files are well checked before committed, at least
for common use cases for new Reference files. A completely manual approach is
outlined here before addressing more automatic schemes. For the time being, the
details of how files are actually submitted is deferred to the next section

Supposing one or more new references files of a specific type for a specific
instrument are ready to be tested and used in the operations system/:

\begin{enumerate}
\item submit each of the reference files (with validation of each file
being part of the submission process). This is expected to generate
unique names for each of the submitted reference files
\item edit the rmap for that reference file type to include the necessary
changes to use these (most likely either a replacement of older versions
or the addition of time-variable ones).
\item submit the updated rmap file (again with implied validation for
correctness)
and again, generating a new, unique rmap file name that represents the version
of the file in the system that has the desired changes.
\item edit the instrument context file to use the new version of the rmap file.
\item submit the updated instrument context file (with validation and 
generating a new, unique name)
\item edit the pipeline context file to use the new version of the
instrument context file.
\item submit the updated pipeline context file (with validation and 
generating a new, unique name)
\end{enumerate}

At this point the new reference files can be used in an operational
context. Normally, it is expected that they will be tested on a test version of
the operations system by at least running the standard regression test suite
using the new configuration, perhaps with specific tests for the purpose of
testing the new reference files in use. These tests can be performed simply by
specifying a different pipeline context than the one currently being used in
operations, and without impacting the operations behavior.

When tests have been suitably passed, then the operations system can be updated
to use the new context. Should tests indicate that the new context has
problems, it can simply be ignored and never used. Presumably corrections will
be made to the reference files and the corresponding rules to generate a new,
correct context. However, if changes are made to the CRDS software itself,
something that happens frequently in its early stage of development and use,
it does require a separate test system to test updates to CRDS. Currently, 
deliveries always use the test environment, though it is expected that when
software updates are infrequent, the above model will be used for pure
reference file deliveries.

Since any number of context can exist, one can have several in testing
simultaneously. If that is the case, one still needs to be careful in
determining if different contexts need merging of information (as could happen
if different instruments are submitting new files independently).

For JWST, most instances of merging will be as simple as generating a
pipeline context that uses the appropriate instrument context (the items
most likely to be different; i.e., it is not expected that an instrument 
will be merging items at a lower level in the hierarchy).

In any case, if the operations system does end up using an incorrect pipeline
context, reversion to a previously good one is quite simple (something that
could be quite tricky in CDBS).

In the context of HST (see section xxx), reversion to prior sets of 
rules has been used to
support pipeline regression testing and coordinate CRDS with available
historical system states of the rest of the pipeline.

\subsection{Streamlined updates}

While this multi-step update process may be necessary in more complex cases, the
great majority of reference file submissions fall into one of two categories:
1) the replacement of existing references files (e.g., a better flat field) or
the addition of a reference file for a previously unsupported mode; or 2) the
addition of time-dependent references files to address data for specific time
ranges.

In either of these cases, it is quite useful to streamline the process to
effectively make it one step. Namely by the fact of submitting the reference
files, automatically updating and submitting the appropriate rmap to use it,
and in turn, making the corresponding updates and submissions to the context
files. As a result of these submissions, the user then is given all the
relevant names for the new reference files, rmap, and context files, most
importantly the pipeline context file. For this to work properly, the user must
indicate which pipeline context they are basing the changes on. Normally this
is the last one,  known as the ``edit context'' which can be modified several
times in advance of adopting the context as operational in the pipeline.

There are several other options as well:

\begin{itemize}
\item operational
\item one of last 10
\item user specified.  
\end{itemize}

Usually only the ``edit context'' is used, but the other choices
enable branching from a common ancestor.  Other activities which are
streamlined here are automatic file checking of reference and generated rules
files, collection of file metadata, and automatic version-to-version
differencing of the generated rules for inspection by the submitter and
verification that the intended changes have occurred prior to confirming
the submission.  Finally, it includes delivery of the files to the archive.

\subsection{Reference File submission details}

The machinery for submitting reference files is an interactive web-based
system. The ability to submit files or make changes requires user
validation. Figure xxx shows a screen shot of the home page of the CRDS
system, which is visible to the public. The submission capabilities 
are indicated in the xxx links in
xxx. Figure xxx shows the submission web page for updates for reference
files. This examples is for xxx.

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Public_Home_Page.png}
\caption{JWST CRDS Public Home Page}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Authenticated_Home.png}
\caption{JWST CRDS Authenticated User Home Page}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Batch_File_Submission.png}
\caption{JWST Batch File Submission Page}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Good_Submission_Review_Page_(after_confirmation).png}
\caption{JWST Good Submission Example}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Failed_Submission_DM_schema_violation.png}
\caption{JWST failed submission example}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Submission_Confirmed.png}
\caption{JWST submission confirmed example}
\end{figure*}

File submission is limited to authenticated users. The fully automatic
standard process is dubbed "Batch Reference
Submission" in reference to submission of a pile of files for one instrument,
multiple types,  and automatic certification and rules updates.

The user identifies the local files designated as the files to replace existing
ones. When all the updates have been identified, the submit button [or
whatever] is clicked, and CRDS will then validate each of the reference
files. If they all pass validation, the user will be presented the results of
the results that will be produced (e.g., the new filenames for the reference
files, rmaps and context files, and other summary information). An example of a
successful validation is shown in Figure xxx. At this point the user confirms
the submission after which they will be assigned unique names, added to the
CRDS database of reference files, sent to the STScI archive for archiving, and
placed in the disk-based repository of reference files. If the validation
doesn't pass, the results indicate what the problem is so the user may make the
necessary corrections. Figure xxx shows such a summary of problems.

The subsequent updates to rmap and context files also are validated, primarily
to ensure the syntax is correct.

\subsection{Reference File Validation}

This is handled by using the tools that the JWST pipeline use to validate the
reference files. These are based on data models that use JSON Schema (ref xxx)
to define the mandatory aspects of the data expected, including all the
expected data elements (whether arrays or tables), the allowable dimensionality
and datatype, and required metadata.

The required metadata includes information on who made the reference file, how
the reference file was made and related information (CRDS will also add
standard metadata related to the submission aspects, such as when the file was
submitted.)

There are further checks on file submissions that are intended to warn regarding
suspicious changes. These changes may be valid, but like indicate a mistake. The
following such situations raise a warning on submission:

\begin{enumerate}
\item The reversion of a file to a previous version. For example, 
if a rmap has an
existing reference file name replaced by one that is earlier in the submission
sequence, that would be unusual, and the submitter warned about this reversion.
Likewise if instrument or pipeline contexts point to earlier rmaps or instrument
contexts, respectively, that raises a warning.

\item If someone tries to commit files that were based on a pipeline context that
is no longer the latest, a warning will be raised. By doing so they may reverse
changes made by other instruments that have gotten into contexts after they
started making edits (this normally would not happen with streamlined submission
processes, but only when users are making submissions for individual components
thus raising the possibility they are bypassing subsequent changes).

\item other cases? xxx
\end{enumerate}

\section{Utilities}

Utilities are generally targeted to one or more of three classes of users:
Operations, Instrument Scientists (i.e., those that must create and maintain
reference files), and general users. Some utilities are useful for only one of
these classes of users whereas others may be more broadly useful. We will
organize this section by this class of users. Where a utility has other uses we
will indicate that.

\subsection{Operations}

Affected files utility: Given a list of datasets, determine which ones have
been affected by a change in a pipeline context. Normally it is expected that
the relevant selection parameters for each dataset is contained in a database
to avoid having to examine the contents of each dataset. This utility needs to
run in a reasonable amount of time since it may have to do this comparison for
hundreds of thousands of datasets. The inputs to the utility is a text list of
datasets, and the two pipeline contexts being compared. The results of this
can be used to determine which datasets must be reprocessed to take advantage
of any improved reference files.

Active reference files in a context: List all reference files used in a
pipeline context. This indicates what files may be needed to process the
data. (possibly useful for other classes of users)

\begin{verbatim}
% python -m crds.list --contexts 
     jwst_0059.pmap --references
jwst_fgs_gain_0000.fits
jwst_fgs_gain_0001.fits
jwst_fgs_ipc_0001.fits
jwst_fgs_ipc_0002.fits
jwst_fgs_linearity_0004.fits
jwst_fgs_linearity_0005.fits
jwst_fgs_mask_0002.fits
jwst_fgs_mask_0003.fits
jwst_fgs_readnoise_0000.fits
jwst_fgs_readnoise_0001.fits
...
\end{verbatim}

Inverse mapping: Which rmaps and contexts use a specific reference file (e.g.,
if one finds that one was defective, identify all the pipeline contexts that
used that file so that users may be notified)?

\begin{verbatim}
% python -m crds.uses jwst_fgs_gain_0000.fits
...
jwst_0078.pmap
jwst_0079.pmap
jwst_0080.pmap
...
jwst_fgs_0003.imap
jwst_fgs_0004.imap
jwst_fgs_0005.imap
...
jwst_fgs_gain_0000.rmap
jwst_fgs_gain_0001.rmap
\end{verbatim}

\subsection{Instrument Scientists}

Difference in rules between two contexts: Summarize what has changed in the
rules between two pipeline or instrument contexts. This allows instrument
scientists to quickly identify the changes made.

\begin{verbatim}
% python -m crds.diff jwst_0080.pmap jwst_0081.pmap 
  --brief --squash-tuples
  jwst_miri_regions_0004.rmap 
  jwst_miri_regions_0005.rmap 
  -- MIRIFUSHORT 12 SHORT N/A 
  -- added Match rule for jwst_miri_regions_0006.fits
jwst_miri_0048.imap jwst_miri_0049.imap -- regions -- replaced jwst_miri_regions_0004.rmap with jwst_miri_regions_0005.rmap
jwst_0080.pmap jwst_0081.pmap -- miri -- replaced jwst_miri_0048.imap with jwst_miri_0049.imap
\end{verbatim}

\subsection{General users}

Compare retrieved data with current pipeline context: A user has downloaded
data and wishes to see what data may need to be re-retrieved since the
reference files it used are not the currently recommended ones. A variant on
this is to update the headers of the files with the newly recommended files
(though for the JWST pipelines, this isn't normally necessary). This typically
will be run remotely and thus need network access to the CRDS server.

\section{Technical implementation details}

All the software (aside from a limited amount of web interface tools) is
written in Python. The bestref functionality uses the following Python
libraries (i.e., what isn't part of the Python Standard Library
distribution). It was originally written to use Python 2, but has since been
updated to use Python 3. The server-side libraries have not been ported to 
Python 3 yet.

\subsection{Client side dependencies:}

\begin{itemize}
\item rules file checking uses the **Parsley** parser generator package to define a grammar capable of detecting duplicate lines (cut-and-paste errors)
  \begin{itemize}
  \item jwst\_lib.models, jwst\_lib.stpipe, jwst\_lib.modeling (STScI)
  \item PyYaml
  \item pyasdf (STScI)
  \item astropy
  \item numpy
  \end{itemize}
\end{itemize}

\subsection{Server-side dependencies:}

The web-based functionality uses the Django framework and the MySQL database
backend. The additional following libraries are used.

\begin{itemize}
\item Apache web server using the Python mod\_wsgi as the library interface.
\item django-file-upoad (source code subsumed into CRDS code with modifications):
  Used to  manage parallel file uploads, drag-and-drop, progress bars, data rate info,  remote file deletion,  pause/resume,  etc.)
\item django-locking (source code subsumed into CRDS code with modifications):
  This is database-backed resource locking used to provide ``instrument lock''
   to limit submissions to one person per instrument (to prevent concurrent 
   submissions).
\item django-json-rpc: Supports the interface between the server and clients.
\item django-dbbackup: Used to backup the database and mirror the database between
  different environments
\item pytz: timezone support
\item jQuery/jQuery-UI: web page interface support
\item DataTables: Table display and manipulation for jQuery
\item MochiKit: Javascript debug shell used by django-json-rpc.
\item memcached / libevent / python-memcached: supports cached results on server
\end{itemize}

\section{Limitations and Improvements}

Web uploads are capably (not perfectly) handled by the django-file-upload
system which is fully integrated with the CRDS code base.  An end-to-end
checksum (sha1sum-based) verification of file uploads would be desirable
for extremely large
(DVD-sized) files.  Direct copies to the CRDS server file upload directories
can be used to bypass inefficient (and potentially less reliable) remote
web-based file uploads.

A significant design issue exists with processing and ingesting unbounded
amounts of data in a single file submission and web transaction.  
The primary limitation of large numbers of files and/or high volumes
of data is the time required to copy and compute 
the sha1sum for the file within
the web server.  Each 4G JWST file currently takes on the order of 
2 minutes just to copy or checksum.   This basic data transfer
time dwarfs the timing one would ideally desire for a web response,  
tens of milliseconds, putting CRDS deep into the regime of ``long polling''.    
Because of the current implementation, the web response time is
unbounded and at risk of exceeding proxy timeouts which cancel 
the overall transaction with the web server.   Processing times for 
real world HST file submissions have approached an hour and
in practice have exceeded generous proxy timeout limits.

This can be
mitigated by partitioning files into multiple smaller submissions (also smaller
incremental *failure groups* for certification errors or other problems) or
using alternate backend delivery mechanisms for particularly large submissions.
After initial bootstrappng, all incremental JWST reference updates to date have
been successfully ingested using the web interface.  Fully addressing large
file submissions requires the addition of background processing which isolates
file ingest processing from web protocol timing; this amounts to the addition
of a miniature hidden pipeline in CRDS.

An additional challenge associated
with the submission of large volumes of data is the loss of processing time
associated with a single errant file forcing the cancellation of the entire
batch.  As the number of files and volume of data in one batch increases, the
processing time increases linearly, and the penalty for errors in submitted
files also increases linearly.  It's bad when file 1199 of 1200 fails wiping
out an entire day of ingest processing.

Automatically partitioning submissions into reasonable chunks of work is a 
challenging requirement. Because of the unknown semantics and 
interrelationships between the potentially multiple (new or old) types 
in a single submission, human intelligence is required to partition files 
into meaningful groups which can be isolated and used independently 
of other potentially failing groups. However, it is relatively
easy for submission system to warn the user regarding excessively large 
submission requests with suggestions that the submission be partitioned.

Reference files in FITS, JSON, and ASDF format are supported.

\section{Enabling pipeline flexibility}

CRDS was designed to allow running the JWST calibration pipelines remotely much
more easily. HST users could always rerun pipelines at their home institutions,
but it was considerably more painful to do since they had to determine what
reference files their datasets required and retrieve them from the archive
before they could run the pipeline. Even the first task was made more
complicated by the fact that there was no reliable way to find the current best
reference files.

For JWST, CRDS will provide a web service that can be accessed
remotely. Furthermore, the JWST calibration pipelines have been designed to
make the request directly to CRDS to determine which reference files to use and
download the file if it is not available locally. This means anyone can run the
pipeline remotely and be assured that the right reference files will be used,
and retrieved if necessary.

In fact, the bestref functionality has been designed to work entirely locally
if all the necessary context and rmap files are available locally. And the
normal mode of operation is to cache all the files for that functionality even
if running remotely. Once these files are downloaded, the only necessary
internet connection is to check if the context used locally is the current one
being used for JWST operational pipelines. Otherwise, it is entirely possible
to run this functionality entirely locally. The bestref functionality is very
portable and easy to distribute with with the calibration pipeline software.

Another aspect of the pipeline flexibility is that this also allows users to
control the reference file rules. For example, there are cases for which users
prefer to continue using the same reference files as for previous data that has
been calibrated remotely in preference to using slightly better reference
files, but introducing an inconsistency in processing the different data
sets. Users may be able to specify a specific pipeline context instead of the
current context.

Finally, users may edit the rules files directly to replace STScI supplied
reference files with their own ones, or even to add a custom step to the
pipeline with an entirely new set of rules and reference files.

\section{Use for HST}

Although CRDS was designed for use with JWST, it was desired to upgrade the HST
system to use it as well. The advantage for JWST is that CRDS would be heavily
tested in an operational environment. The bestref machinery is essentially
identical, but different in application since HST pipelines populate the data
set's header with the reference files to be used rather than the calibration
pipeline using the service.

The major challenge for HST was in translating the effective rules that existed
in the database into rmap files and ensuring that CRDS was producing the same
results. This was done by doing the recommended comparison for every dataset
in the HST archive. The generation of the rmaps was automated since the target
was constantly changing for HST because of continual reference file
updates. The cycle of generating rmaps and making the reference file comparison
for all datasets was repeated many times until CRDS went operational. This was
further complicate by the fact that the database that contained the CDBS best
references was not reliable. The differences that arose had to be further
tested with the operations bestref facility (which requires using actual
datasets thus is much slower).

This testing uncovered a number of yet undiscovered problems with the CDBS
recommendations, which were then fixed in both.

The two systems were run in parallel for many months with the results being
compared, first with CDBS used for the actual results, then switching to CRDS
as the primary system. CDBS has since been disabled.

\section{Other Applications}

It is important to realize that this system has a wider range of application
than just for selecting appropriate reference files. It can act as a selector
many uses so long as the number of selections is not enormous, and the set of
selection parameter is reasonably consistent and bounded for all data
sets. Other uses are already envisioned for JWST. For example, it will be used
to determine which calibration pipeline to run for the dataset supplied. 
So rather than supplying a reference file to use, it will supply the pipeline 
to execute (either as a name of an executable, or more exactly, a pipeline 
configuration file that the pipeline startup system uses to execute the right
pipeline). It may also be
used to aid in mapping data files to the appropriate data analysis object model
for the data analysis software.

In cases where the parameter sets branch significantly (e.g., when dealing with
data from widely different instruments or even observatories where it is likely
very different conventions are being used for metadata) one may possibly invoke
CRDS tools iteratively, using the first iteration to branch to different sets of
rules on a small subset of the metadata, to cases where each branch has more
consistent metadata.

\section{Licensing and Availability}

The bestref client library has a 3-clause BSD and available through its
repository (xxx). The server side software (e.g., the machinery that handles
file submissions and web services) is not publicly available due to security
concerns, though it is possible that it may be made publicly available once it
has been vetted to be free of any security issues. We will make it available to
qualified institutions and individuals provided that they agree not to make it
publicly available. The client library is quite portable. The server-side
software has more local (STScI) dependencies as well as library dependencies,
and all the configuration, administration , and security issues providing a
server entails.

\section{Acknowledgments}

This work was supported by the JWST mission, a joint effort of NASA,
ESA, and CSA. STScI is operated on behalf of NASA by the Association
of Universities for Research in Astronomy, and by the HST mission xxx
The implementation was aided by
Jonathan Eisenhamer, and the integration into the operations system by Michael
Swam. Testing from the instrument scientist perspective was carried out by Rosa
Diaz and Matthew McMaster. Motivations for the work were provided by the weekly
Science Software Branch Donut meeting.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%%
%%  \citet{key}  ==>>  Jones et al. (1990)
%%  \citep{key}  ==>>  (Jones et al., 1990)
%%
%% Multiple citations as normal:
%% \citep{key1,key2}         ==>> (Jones et al., 1990; Smith, 1989)
%%                            or  (Jones et al., 1990, 1991)
%%                            or  (Jones et al., 1990a,b)
%% \cite{key} is the equivalent of \citet{key} in author-year mode
%%
%% Full author lists may be forced with \citet* or \citep*, e.g.
%%   \citep*{key}            ==>> (Jones, Baker, and Williams, 1990)
%%
%% Optional notes as:
%%   \citep[chap. 2]{key}    ==>> (Jones et al., 1990, chap. 2)
%%   \citep[e.g.,][]{key}    ==>> (e.g., Jones et al., 1990)
%%   \citep[see][pg. 34]{key}==>> (see Jones et al., 1990, pg. 34)
%%  (Note: in standard LaTeX, only one note is allowed, after the ref.
%%   Here, one note is like the standard, two make pre- and post-notes.)
%%
%%   \citealt{key}          ==>> Jones et al. 1990
%%   \citealt*{key}         ==>> Jones, Baker, and Williams 1990
%%   \citealp{key}          ==>> Jones et al., 1990
%%   \citealp*{key}         ==>> Jones, Baker, and Williams, 1990
%%
%% Additional citation possibilities
%%   \citeauthor{key}       ==>> Jones et al.
%%   \citeauthor*{key}      ==>> Jones, Baker, and Williams
%%   \citeyear{key}         ==>> 1990
%%   \citeyearpar{key}      ==>> (1990)
%%   \citetext{priv. comm.} ==>> (priv. comm.)
%%   \citenum{key}          ==>> 11 [non-superscripted]
%% Note: full author lists depends on whether the bib style supports them;
%%       if not, the abbreviated list is printed even when full requested.
%%
%% For names like della Robbia at the start of a sentence, use
%%   \Citet{dRob98}         ==>> Della Robbia (1998)
%%   \Citep{dRob98}         ==>> (Della Robbia, 1998)
%%   \Citeauthor{dRob98}    ==>> Della Robbia

%% References with bibTeX database:

\makeatletter
    \clubpenalty10000
    \@clubpenalty \clubpenalty
    \widowpenalty10000
\makeatother

\bibliographystyle{model2-names}
\bibliography{asdf}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model2-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have one of the following forms:
%%   \bibitem[Jones et al.(1990)]{key}...
%%   \bibitem[Jones et al.(1990)Jones, Baker, and Williams]{key}...
%%   \bibitem[Jones et al., 1990]{key}...
%%   \bibitem[\protect\citeauthoryear{Jones, Baker, and Williams}{Jones
%%       et al.}{1990}]{key}...
%%   \bibitem[\protect\citeauthoryear{Jones et al.}{1990}]{key}...
%%   \bibitem[\protect\astroncite{Jones et al.}{1990}]{key}...
%%   \bibitem[\protect\citename{Jones et al., }1990]{key}...
%%   \harvarditem[Jones et al.]{Jones, Baker, and Williams}{1990}{key}...
%%

% \bibitem[ ()]{}

% \end{thebibliography}

\end{document}

%%
%% End of file `elsarticle-template-2-harv.tex'.

### 2015-10-04 docs/paper/crds.tex
fixed a bunch of figure issues
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2122 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
-xxx example 1 (highlighting a \& b)
+Figure~\ref{fig:example1} illustrates use of the first two items.
+Essentially two different configurations are supported, and for each there are three possible choices of reference files that depend on the date of the observation.
+For example, if the date of the observation for the configuration {\tt (\textquotesingle MIRIFULONG\textquotesingle , \textquotesingle FAST\textquotesingle , \textquotesingle FULL\textquotesingle )} is 2015-04-02, the second choice will be used resulting in the return of {\tt jwst\_miri\_dark\_0032.fits} as the recommended reference file.
 
 \begin{figure*}
-\centering
 \begin{verbatim}
@@
 \end{verbatim}
-\caption{xxx}
+\caption{Example showing basic parameter matching rules coupled with date dependency.}
+\label{fig:example1}
 \end{figure*}
 
-xxx example 2 adding c
-\begin{figure}
+Figure~\ref{fig:example2} shows the use of the software selection mechanism.
+In this case if the software version is less than 3.1 (using the typical version semantics) then the first file will be chosen, if less than 5 the second will be chosen, otherwise the last file will be used.
+
+\begin{figure*}
 \begin{verbatim}
@@
 \end{verbatim}
-\end{figure}
-
-xxx example 3 illustrating d
-
-\begin{figure}
+\caption{Example showing use of the software version selection mechanism.}
+\label{fig:example2}
+\end{figure*}
+
+Figure~\ref{fig:example3} shows how two reference files may be selected
+that bracket the particular parameter. Here if the parameter has a value 
+of 3.2, then the pair of images 
+(\texttt{cref\_flatfield\_124.fits}, \texttt{cref\_flatfield\_137.fits}) will be returned
+
+\begin{figure*}
 \begin{verbatim}
@@
 \end{verbatim}
-\end{figure}
-
-Here, a parameter value of 1.3 returns the value:
-
-\begin{verbatim}
-('cref_flatfield_120.fits', 'cref_flatfield_124.fits')
-\end{verbatim}
-
-xxxx example 4 illustrating e
-
+\caption{Example showing bracketing selection.}
+\label{fig:example3}
+\end{figure*}
+
+Figure~\ref{fig:example4} shows how a
+wavelength of 1300 (between 1220 and 1530) results in the partial match 
+of \texttt{hst\_wfc3\_flatfile\_0027.fits} and eliminates 
+\texttt{hst\_wfc3\_flatfile\_0028.fits}
+of as a candidate.   Since \texttt{BETWEEN}
+can be used in an arbitrary Match parameter
+slot,  potentially multiple times,  volumes can be described, and also
+described in concert with other types of match syntax for other parameters
+such as wildcard matching or regular expressions.
+
+\begin{figure*}
 \begin{verbatim}
@@
 \end{verbatim}
-
-Here a wavelength of 1300 (between 1220 and 1530) results in the partial match
-of
-
-\begin{verbatim}
-'hst_wfc3_flatfile_0027.fits' and eliminates 
-"hst_wfc3_flatfile_0028.fits"
-\end{verbatim}
-
-as a candidate.   Since BETWEEN can be used in an arbitrary Match parameter
-slot,  potentially multiple times,  volumes can be described, and also
-described in concert with other types of match syntax for other parameters
-such as wildcard matching or regular expressions.
-
-XXXXXXX I think the capabilities of (e) are actually folded into Match()
-described in (a),  where each individual parameter of a match case can use
-one of several match syntaxes.   Further,  there is no requirement that the
-match expressions of the same parameter use the same method across all cases,
-and indeed it is common to use N/A which is a specialized kind of match.
-
-\begin{verbatim}
-XXXX I documented all this stuff here:
-
-XXXX   https://jwst-crds.stsci.edu/static/users_guide/rmap_syntax.html#selectors
-\end{verbatim}
-
-XXXX By far the most common match syntax used is the literal-value-or-glob,
-including the degenerate case of a single literal value.  Unlike CDBS which had
-discrete rows for every combination of discrete parameter values, CRDS
-summarizes the combinatorial explosion of parameter possibilities into a single
-concise multi-parameter expression by virtue of the matching syntax.  It is far
-more comprehensible to look at one multi-parameter match expression with
-or-globs than it is to scan 60 or 100 simple rows in the CDBS database.
-Another common match expression is N/A.  BETWEEN has also been used.
+\caption{An example showing matching specified ranges.}
+\label{fig:example4}
+\end{figure*}
+
+[xxx need headers included and explained since examples have unnamed
+parameters that won't make any sense unless put in context]
+
+[xxx insert full description of syntax used]
+
+[xxx somewhere put in explanation of safety features preventing hand
+mangling of rules files and configuration]
+
+Full documentation of the syntax and semantics of all the rmap and
+context files is available on the web 
+\footnote{\texttt{https://jwst-crds.stsci.edu/static/users\_guide/rmap\_syntax.html\#selectors}}
 
@@
 
-xxx example of instrument context file
+[xxx need example of instrument context file]
 
@@
 
-xxx example of pipeline context file
+[xxx need example of pipeline context file]
 
@@
 system. The ability to submit files or make changes requires user
-validation. Figure xxx shows a screen shot of the home page of the CRDS
-system, which is visible to the public. The submission capabilities 
-are indicated in the xxx links in
-xxx. Figure xxx shows the submission web page for updates for reference
-files. This examples is for xxx.
+validation. Figure~\ref{fig:publichome} 
+shows a screen shot of the home page of the CRDS
+system, which is visible to the public.
+
+File submission is limited to authenticated users. The home page for
+authentic pages is shown in Figure~\ref{fig:authenticatedhome}.
+The fully automatic
+standard process is dubbed ``Batch Reference Submission'' 
+in reference to submission of a pile of files for one instrument,
+multiple types,  and automatic certification and rules updates.
+
+Figure~\ref{fig:batchsubmission} shows the starting page for submitting
+a batch set of files using the streamlined system.
+
+Figure~\ref{fig:goodsubmissionreview} shows the results of a successfully validated batch  submission request.
+
+Figure~\ref{fig:failedsubmission} shows the results of an unsuccessfully validated batch submission request showing what went wrong.
+
+Figure~\ref{fig:confirmedsubmission} shows the results of a successfully completed submission request.
 
@@
 \caption{JWST CRDS Public Home Page}
+\label{fig:publichome}
 \end{figure*}
@@
 \includegraphics[width=180mm]{JWST_Authenticated_Home.png}
-\caption{JWST CRDS Authenticated User Home Page}
+\caption{JWST Authenticated Users Home Page}
+\label{fig:authenticatedhome}
 \end{figure*}
@@
 \caption{JWST Batch File Submission Page}
+\label{fig:batchsubmission}
 \end{figure*}
@@
 \caption{JWST Good Submission Example}
+\label{fig:goodsubmissionreview}
 \end{figure*}
@@
 \caption{JWST failed submission example}
+\label{fig:failedsubmission}
 \end{figure*}
@@
 \caption{JWST submission confirmed example}
+\label{fig:confirmedsubmission}
 \end{figure*}
-
-File submission is limited to authenticated users. The fully automatic
-standard process is dubbed "Batch Reference
-Submission" in reference to submission of a pile of files for one instrument,
-multiple types,  and automatic certification and rules updates.
 

### 2015-10-04 docs/paper/crds.tex
fixed a bunch of figure issues
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2123 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 The system that was used for the Hubble Space Telescope (HST) was called the
-Calibration Database System (CDBS). It was used successfully for many
-years. The experience with it revealed that there were some limitations that
+Calibration Database System (CDBS,  
+\citealt{1994Cox,1997Lubow,1998Cox,1997hstinternal,2004Swam}). It was used successfully for many years (with some design changes documented in the 
+cited references). The experience with it revealed that there were some limitations that
 proved to constrain its capabilities, and as a result, a newer system that

### 2015-10-05 sources/interactive/tests.py
Unit test fixes for JWST,  ill-advised META.INSTRUMENT.TYPE hack added to database.py as comment,  right approach is probably to write off META.INSTRUMENT.TYPE for dataset parameters (which breaks the unit test form which uses an old .pmap,  then have to correct tests to use modern pmap).
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2127 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -446,12 +446,9 @@ class InteractiveBase(TransactionTestCase):
     def test_batch_submit_truncated(self):
         self.login()
         response = self._batch_submit_insert(self.batch_submit_truncated_references)
-        assert "File may have been truncated" in response.content, \
-            "Expected file truncation warning not present"
+        self.assertIn("File may have been truncated", response.content)
         # doesn't guarantee same message but any WARNING will trigger top level notice
-        assert "WARNING" in response.content, \
-            "No warning in response,  truncation may be overlooked."
-        # log.info("truncated:", response.content)
+        self.assertIn("WARNING", response.content)
 
     def _assert_normal_bsr_insert(self, response):
         # print response

### 2015-10-05 sources/jwst/database.py

@@ -114,6 +114,9 @@ def get_dataset_headers_by_id(context, dataset_ids):
     
     for instr, dids in ids_by_instrument.items():
         instr_headers = parameter_interface.get_dataset_headers_by_id(dids, matching_params[instr])
+        # for (key, header) in instr_headers.items():
+        #     if "META.INSTRUMENT.TYPE" not in header:
+        #         header["META.INSTRUMENT.TYPE"] = header["META.INSTRUMENT.NAME"]
         headers.update(instr_headers)
 
     return headers

### 2015-10-06 docs/paper/crds.tex
added references
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2124 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3
various improvements, extra examples, section on selectors, etc
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2128 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 \ead{perry@stsci.edu}
-\author[stsci]{J.~Miller}
+\author[stsci]{Todd~Miller}
 
@@
 
-FITS \sep
-File formats \sep
-Standards \sep
-World Coordinate System
+Calibration \sep
+Pipelines \sep
 
@@
 
+\subsection{Rules Framework}
+
+All the files that define the rules for how reference files are selected
+use the same organization and syntax.
+A simple syntax is used that consists of expected variables set to simple, 
+possibly nested, datastructures. Each file is expected to have a header 
+and selector defined. The header contains information about the intended 
+use of the file, history, information to validate the integrity of the file,
+and other similar items. Most important, the header identifies the exposure
+parameters that are to be used in the selection process. The selector 
+contains the specifics on the rules themselves.
+
 \subsection{Examples}
 
-Figure~\ref{fig:example1} illustrates use of the first two items.
-Essentially two different configurations are supported, and for each there are three possible choices of reference files that depend on the date of the observation.
-For example, if the date of the observation for the configuration {\tt (\textquotesingle MIRIFULONG\textquotesingle , \textquotesingle FAST\textquotesingle , \textquotesingle FULL\textquotesingle )} is 2015-04-02, the second choice will be used resulting in the return of {\tt jwst\_miri\_dark\_0032.fits} as the recommended reference file.
+Figure~\ref{fig:example1} illustrates use of the first two items. First note the contents
+of the header. It shows what previous rmap file it was derived from, that it is defining
+the rules for the selection of reference files (since this syntax is also used for
+the selection of other kinds of files), what kind of reference file is being selected, information about the telescope and instrument, and what the name of the file is. 
+The {\tt parkey} attribute defines the parameters to use for the selection. In the
+case of JWST, the parameters map to FITS header keywords, but are referred through
+nested object-oriented scheme; the mapping to specific keywords is handled by a special
+library interface that is part of the calibration pipeline. In this specific example,
+This is the rules file for selecting the JWST MIRI instrument dark files, based on 
+the specific detector, read pattern, and subarray configuration, along with the 
+observation date.
+
+The header permits attributes that allow specialized handling of the metadata 
+the dataset, including indicating when parameters are relevant or not (e.g., only 
+care about its value if the value of another parameter is given as specified), 
+how to handle cases where no match is found, and hooks to allow special preprocessing
+of parameter values. See the documentation for details on these cases. 
+\footnote{\url{https://jwst-crds.stsci.edu/static/users\_guide/rmap_syntax.html\#active-header-fields}}
+Most of these special features were added to handle the existing complexitites present in the CDBS rule system; we expect these will be used far less for JWST.
+
+The selector part of the file indicates that a match is first performed on the 
+three specified parameters. There are two supported configurations in this example.
+If one matches, then the date is used to determine which of the following three files
+should be used.
+For example, if the date of the observation for the configuration {\tt (\textquotesingle 
+MIRIFULONG\textquotesingle , \textquotesingle FAST\textquotesingle , 
+\textquotesingle FULL\textquotesingle )} is 2015-04-02, the second choice 
+will be used resulting in the return of {\tt jwst\_miri\_dark\_0032.fits} 
+as the recommended dark reference file.
 
@@
 \begin{verbatim}
+header = {
+    'derived_from' : 'jwst_miri_dark_0007.rmap',
+    'filekind' : 'DARK',
+    'instrument' : 'MIRI',
+    'mapping' : 'REFERENCE',
+    'name' : 'jwst_miri_dark_0009.rmap',
+    'observatory' : 'JWST',
+    'parkey' : (('META.INSTRUMENT.DETECTOR', 'META.EXPOSURE.READPATT', 'META.SUBARRAY.NAME'),),
+    'sha1sum' : 'bd99f4960096de9ad39a9ce506d5ff985847c4a3',
+}
+
 selector = Match({
@@
 
-Figure~\ref{fig:example2} shows the use of the software selection mechanism.
+Figure~\ref{fig:example2} shows the use of the software selection mechanism (for brevity, the header is omitted in this and subsequent examples).
 In this case if the software version is less than 3.1 (using the typical version semantics) then the first file will be chosen, if less than 5 the second will be chosen, otherwise the last file will be used.
@@
 
-[xxx need headers included and explained since examples have unnamed
-parameters that won't make any sense unless put in context]
-
-[xxx insert full description of syntax used]
-
-[xxx somewhere put in explanation of safety features preventing hand
-mangling of rules files and configuration]
+\subsection{Suppported Selectors and Features}
+
+This section more systematically describes existing selector mechanisms. 
+First is is necessary to understand how the supplied parameters (specified
+in the header parkey attribute) are used with selectors. If selectors are 
+nested, each layer removes one or more parameters from the list leaving 
+the rest for lower nestings. For example, if parkey is as specified in
+Figure~\ref{fig:example1}, then 4 parameters are available. The Match 
+selector is requesting 3 since all of its keys have a tuple of 3 items,
+that leaves only the date parameter for subsequent selectors.
+In all cases, the selector expects to be provided an argument that is the 
+appropriate type (e.g., if time).
+
+Selectors may return a single filename, a tuple of filenames,
+``Not Applicable'' (which basically implies that no file is
+needed for this specific case, i.e., no such calibration need be 
+performed) or ``OMIT'' (Currently unused).
+
+\subsubsection{Match}
+This selector finds which tuple of parameters matches the supplied tuple
+of values for those parameters. This is a very flexible selector, and 
+many options are provided for its use. (If only one parameteter is being,
+matched, the tuple can be replaced by a simple string.)
+
+In the simple case, matches are required to be exact. However, to avoid
+rules from having to specify large numbers of combinations where no
+distinctions are being made, a number of mechanisms have been provided
+to make rules much more concise.
+
+\begin{description}
+\item[lists of allowable alternatives:] Allowable values for parameteters
+may be supplied as an \textquotesingle OR\textquotesingle 
+list using {\tt |} as a separator. For example:
+\texttt {({\ttfamily"}filter1{\ttfamily"}
+| {\ttfamily"}filter2{\ttfamily"},...)} will allow either value to match the first
+parameter.
+\item[Wild Cards:] Using an {\tt \*} in a string applies familiar wildcard 
+matching rules to the supplied string. For example 
+\texttt {({\ttfamily"}F*122{\ttfamily"})} will
+match any value starting with {\tt F} and ending with {\tt 122}
+\item[Regular Expressions:] This allows matching true regular expressions,
+allowing for more complex matching rules than simple wildcards permit.
+\item[Literal Expressions:] A literal expression is bracketed with curly
+braces {\tt \{ \}} and allows inclusion of special characters without 
+special interpretation by CRDS, such as {\tt | and \*}.
+\item[Relational Expressions:] Relational expressions are braketed by {\tt \#}.
+These do numerical comparisons on the supplied parameter value to determine
+a match. Supported comparison operators are: 
+\texttt {\textgreater, \textgreater =, \textless, \textless =, == and or}. 
+For example \texttt {({\ttfamily"}\# >=1 and <37\",)} 
+will match any number equal to or 
+greater than 1 and less than 37.
+\item[Between:] This is simply a more convenient way of expressing a range
+than using relational expressions. E.g., equivalent to the previous example
+is: \texttt{{\ttfamily"}between 1 37{\ttfamily"}}. It is inclusive of the first number.
+\item[N/A:] This is equivalent to using a wildcard for the value, but with 
+the difference of how weighting is used (discussed below). This does not
+affect the weight of the match.
+\item[NOT Expressions:] A negation of a match. 
+\texttt {{\ttfamily"}not HRC{\ttfamily"}} 
+is a match if the value does not match {\tt HRC}.
+\item[Substitutions:] A shorthand notation that needs better explanation 
+than is in the documenation [I couldn't understatnd it as written xxx]
+\end{description}
+
+With all these match options it is possible to write multiple items that 
+match a given case. In order to allow effective defaults for general cases
+while allowing specific cases to override the general case, special rule
+for disambiguation in these situations have been developed. The basic idea
+is that more specific matches take precedence over more general matches.
+For example, if one item lists as its matching value a wildcard, and another
+gives a specific value for the same parameter, the specific match takes
+precedence. The precedence is handled by determining the generality of the
+match. Use of wildcards or regular expressions increase the generality index,
+while use of N/A does not. [I found the explanation of Match weighting
+unclear, and it suggests the oppposite, a couple examples would help a lot
+ xxx].
+
+If after using these precedence rules, there are still multiple matches,
+an error results.
+
+\subsubsection{UseAfter}
+This expects an ordered sequence of date/time values as part of the rules.
+This selector finds the greates date/time value that is less than or equal
+to the supplied date/time.
+
+\subsubsection{SelectVersion}
+This is essentially a special case of relational matches that understands
+the semantics of software versions (e.g., that 1.2 > 1.1.10).
+
+\subsubsection{ClosestTime}
+This selector selects the item with the closest time.
+
+\subsubsection{GeometricallyNearest}
+This selector selects the item where the ratio of the parameter to that
+in the list of choices is closest to 1. For example, 4 would match 10 
+instead of 1 since 10/4 is closer to 1 than 4/1.
+
+\subsubsection{Bracket}
+This selector finds the two items for which one is next greater in value,
+and the one that is next least in value (as illustrated in
+Figure~\ref{fig:example3}).
 
@@
 context files is available on the web 
-\footnote{\texttt{https://jwst-crds.stsci.edu/static/users\_guide/rmap\_syntax.html\#selectors}}
+\footnote{\url{https://jwst-crds.stsci.edu/static/users\_guide/rmap\_syntax.html\#selectors}}
 
@@
 
-[xxx need example of instrument context file]
+Figure~\ref{fig:example_instrument_context}
+
+\begin{figure*}
+\begin{verbatim}
+header = {
+    'derived_from' : 'jwst_nircam_0015.imap',
+    'instrument' : 'NIRCAM',
+    'mapping' : 'INSTRUMENT',
+    'name' : 'jwst_nircam_0016.imap',
+    'observatory' : 'JWST',
+    'parkey' : ('REFTYPE',),
+    'sha1sum' : '0fd29b57f226f8c53bf3dfa7564eccd4e3fc56bf',
+}
+
+selector = {
+    'DARK' : 'jwst_nircam_dark_0003.rmap',
+    'DISTORTION' : 'N/A',
+    'DRIZPARS' : 'jwst_nircam_drizpars_0000.rmap',
+    'FLAT' : 'jwst_nircam_flat_0000.rmap',
+    'GAIN' : 'jwst_nircam_gain_0001.rmap',
+    'IPC' : 'jwst_nircam_ipc_0000.rmap',
+    'LASTFRAME' : 'N/A',
+    'LINEARITY' : 'jwst_nircam_linearity_0003.rmap',
+    'MASK' : 'jwst_nircam_mask_0002.rmap',
+    'PHOTOM' : 'jwst_nircam_photom_0002.rmap',
+    'READNOISE' : 'jwst_nircam_readnoise_0001.rmap',
+    'REGIONS' : 'N/A',
+    'RESET' : 'N/A',
+    'SATURATION' : 'jwst_nircam_saturation_0002.rmap',
+    'SPECWCS' : 'N/A',
+    'SUPERBIAS' : 'jwst_nircam_superbias_0003.rmap',
+    'WCSREGIONS' : 'N/A',
+}
+\end{verbatim}
+\caption{An example of an instrument contex file (.imap)}
+\label{fig:example_instrument_context}
+\end{figure*}
 
@@
 
-[xxx need example of pipeline context file]
+Figure~\ref{fig:example_pipeline_context} shows an example of such a pipeline context file.
+It is used to select the appropriate instrument context file to use.
+
+\begin{figure*}
+\begin{verbatim}
+header = {
+    'derived_from' : 'jwst_0068.pmap',
+    'description' : 'Hand edited to support updated .imaps for N/A',
+    'mapping' : 'PIPELINE',
+    'name' : 'jwst_0069.pmap',
+    'observatory' : 'JWST',
+    'parkey' : ('META.INSTRUMENT.NAME',),
+    'sha1sum' : '691d78053ef710f31bfd8f5bea8ffdc3c1dec1aa',
+}
+
+selector = {
+    'FGS' : 'jwst_fgs_0016.imap',
+    'MIRI' : 'jwst_miri_0043.imap',
+    'NIRCAM' : 'jwst_nircam_0016.imap',
+    'NIRISS' : 'jwst_niriss_0024.imap',
+    'NIRSPEC' : 'jwst_nirspec_0026.imap',
+}
+\end{verbatim}
+\caption{An example of a pipeline context file (.pmap)}
+\label{fig:example_pipeline_context}
+\end{figure*}
 
@@
 take significant modifications but is possible.
+
+\subsection{Ensuring integrity of the configuration}
+
+Since all the rules involve simple text files, one possible corruption of the
+integrity of the system is if someone edits or otherwise changes the
+contents of one of the files. As a protection against that, all the files
+involved contain a SHA1SUM checksum on the contents 
+(\citealt{sha1ref}).
+CRDS when loading the
+files compares the the computed SHA1SUM against what is contained in the 
+file header. If they do not match, an error is raised.
+
+To allow flexibility in usage by remote users of the pipeline, one can
+invoke CRDS so that this check is overridden, allowing users to hand edit 
+such files with their local customizations. But with the operational systems,
+these checks are always performed.
 
@@
 
+Another improvement planned is the ability to return values other than
+filenames or tuples of filenames. A common use of reference files for HST 
+was to provide a table of parameter to be used by the calibration 
+pipeline to tune processing to the configurations. Often the real need
+of the pipeline was just a handful of parameter values. Often this resulted
+in a dual layer lookup system. CDBS would select a table (though sometimes
+there was only one reference file for all cases), and then the calibration
+pipeline would select a specific row in the table that matched an additional
+set of selection parameters. This could be greately simplified if the 
+rmap itself bypassed reference files entirely and effectively embedded
+the parameter values as what is returned. In this manner, it relieves 
+the calibration pipeline of embedding its own matching system in its code.
+
 \section{Enabling pipeline flexibility}
@@
 \bibliographystyle{model2-names}
-\bibliography{asdf}
+\bibliography{crds}
 

### 2015-10-06 docs/paper/crds.tex
adding references, fixing text refernces, etc, adding draft watermark...
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2129 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
+\usepackage{draftwatermark}
+\SetWatermarkText{DRAFT}
+\SetWatermarkScale{1}
 \lstset{
@@
 
-In the context of HST (see section xxx), reversion to prior sets of 
+In the context of HST (see section~\ref{sec:HST}), reversion to prior sets of 
 rules has been used to
@@
 
-Figure~\ref{fig:batchsubmission} shows the starting page for submitting
-a batch set of files using the streamlined system.
-
-Figure~\ref{fig:goodsubmissionreview} shows the results of a successfully validated batch  submission request.
-
-Figure~\ref{fig:failedsubmission} shows the results of an unsuccessfully validated batch submission request showing what went wrong.
-
-Figure~\ref{fig:confirmedsubmission} shows the results of a successfully completed submission request.
-
 \begin{figure*}[ht!]
@@
 
-The user identifies the local files designated as the files to replace existing
-ones. When all the updates have been identified, the submit button [or
+The authenticated user begains a batch submission of files on the batch
+submission page (Figure~\ref{fig:batchsubmission}) 
+by identifying the local files designated as the 
+files to replace existing ones (note, the local file names are not the 
+names the files will have when ingested into CRDS). 
+When all the updates have been identified, the submit button [or
 whatever] is clicked, and CRDS will then validate each of the reference
@@
 files, rmaps and context files, and other summary information). An example of a
-successful validation is shown in Figure xxx. At this point the user confirms
+successful validation is shown in Figure~\ref{fig:goodsubmissionreview}.
+At this point the user confirms
 the submission after which they will be assigned unique names, added to the
 CRDS database of reference files, sent to the STScI archive for archiving, and
-placed in the disk-based repository of reference files. If the validation
+placed in the disk-based repository of reference files. When the submission
+process completes, the user is presented with a summary page, shown in
+Figure~\ref{confirmedsubmission}
+
+If the validation
 doesn't pass, the results indicate what the problem is so the user may make the
-necessary corrections. Figure xxx shows such a summary of problems.
+necessary corrections. Figure~\ref{fig:failedsubmission}
+shows such a summary of problems.
 
@@
 This is handled by using the tools that the JWST pipeline use to validate the
-reference files. These are based on data models that use JSON Schema (ref xxx)
+reference files. These are based on data models that use JSON Schema
+(\citealt{JSONSchemaCore, JSONSchemaValidation, JSONHyperSchema, JSONSchemaGuide})
 to define the mandatory aspects of the data expected, including all the
@@
 
-\item other cases? xxx
 \end{enumerate}
@@
 
-Reference files in FITS, JSON, and ASDF format are supported.
+Reference files in FITS 
+(\citealt{2010FITS}), JSON (\citealt{JSON}), and ASDF (\citealt{2015ASDF})
+format are supported.
 
@@
 \section{Use for HST}
+\label{sec:HST}
 
@@
 Swam. Testing from the instrument scientist perspective was carried out by Rosa
-Diaz and Matthew McMaster. Motivations for the work were provided by the weekly
-Science Software Branch Donut meeting.
+Diaz and Matthew McMaster.
 

### 2015-10-17 sources/interactive/common.py
DATASET_ID_RE added characters,  comments.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2134 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -15,7 +15,8 @@ from crds.server.config import crds_server_log_dir
 DESCRIPTION_RE = re.compile(complete_re(r"[A-Za-z0-9._\s/,#=\-\+\*!]{0,20000}"))  # 20k == approx 20 pages
 PERSON_RE = re.compile(complete_re(r"[A-Za-z_0-9\.@, \-]{0,128}"))
 
-DATASET_ID_RE = re.compile(complete_re(r"[A-Za-z0-9_:\.]{1,128}"))
+DATASET_ID_PART = r"[A-Za-z0-9_\.\+\-]{1,128}"
+DATASET_ID_RE = re.compile(complete_re(DATASET_ID_PART + ":" + DATASET_ID_PART))
 
 FITS_KEY_RE = re.compile(complete_re(r"[A-Za-z0-9_\-\.]{1,256}"))
 FITS_VAL_RE = re.compile(complete_re(r".{0,256}"))

### 2015-10-17 sources/interactive/views.py

@@ -421,8 +421,8 @@ def handle_upload_delete(must_delete, orig, path):
 
 def get_uploaded_file(request, formvar):
     """Return the DJango UploadedFile associated with `request` and `formvar`,
-    raising an exception if it's original name does not end with one of
-    `legal_exts` file extensions.   Handles <input type='file'>, part 1.
+    screening the original filename for legality.  Handles 
+    <input type='file'>, part 1.
     """
     assert request.user.is_authenticated(), \
         "file uploads are only available for authenticated users."

### 2015-10-18 sources/interactive/tests.py
Unit test fixes for JWST interactive,  adopted jwst_0082.pmap in places since it has META.INSTRUMENT.NAME.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2135 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -92,7 +92,7 @@ class InteractiveBase(TransactionTestCase):
         except Exception, exc:
             print "failed user save:", str(exc)
         self.ingest_path = os.path.join(sconfig.CRDS_INGEST_DIR, str(self.user))
-        self.fake_database_files([self.pmap])
+        self.fake_database_files([self.pmap, self.pmap2])
         models.set_default_context(self.pmap, skip_history=True)
         models.set_default_context(self.pmap, state="operational")
         utils.ensure_dir_exists(os.path.join(lconfig.get_crds_refpath(self.observatory), "test.fits"))
@@ -216,7 +216,7 @@ class InteractiveBase(TransactionTestCase):
     def test_bestrefs_post_archive_dataset(self):
         response = self.client.post("/bestrefs/", {
             "pmap_mode" : "pmap_text",
-            "pmap_text" : self.pmap,
+            "pmap_text" : self.pmap2,
             "dataset_mode" : "dataset_archive",
             "dataset_archive" : self.archive_dataset_id,
             })  
@@ -225,7 +225,7 @@ class InteractiveBase(TransactionTestCase):
     def test_bestrefs_post_default_context(self):
         response = self.client.post("/bestrefs/", {
             "pmap_mode" : "pmap_edit",
-            "pmap_edit" : self.pmap,
+            "pmap_edit" : self.pmap2,
             "dataset_mode" : "dataset_archive",
             "dataset_archive" : self.archive_dataset_id, 
             })  
@@ -239,7 +239,7 @@ class InteractiveBase(TransactionTestCase):
         self.login()
         response = self.client.post("/bestrefs/", {
             "pmap_mode" : "pmap_text",
-            "pmap_text" : self.pmap,
+            "pmap_text" : self.pmap2,
             "dataset_mode" : "dataset_uploaded",
             "dataset_uploaded" : open(dataset1),
             })  
@@ -667,8 +667,8 @@ if sconfig.observatory == "hst":
     class Hst(InteractiveBase):
 
         observatory = "hst"
-        pmap = "hst.pmap"
-        cached_contexts = [pmap]
+        pmap = pmap2 = "hst.pmap"
+        cached_contexts = [pmap, pmap2]
         
         new_context = "interactive/test_data/hst_0027.pmap"
         
@@ -767,8 +767,9 @@ else:  # JWST
 
         observatory = "jwst"
         pmap = "jwst_0000.pmap"
[…]

### 2015-10-18 sources/interactive/common.py
Fixed DATASET_ID regex making : syntax optional to support HST association-only style IDS.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2136 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -16,7 +16,7 @@ DESCRIPTION_RE = re.compile(complete_re(r"[A-Za-z0-9._\s/,#=\-\+\*!]{0,20000}"))
 PERSON_RE = re.compile(complete_re(r"[A-Za-z_0-9\.@, \-]{0,128}"))
 
 DATASET_ID_PART = r"[A-Za-z0-9_\.\+\-]{1,128}"
-DATASET_ID_RE = re.compile(complete_re(DATASET_ID_PART + ":" + DATASET_ID_PART))
+DATASET_ID_RE = re.compile(complete_re(DATASET_ID_PART + "(:" + DATASET_ID_PART+")?"))
 
 FITS_KEY_RE = re.compile(complete_re(r"[A-Za-z0-9_\-\.]{1,256}"))
 FITS_VAL_RE = re.compile(complete_re(r".{0,256}"))

### 2015-10-20 docs/paper/crds.tex
latest, maybe last presubmission version?
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2137 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 We describe a software architecture and implementation for using rules to
-determine which calibration files are appropriate for use in calibrating a
-given observation. This new system replaces what had been previously used for
-the Hubble Space Telescope (HST) calibration pipelines, a system called the
-Calibration Database System (CDBS), and will be used for the James Webb Space
-Telescope (JWST) calibration pipelines, and is currently being used for HST calibration pipelines. . The approach used for this can be
+determine which calibration files are appropriate for calibrating a
+given observation. This new system, the Calibration Reference Data System
+(CRDS), replaces what had been previously used for
+the Hubble Space Telescope (HST) calibration pipelines, 
+the Calibration Database System (CDBS). 
+CRDS will be used for the James Webb Space
+Telescope (JWST) calibration pipelines, and is currently
+being used for HST calibration pipelines. CRDS can be
 easily generalized for use in similar applications that need a rules-based
-system for selecting the appropriate file for a given case; we give some
+system for selecting the appropriate item for a given dataset; we give some
 examples of such generalizations that will likely be used for JWST. The core
@@
 typically numerous, and there may be many that have to be applied to a specific
-dataset. Examples are dark current, bias, flat field, photometric, and
+dataset. Examples include dark current, bias, flat field, photometric, and
 geometric distortions, among many others. Typically calibration files depend on
@@
 cited references). The experience with it revealed that there were some limitations that
-proved to constrain its capabilities, and as a result, a newer system that
+proved to constrain its capabilities, and as a result a newer system that
 removed these constraints was sought. We will briefly describe the design of
@@
 concerned the keyword values used to match datasets to the appropriate
-references.  Unlike dataset parameter keywords which describe a specific
+references.  Unlike dataset parameter keywords that describe a specific
 instrument configuration for one observation, reference file keywords
-circumscribe range of parameter values for which the reference applies.  In
-CDBS, ranges of parameter values were often represented by intermediate values
-which expand into the discrete values used to define specific instrument
-configurations.  As part of submitting reference files, the intermediate values
-were combinatorially exploded into database rows which represented each
-possible application of a reference to some discrete instrument parameter
-configuration.  As an example, a dataset APERTURE keyword would describe the
+circumscribe range of parameter values for which the reference file applies.
+In CDBS, ranges of parameter values were often represented by special values
+that expand into the discrete values used to define specific instrument
+configurations.  As part of submitting reference files, these special values
+were combinatorially exploded into multiple database rows that represented each
+possible combination of parameter values intended to match to the specified
+reference file.  As an example, a dataset APERTURE keyword would describe the
 specific aperture an instrument was configured to use for one observation. In
@@
 describe, indirectly, the combined set of different specific APERTUREs that
-reference file was capable of supporting.  When multiple parameters were used
+reference file was intended to be used for.  When multiple parameters were used
 to match datasets to references, the number of distinct rows in the CDBS
 database was equal to the product of the number of specific values supported by
-a particular reference for each parameter.
+a particular reference file for each parameter.
 
@@
 \begin{enumerate}
-\item Difficulty testing new reference files. The use of a database essentially
+\item \textbf{Difficulty testing new reference files.} 
+The use of a database essentially
 limited the system to one set of rules for selecting reference files. Once a
@@
 for. As a result, the operational pipeline would only discover that there was a
-problem when processing real data, thus resulting in dealing with correcting
-mis-processed data (or in some cases, failure to even process). Problems in the
-operational pipeline are significant disruptions. In the last few years, a test
+problem when processing real data, thus resulting in having to deal with correcting
+mis-processed data (or in some cases, the failure to even process). Problems in the
+operational pipeline are significant disruptions requiring significant work
+to correct. In the last few years a test
 version of the database was created so that tests could be performed, but that
@@
 
-\item Difficulty in undoing mistakes. A delivery of a file with mistaken
+\item \textbf{Difficulty in undoing mistakes.}
+A delivery of a file with mistaken
 parameters could be difficult to undo. No reference file could be removed from
@@
 ``useafter'' date associated with them that indicated that it should be used for
-a date after the specified one *if no other file had a later date that was
-still before the date of the observation*. If one submitted a file intended to
+a date after the specified one \textit{if no other file had a later date that was
+still before the date of the observation}. If one submitted a file intended to
 be used for data after 2000-01-01 but mistakenly provided
@@
 
-\item Difficulty in supporting remote usage by astronomers. 
+\item \textbf{Difficulty in supporting remote usage by astronomers.} 
 Using the bestref facility remotely
@@
 
-\item Difficulty in allowing customized variants of selection rules. Sometimes
+\item \textbf{Difficulty in allowing customized variants of selection rules.}
+Sometimes
 observers or teams have specialized calibration files that they wish to
@@
 calibration pipeline remotely at another institution very difficult since there
-is no simple way to get the the most recent recommendations.
-
-\item Difficulty in providing remote pipelines a consistent bestref
-environment. There are times observers *do not* want changing references files
-if they wish comparison to previously computed results. They want the same
+is no simple way to get the most recent recommendations.
+
+\item \textbf{Difficulty in providing remote pipelines a consistent bestref
+environment.}
+There are times observers \textit{do not} want changing references files
+if they wish comparisons to previously computed results. They want the same
 rules applied, even if they aren't the very best version.
@@
 
-\item Difficulty in understanding what the effective rules are. The exact
+\item \textbf{Difficulty in understanding what the effective rules are.}
+The exact
 selection rules are embodied in a database with a history of transactions for
@@
 that they are not what was intended. Finding mistakes in this situation can be
-quite difficult. And once found, can be difficult to rectify.
-
-\item Difficulty in adding new kinds of selection rules. The database schema
+quite difficult. And once found, they can be difficult to rectify.
+
+\item \textbf{Difficulty in adding new kinds of selection rules.} 
+The database schema
 effectively constrains what kinds of rules can be used. More complex rules
@@
 \item Databases are effectively one state systems. Yes, one can deal with
-multiple states but usually at great complexity.
+multiple states but usually with significantly added complexity.
 \item Databases do not make it simple to distribute software since installing,
 administering and maintaining a database elsewhere is a major task, and keeping
-them synchronized to the master copy is yet a greater complexity
+them synchronized to the master copy is yet a greater complexity.
 \item Once established, changing the structure of database is difficult,
@@
 Is it in fact necessary to use a database to hold the rules? In reviewing all
-the previous and anticipated cases for HST and JWST, it did not appear that a
+the previous and anticipated cases for HST and JWST it did not appear that a
 database was necessary for selection rules, and that a simpler and more
@@
 \begin{enumerate}
-\item the rules are explicit
-\item multiple versions of these rules may exist without conflict, and used in
+\item The rules are explicit.
+\item Multiple versions of these rules may exist without conflict, and used in
 different contexts simultaneously without confusion.
-\item these rule files may be easily distributed so that remote users can run the
+\item These rule files may be easily distributed so that remote users can run the
 ``bestref'' functionality remotely without needing to install or administer
 complex software.
-\item the rules are easily customized, even by hand if necessary if
+\item The rules are easily customized, even by hand if necessary if
 users wish to.
@@
 
-\section{High level organization of CRDS}
-
-The software for CRDS can be considered to be in one of three categories:
+\section{High-Level Organization of CRDS}
+
+The software for the Calibration Reference Data System (CRDS) 
+can be considered to be in one of three categories:
 
 \begin{enumerate}
-\item supporting the bestref functionality
-\item supporting submitting new reference files and all the issues that
-go with that
+\item Supporting the bestref functionality.
+\item Supporting the submittion of new reference files and all the issues that
+go with that.
 \item Supporting format, semantic, and parameter constraint checking for both
-references and rules files.  Capability to detect typos, duplicate lines, and
-grammatical errors in rules files.   Capability to analyze basic properties
+references and rules files.  Having the capability to detect typos, duplicate 
+lines, and grammatical errors in rules files. 
+Having the capability to analyze basic properties
 such duplicate or deleted rows,  by pseudo-mode, for supported tables files.
-\item providing utilities for making CRDS useful in operations, for instrument
-scientists that must generate and monitor reference files, and end users.
+\item Providing utilities for making CRDS useful in: operations; for instrument
+scientists that must generate and monitor reference files; and end users.
 \end{enumerate}
@@
 Each of these will be described in a separate section. Since most of the design
-is centered around the first category, most of the description will be centered
+is centered around the first category, most of the description will be concentrated
 around that.
@@
 can be supported. If more complex cases arise, new structures can be added to
-the library to support these. The following lists existing and possible kinds
-of selections structures. Those that already are supported are marked with an
-`*'. The ones that are not supported are intended to illustrate possible
-extensions that are not purely hypothetical. The following examples of files
-will illustrate specifically these structures.
+the library to support these. The following lists existing selection mechanisms. 
+Examples of files will illustrate specifically these structures.
 
 \begin{enumerate}
-\item matching on sets of discrete parameter values. That is, the item associated
+\item \textbf{Matching on sets of discrete parameter values.}
+That is, the item associated
 with this specific set of parameters is selected if the parameter values are
@@
 name, or a nested set of rules that will be evaluated in turn.  
-There are a number of different parameter match types, literal, or-glob,
-pure regex, between, not, relational, etc.  In the case of multiple parameters,
+There are a number of different parameter match types: exact, enumerated
+list, wildcards,
+pure regex expression, range specification, exclusion test, comparison, etc.  
+In the case of multiple parameters,
 each parameter is matched across all match cases using a process of elimination
@@
 
-\item matching on a sequence of dates. This corresponds to the useafter mechanism
+\item \textbf{Matching on a sequence of dates.}
+This corresponds to the useafter mechanism
 in CDBS. Normally these items will be sorted in date/time order, and the
@@
 
-\item matching software version requirements. This structure indicates selection
+\item \textbf{Matching software version requirements.} 
+This structure indicates selection
 based on versions of the software which item should be selected. It may use
@@
 
-\item getting bracketing files. This is useful if some sort of interpolation
+\item \textbf{Identifying bracketing files.}
+This is useful if some sort of interpolation
 between reference files is desired, in which case a pair of results is
@@
 
-\item matching on ranges of non-discrete values. For example, this may select a
+\item \textbf{Matching on ranges of non-discrete values.}
+For example, this may select a
 file if an observational parameter is in the specified range. Normally, this
@@
 A simple syntax is used that consists of expected variables set to simple, 
-possibly nested, datastructures. Each file is expected to have a header 
+possibly nested, data structures. Each file is expected to have a header 
 and selector defined. The header contains information about the intended 
@@
 The {\tt parkey} attribute defines the parameters to use for the selection. In the
-case of JWST, the parameters map to FITS header keywords, but are referred through
+case of JWST, the parameters map to FITS header keywords, but are referred through a
 nested object-oriented scheme; the mapping to specific keywords is handled by a special
@@
 nested, each layer removes one or more parameters from the list leaving 
-the rest for lower nestings. For example, if parkey is as specified in
+the rest for lower nestings. For example, if \texttt{parkey} is as specified in
 Figure~\ref{fig:example1}, then 4 parameters are available. The Match 
@@
 In all cases, the selector expects to be provided an argument that is the 
-appropriate type (e.g., if time).
+appropriate type (e.g., time for UseAfter).
 
@@
 may be supplied as an \textquotesingle OR\textquotesingle
-list using {\tt |} as a separator. For example:
+{\tt }list using {\tt |} as a separator. For example:
 \texttt {({\ttfamily"}filter1{\ttfamily"}
@@
 \texttt {\textgreater, \textgreater =, \textless, \textless =, == and or}. 
-For example \texttt {({\ttfamily"}\# >=1 and <37\",)} 
+For example \texttt {({\ttfamily"}\# >=1 and <37",)} 
 will match any number equal to or 
@@
 \item[N/A:] This is equivalent to using a wildcard for the value, but with 
-the difference of how weighting is used (discussed below). This does not
-affect the weight of the match.
+the difference of how weighting is used (discussed below). 
 \item[NOT Expressions:] A negation of a match. 
@@
 is a match if the value does not match {\tt HRC}.
-\item[Substitutions:] A shorthand notation that needs better explanation 
-than is in the documenation [I couldn't understatnd it as written xxx]
+\item[Substitutions:] Substitutions can be defined in the header. Essentially
+they result in the replacement of a string in a rules file with a different
+string. This is useful in the case the string is complex and must be entered
+in many different rules (e.g., it is a combination of many different 
+allowable values), or it is more mnemonic to those that must maintain
+the rules than the actual header values are.
 \end{description}
@@
 gives a specific value for the same parameter, the specific match takes
-precedence. The precedence is handled by determining the generality of the
-match. Use of wildcards or regular expressions increase the generality index,
-while use of N/A does not. [I found the explanation of Match weighting
-unclear, and it suggests the oppposite, a couple examples would help a lot
- xxx].
-
-If after using these precedence rules, there are still multiple matches,
-an error results.
+precedence. The precedence is handled by determining the specificity of the
+match. Use of specific values, wildcards, or regular expressions increase
+the specificity index, while use of N/A does not. If multiple rules match,
+the one with the highest specificity index is selected
+
+If after using these precedence rules, there are still multiple matches and 
+if the USEAFTER parameter is used, the most appropriate USEAFTER entry is
+chosesn. If not, an error results.
 
@@
 This is essentially a special case of relational matches that understands
-the semantics of software versions (e.g., that 1.2 > 1.1.10).
+the semantics of software versions (e.g., that 1.2 $>$ 1.1.10).
 
@@
 effect for that instrument. In the example of the instrument context file
-below, one can see that each distinct rmap file has a unique name. If anything
+shown in Figure~\ref{fig:example_instrument_context},
+one can see that each distinct rmap file has a unique name. If anything
 is changed in an rmap file, it gets a new name
-
-Figure~\ref{fig:example_instrument_context}
 
@@
 different in number depending on the branch taken. Achieving that would
-take significant modifications but is possible.
-
-\subsection{Ensuring integrity of the configuration}
+take some modification of the bestref client functionality but is possible
+without a large effort. Doing the same for the submission machinery would 
+be significantly more work.
+
+\subsection{Ensuring Integrity of the Configuration}
 
@@
 
-\subsection{Practicality and Restrictions of this design}
+\subsection{Practicality and Restrictions of this Design}
 
@@
 \begin{enumerate}
-\item submit each of the reference files (with validation of each file
+\item Submit each of the reference files (with validation of each file
 being part of the submission process). This is expected to generate
-unique names for each of the submitted reference files
-\item edit the rmap for that reference file type to include the necessary
+unique names for each of the submitted reference files.
+\item Edit the rmap for that reference file type to include the necessary
 changes to use these (most likely either a replacement of older versions
 or the addition of time-variable ones).
-\item submit the updated rmap file (again with implied validation for
+\item Submit the updated rmap file (again with implied validation for
 correctness)
@@
 of the file in the system that has the desired changes.
-\item edit the instrument context file to use the new version of the rmap file.
-\item submit the updated instrument context file (with validation and 
-generating a new, unique name)
-\item edit the pipeline context file to use the new version of the
+\item Edit the instrument context file to use the new version of the rmap file.
+\item Submit the updated instrument context file (with validation and 
+generating a new, unique name).
+\item Edit the pipeline context file to use the new version of the
 instrument context file.
-\item submit the updated pipeline context file (with validation and 
-generating a new, unique name)
+\item Submit the updated pipeline context file (with validation and 
+generating a new, unique name).
 \end{enumerate}
@@
 
-Since any number of context can exist, one can have several in testing
+Since any number of contexts can exist, one can have several in testing
 simultaneously. If that is the case, one still needs to be careful in
@@
 
-\subsection{Streamlined updates}
+\subsection{Streamlined Updates}
 
@@
 In either of these cases, it is quite useful to streamline the process to
-effectively make it one step. Namely by the fact of submitting the reference
-files, automatically updating and submitting the appropriate rmap to use it,
-and in turn, making the corresponding updates and submissions to the context
+effectively make it a one step operation.
+Specifically by the fact of submitting the reference
+files, in turn automatically updating and submitting
+the appropriate rmap to use it,
+and subsequently, making the corresponding updates and submissions to the context
 files. As a result of these submissions, the user then is given all the
@@
 
-There are several other options as well:
+There are several other options for the edit context as well:
 
 \begin{itemize}
-\item operational
-\item one of last 10
-\item user specified.  
+\item Operational context.
+\item One of last 10 contexts.
+\item User specified context.  
 \end{itemize}
@@
 
-\subsection{Reference File submission details}
+\subsection{Reference File Submission Details}
 
@@
 standard process is dubbed ``Batch Reference Submission'' 
-in reference to submission of a pile of files for one instrument,
+in reference to submission of a group of reference 
+files for one instrument,
 multiple types,  and automatic certification and rules updates.
@@
 \centering
+\includegraphics[width=180mm]{JWST_Submission_Confirmed.png}
+\caption{JWST submission confirmed example}
+\label{fig:confirmedsubmission}
+\end{figure*}
+
+\begin{figure*}[ht!]
+\centering
 \includegraphics[width=180mm]{JWST_Failed_Submission_DM_schema_violation.png}
@@
 \label{fig:failedsubmission}
-\end{figure*}
-
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width=180mm]{JWST_Submission_Confirmed.png}
-\caption{JWST submission confirmed example}
-\label{fig:confirmedsubmission}
 \end{figure*}
@@
 names the files will have when ingested into CRDS). 
-When all the updates have been identified, the submit button [or
-whatever] is clicked, and CRDS will then validate each of the reference
+When all the updates have been identified, the submit button is clicked,
+and CRDS will then validate each of the reference
 files. If they all pass validation, the user will be presented the results of
@@
 process completes, the user is presented with a summary page, shown in
-Figure~\ref{confirmedsubmission}
-
-If the validation
-doesn't pass, the results indicate what the problem is so the user may make the
+Figure~\ref{fig:confirmedsubmission}
+
+If the validation does not pass, 
+the results indicate what the problem is so the user may make the
 necessary corrections. Figure~\ref{fig:failedsubmission}
@@
 There are further checks on file submissions that are intended to warn regarding
-suspicious changes. These changes may be valid, but like indicate a mistake. The
+suspicious changes. These changes may be valid, but likely indicate a mistake. The
 following such situations raise a warning on submission:
@@
 existing reference file name replaced by one that is earlier in the submission
-sequence, that would be unusual, and the submitter warned about this reversion.
-Likewise if instrument or pipeline contexts point to earlier rmaps or instrument
-contexts, respectively, that raises a warning.
+sequence that would be unusual, and the submitter is warned about this reversion.
+Likewise, if instrument or pipeline contexts point to earlier rmaps or instrument
+contexts respectively, that raises a warning.
 
@@
 Utilities are generally targeted to one or more of three classes of users:
-Operations, Instrument Scientists (i.e., those that must create and maintain
+operations, instrument scientists (i.e., those that must create and maintain
 reference files), and general users. Some utilities are useful for only one of
@@
 
-Affected files utility: Given a list of datasets, determine which ones have
+\textbf{Affected files utility:} Given a list of datasets, determine which ones have
 been affected by a change in a pipeline context. Normally it is expected that
@@
 
-Active reference files in a context: List all reference files used in a
+\textbf{Active reference files in a context:} List all reference files used in a
 pipeline context. This indicates what files may be needed to process the
@@
 
-Inverse mapping: Which rmaps and contexts use a specific reference file (e.g.,
+\textbf{Inverse mapping:} Which rmaps and contexts use a specific reference file (e.g.,
 if one finds that one was defective, identify all the pipeline contexts that
-used that file so that users may be notified)?
+used that file so that users may be notified).
 
@@
 
-Difference in rules between two contexts: Summarize what has changed in the
+\textbf{Difference in rules between two contexts:} Summarize what has changed in the
 rules between two pipeline or instrument contexts. This allows instrument
@@
 
-\begin{verbatim}
-% python -m crds.diff jwst_0080.pmap jwst_0081.pmap 
-  --brief --squash-tuples
-  jwst_miri_regions_0004.rmap 
-  jwst_miri_regions_0005.rmap 
-  -- MIRIFUSHORT 12 SHORT N/A 
-  -- added Match rule for jwst_miri_regions_0006.fits
-jwst_miri_0048.imap jwst_miri_0049.imap -- regions -- replaced jwst_miri_regions_0004.rmap with jwst_miri_regions_0005.rmap
-jwst_0080.pmap jwst_0081.pmap -- miri -- replaced jwst_miri_0048.imap with jwst_miri_0049.imap
-\end{verbatim}
-
 \subsection{General users}
 
-Compare retrieved data with current pipeline context: A user has downloaded
+\textbf{Compare retrieved data with current pipeline context:} A user has downloaded
 data and wishes to see what data may need to be re-retrieved since the
@@
 written in Python. The bestref functionality uses the following Python
-libraries (i.e., what isn't part of the Python Standard Library
+libraries (i.e., what is not part of the Python Standard Library
 distribution). It was originally written to use Python 2, but has since been
@@
 
-\subsection{Client side dependencies:}
+\subsection{Client Side Dependencies:}
 
 \begin{itemize}
-\item rules file checking uses the **Parsley** parser generator package to define a grammar capable of detecting duplicate lines (cut-and-paste errors)
-  \begin{itemize}
+\item Parsley: used by rules file checking to define a grammar capable of detecting duplicate lines (cut-and-paste errors)
 \item jwst\_lib.models, jwst\_lib.stpipe, jwst\_lib.modeling (STScI)
@@
 \item pyasdf (STScI)
-  \item astropy
-  \item numpy
-  \end{itemize}
+\item Astropy
+\item Numpy
+
 \end{itemize}
@@
 \item django-file-upoad (source code subsumed into CRDS code with modifications):
-  Used to  manage parallel file uploads, drag-and-drop, progress bars, data rate info,  remote file deletion,  pause/resume,  etc.)
+  Used to  manage parallel file uploads, drag-and-drop, progress bars, data rate info,  remote file deletion,  pause/resume,  etc.).
 \item django-locking (source code subsumed into CRDS code with modifications):
@@
 \item django-dbbackup: Used to backup the database and mirror the database between
-  different environments
-\item pytz: timezone support
-\item jQuery/jQuery-UI: web page interface support
-\item DataTables: Table display and manipulation for jQuery
+  different environments.
+\item pytz: timezone support.
+\item jQuery/jQuery-UI: web page interface support.
+\item DataTables: Table display and manipulation for jQuery.
 \item MochiKit: Javascript debug shell used by django-json-rpc.
-\item memcached / libevent / python-memcached: supports cached results on server
+\item memcached / libevent / python-memcached: supports cached results on server.
 \end{itemize}
@@
 
-Web uploads are capably (not perfectly) handled by the django-file-upload
+Web uploads are handled by the django-file-upload
 system which is fully integrated with the CRDS code base.  An end-to-end
@@
 the sha1sum for the file within
-the web server.  Each 4G JWST file currently takes on the order of 
-2 minutes just to copy or checksum.   This basic data transfer
+the web server.  Each 4~GB JWST file currently takes on the order of 
+two minutes just to copy or checksum.   This basic data transfer
 time dwarfs the timing one would ideally desire for a web response,  
@@
 mitigated by partitioning files into multiple smaller submissions (also smaller
-incremental *failure groups* for certification errors or other problems) or
+incremental \textit{failure groups} for certification errors or other problems) or
 using alternate backend delivery mechanisms for particularly large submissions.
@@
 (\citealt{2010FITS}), JSON (\citealt{JSON}), and ASDF (\citealt{2015ASDF})
-format are supported.
+formats are supported.
 
@@
 filenames or tuples of filenames. A common use of reference files for HST 
-was to provide a table of parameter to be used by the calibration 
-pipeline to tune processing to the configurations. Often the real need
-of the pipeline was just a handful of parameter values. Often this resulted
-in a dual layer lookup system. CDBS would select a table (though sometimes
+was to provide a table of parameters to be used by the calibration 
+pipeline to tune processing to the configurations. Usually the real need
+of the pipeline was just a handful of parameter values rather than
+a whole file. This kind of usage resulted
+in a dual-layer lookup system. CDBS would select a table (though sometimes
 there was only one reference file for all cases), and then the calibration
@@
 rmap itself bypassed reference files entirely and effectively embedded
-the parameter values as what is returned. In this manner, it relieves 
-the calibration pipeline of embedding its own matching system in its code.
-
-\section{Enabling pipeline flexibility}
+the parameters as what is returned. In this manner it would relieve 
+the calibration pipeline of the need for embedding its own matching 
+system in its code.
+
+\section{Enabling Pipeline Flexibility}
 
@@
 selection parameter is reasonably consistent and bounded for all data
-sets. Other uses are already envisioned for JWST. For example, it will be used
+sets. Other such uses are already envisioned for JWST. For example, it will be used
 to determine which calibration pipeline to run for the dataset supplied. 
@@
 The bestref client library has a 3-clause BSD and available through its
-repository (xxx). The server side software (e.g., the machinery that handles
+Subversion repository (https://aeon.stsci.edu/ssb/trac/crds). 
+The server side software (e.g., the machinery that handles
 file submissions and web services) is not publicly available due to security
@@
 software has more local (STScI) dependencies as well as library dependencies,
-and all the configuration, administration , and security issues providing a
+and all the configuration, administration, and security issues providing a
 server entails.
@@
 
-This work was supported by the JWST mission, a joint effort of NASA,
-ESA, and CSA. STScI is operated on behalf of NASA by the Association
-of Universities for Research in Astronomy, and by the HST mission xxx
-The implementation was aided by
-Jonathan Eisenhamer, and the integration into the operations system by Michael
-Swam. Testing from the instrument scientist perspective was carried out by Rosa
-Diaz and Matthew McMaster.
+This work was funded by NASA (contract NAS5-03127) as part of the JWST mission, a joint effort of NASA, the European Space Agency, and the Canadian Space Agency.
+It was also funded as part of the NASA Hubble Space Telescope Science Operations Contract NAS5-26555 with the Space Telescope Science Institute.
+STScI is operated on behalf of NASA by the Association of Universities for Research in Astronomy.
+
+The implementation was aided by Jonathan Eisenhamer, Warren Hack, Mike Droettboom
+and Pey-Lian Lim. 
+Michael Swam patiently answered countless questions about how CDBS
+worked as well as issues regarding operations, and aided integration into the 
+operations system. Further help with the archive systems and web services
+was provided by Linda Thompson, Doris Fraquelli, Kim Dupries.
+Testing and recommendations for changes from the instrument scientist
+perspective was carried out by Rosa Diaz, Matthew McMaster, and Van Dixon.
+Daniel Durand of the Canadian Astronomy Data Centre and Jonas Haase of the
+European Southern Observatory provided useful feedback on issues relevant
+for outside institutions.
 

### 2016-02-25 sources/configs/config.ops.hst.py
opus-2015.3-server-3 dot_setenv crds_stack15
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/branches/opus_2015.3-3@2237 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -27,7 +27,7 @@ PYSYN_CDBS = ""
 
 # These are the file states which are available for download or rpc.
 # XXX TODO restrict to archived or operational
-CRDS_DISTRIBUTION_STATES =  [ "archived", "operational"]  # ["delivered", "submitted", "archiving", 
+CRDS_DISTRIBUTION_STATES =  [ "archived", "operational", "delivered", "submitted", "archiving"]
 
 # The primary URL used by end-users which passes through a proxy which
 # assigns more user-friendly URLs based on standard ports 443.

### 2016-02-25 sources/configs/config.ops.hst.py
Restored distribution states to post-archive for opus-2015.3-server-3 branch, delivery must be archived before consequent .pmap is derivable.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/branches/opus_2015.3-3@2238 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -27,7 +27,7 @@ PYSYN_CDBS = ""
 
 # These are the file states which are available for download or rpc.
 # XXX TODO restrict to archived or operational
-CRDS_DISTRIBUTION_STATES =  [ "archived", "operational", "delivered", "submitted", "archiving"]
+CRDS_DISTRIBUTION_STATES =  [ "archived", "operational",] # "delivered", "submitted", "archiving"]
 
 # The primary URL used by end-users which passes through a proxy which
 # assigns more user-friendly URLs based on standard ports 443.

### 2016-02-26 docs/paper/response.txt
most of reviewer 1 changes, sans those for figures
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2239 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

===================================================

Reviewer 1

The first question in the second paragraph appears to be more
for direct information to the reviewer than request for inclusion 
in the paper. If that isn't so, we are happy to address this
there (though it seems a bit off the software issue). For HST
there is a signoff on updates by instrument teams, and there is
a committee responsible for the updates, but I don't think I would
go as far as to call it a CCB. As far as contemporaneous calibration
data, these are invariably associated with the proposal and thus
the calibration is done through associating the data with the science
data in the pipeline, and these files generally do not appear
in the CDRS (or the older CDBS). Pipelines are fed tables of the
files that belong in an association so that they know which file
to use for such a purpose.

The issue of tracability is handled by the fact that all data products
are tagged with the version of CRDS rules in their header
(the pipeline context) along with relevant software versions.
Given that, the exact same numbers should be extracted if the 
same context is given. That was one major goal of the system was 
to be able to replicate previous results (file recommendations
and otherwise), which the older system could not do. We have 
added a sentence assuring that this functionality is also repeatable
for the given context. E.g., one knows which rules file the value
was extracted from and that provides all the information one 
needs.

The comment about limiting the downloads needed for areas with
limited bandwidth is already a feature of the system. The client
library only downloads files that a pipeline invocation needs, and
these downloads will be cached for the event other datasets 
require them. No other files are automatically downloaded when it
is used in this manner. We have added a sentence to make that clear.

Section 2 comments
------------------

Paper section 3 item 1:
The main point being made was that one team may submit a change
to be tested (which could take a while), followed by another team
that has a  more urgent need for an update and tesing, yet must
await the previous test to complete. The teams operate asynchronously
so one test system isn't necessarily sufficient. But the criticism 
is a good one, and given this isn't a very important point in the
paper, we have shortened this issue to say essentially that the
test system didn't address all test needs.

page 6, substitutions.
The wording suggestions are indeed much better and have been 
made.

page 6, last paragraph
Again the suggested text is much better and has been used.

****** To do

1) box text file figures
2) improve screen shots

===================================================

Reviewer 2

### 2016-02-26 docs/paper/crds.tex
most of reviewer 1 changes, sans those for figures
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2239 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
-\usepackage{draftwatermark}
-\SetWatermarkText{DRAFT}
-\SetWatermarkScale{1}
-\lstset{
-  basicstyle=\ttfamily,
-  showstringspaces=false,
-  stringstyle=\color{red},
-  morecomment=[l]{/},
-  commentstyle=\color{blue},
-}
+%%\usepackage{draftwatermark}
+%%\SetWatermarkText{DRAFT}
+%%\SetWatermarkScale{1}
+%%\lstset{
+%%  basicstyle=\ttfamily,
+%%  showstringspaces=false,
+%%  stringstyle=\color{red},
+%%  morecomment=[l]{/},
+%%  commentstyle=\color{blue},
+%%}
 
@@
 instrument configuration for one observation, reference file keywords
-circumscribe range of parameter values for which the reference file applies.
+circumscribe a range of parameter values for which the reference file applies.
 In CDBS, ranges of parameter values were often represented by special values
@@
 to correct. In the last few years a test
-version of the database was created so that tests could be performed, but that
-introduces synchronization and management issues to make sure what is being
-tested corresponds to the previous operational version. Furthermore, if
-multiple deliveries are in progress from different instruments, it introduces a
-coordination issue to make sure they are either all completed together or in
-sequence, which can prove constraining to the needs of each instrument as far
-as testing goes.
+version of the database was created so that tests could be performed without
+affecting operations, yet it still didn't satisfy all testing needs.
 
@@
 resubmissions of already submitted files to correct for the effect of the wrong
-submission. One such example is if one mistakenly supplies a``wildcard'' for a
+submission. One such example is if one mistakenly supplies a ``wildcard'' for a
 parameter that should only apply to one case. In this event, all the other
@@
 Having the capability to analyze basic properties
-such duplicate or deleted rows,  by pseudo-mode, for supported tables files.
-\item Providing utilities for making CRDS useful in: operations; for instrument
-scientists that must generate and monitor reference files; and end users.
+such as duplicate or deleted rows,  by pseudo-mode, for supported tables files.
+\item Providing utilities for making CRDS useful for operations, instrument
+scientists that must generate and monitor reference files, and end users.
 \end{enumerate}
@@
 describes information about what kind of reference file that it is applied to,
-what the relevant information from the dataset is needed to make that
+what relevant information from the dataset is needed to make that
 selection, and other bookkeeping information. Following that header are the
@@
 \begin{description}
-\item[lists of allowable alternatives:] Allowable values for parameteters
+\item[Lists of Allowable Alternatives:] Allowable values for parameteters
 may be supplied as an \textquotesingle OR\textquotesingle
 {\tt }list using {\tt |} as a separator. For example:
-\texttt {({\ttfamily"}filter1{\ttfamily"}
-| {\ttfamily"}filter2{\ttfamily"},...)} will allow either value to match the first
+\texttt {({\ttfamily"}filter1|filter2{\ttfamily"},...)} will allow either value to match the first
 parameter.
-\item[Wild Cards:] Using an {\tt \*} in a string applies familiar wildcard 
+\item[Wild Cards:] Using an {\tt *} in a string applies familiar wildcard 
 matching rules to the supplied string. For example 
@@
 they result in the replacement of a string in a rules file with a different
-string. This is useful in the case the string is complex and must be entered
-in many different rules (e.g., it is a combination of many different 
-allowable values), or it is more mnemonic to those that must maintain
+string. This is useful in the case where the string is complex and must be 
+entered in many different rules (e.g., it is a combination of many different 
+allowable values), or where it is more mnemonic to those that must maintain
 the rules than the actual header values are.
@@
 match a given case. In order to allow effective defaults for general cases
-while allowing specific cases to override the general case, special rule
+while allowing specific cases to override the general case, special rules
 for disambiguation in these situations have been developed. The basic idea
-is that more specific matches take precedence over more general matches.
-For example, if one item lists as its matching value a wildcard, and another
-gives a specific value for the same parameter, the specific match takes
-precedence. The precedence is handled by determining the specificity of the
+is that. The precedence is handled by determining the specificity of the
 match. Use of specific values, wildcards, or regular expressions increase
@@
 This expects an ordered sequence of date/time values as part of the rules.
-This selector finds the greates date/time value that is less than or equal
+This selector finds the greatest date/time value that is less than or equal
 to the supplied date/time.
@@
 Full documentation of the syntax and semantics of all the rmap and
-context files is available on the web 
+context files is available on the web.
 \footnote{\url{https://jwst-crds.stsci.edu/static/users\_guide/rmap\_syntax.html\#selectors}}
@@
 
-The system is based on these files (which we refer to rmap files since they
+The system is based on these files (which we refer to as rmap files since they
 indicate the mapping to reference files) but also involves a hierarchy of
@@
 This hierarchy is designed to match that for JWST and as such is currently
-designed around the current levels of hierarchy. It is a possible generalization
-that would allow it to deal with arbitrary levels of heirarchy, perhaps
-different in number depending on the branch taken. Achieving that would
+designed around the current levels of hierarchy. A possible generalization
+of this scheme would allow arbitrary levels of heirarchy, perhaps
+different in number depending on the branch taken. Achieving this would
 take some modification of the bestref client functionality but is possible
@@
 One of the important goals for CRDS was to streamline the process of submitting
-new files while ensuring that files are well checked before committed, at least
-for common use cases for new Reference files. A completely manual approach is
+new files while ensuring that files are well checked before committed.
+A completely manual approach is
 outlined here before addressing more automatic schemes. For the time being, the
-details of how files are actually submitted is deferred to the next section
+details of how files are actually submitted is deferred to the next section.
 
 Supposing one or more new references files of a specific type for a specific
-instrument are ready to be tested and used in the operations system/:
+instrument are ready to be tested and used in the operations system:
 
@@
 \item Submit the updated rmap file (again with implied validation for
-correctness)
-and again, generating a new, unique rmap file name that represents the version
+correctness), generating a new, unique rmap file name that represents the version
 of the file in the system that has the desired changes.
 \item Edit the instrument context file to use the new version of the rmap file.
-\item Submit the updated instrument context file (with validation and 
+\item Submit the updated instrument context file (with validation,
 generating a new, unique name).
@@
 instrument context file.
-\item Submit the updated pipeline context file (with validation and 
-generating a new, unique name).
+\item Submit the updated pipeline context file with validation, 
+generating a new, unique name.
 \end{enumerate}
@@
 File submission is limited to authenticated users. The home page for
-authentic pages is shown in Figure~\ref{fig:authenticatedhome}.
+authenticated users is shown in Figure~\ref{fig:authenticatedhome}.
 The fully automatic
@@
 \includegraphics[width=180mm]{JWST_Failed_Submission_DM_schema_violation.png}
-\caption{JWST failed submission example}
+\caption{JWST failed submission example\newline\newline}
 \label{fig:failedsubmission}
@@
 
-The authenticated user begains a batch submission of files on the batch
+The authenticated user begins a batch submission of files on the batch
 submission page (Figure~\ref{fig:batchsubmission}) 
@@
 and CRDS will then validate each of the reference
-files. If they all pass validation, the user will be presented the results of
+files. If they all pass validation, the user will be presented
 the results that will be produced (e.g., the new filenames for the reference
@@
 process completes, the user is presented with a summary page, shown in
-Figure~\ref{fig:confirmedsubmission}
+Figure~\ref{fig:confirmedsubmission}.
 
@@
 
-This is handled by using the tools that the JWST pipeline use to validate the
+This is handled by using the tools that the JWST pipeline uses to validate the
 reference files. These are based on data models that use JSON Schema
@@
 The required metadata includes information on who made the reference file, how
-the reference file was made and related information (CRDS will also add
+the reference file was made, and related information. (CRDS will also add
 standard metadata related to the submission aspects, such as when the file was
@@
 
-There are further checks on file submissions that are intended to warn regarding
+There are further checks on file submissions that are intended to warn the submitter
+regarding
 suspicious changes. These changes may be valid, but likely indicate a mistake. The
@@
 existing reference file name replaced by one that is earlier in the submission
-sequence that would be unusual, and the submitter is warned about this reversion.
+sequence that would be unusual, the submitter is warned about this reversion.
 Likewise, if instrument or pipeline contexts point to earlier rmaps or instrument
@@
 can be used to determine which datasets must be reprocessed to take advantage
-of any improved reference files.
+of any improved reference files. This functionality is implemented as a server-side
+web service.
 
@@
 pipeline context. This indicates what files may be needed to process the
-data. (possibly useful for other classes of users)
+data. (This is possibly useful for other classes of users.)
 
@@
 
-\textbf{Inverse mapping:} Which rmaps and contexts use a specific reference file (e.g.,
-if one finds that one was defective, identify all the pipeline contexts that
-used that file so that users may be notified).
+\textbf{Inverse mapping:} Identify which rmaps and contexts
+use a specific reference file.
 
@@
 (though for the JWST pipelines, this isn't normally necessary). This typically
-will be run remotely and thus need network access to the CRDS server.
+will be run remotely and thus needs network access to the CRDS server.
 
@@
 pipeline would select a specific row in the table that matched an additional
-set of selection parameters. This could be greately simplified if the 
+set of selection parameters. This could be greatly simplified if the 
 rmap itself bypassed reference files entirely and effectively embedded
@@
 the calibration pipeline of the need for embedding its own matching 
-system in its code.
+system in its code. Given that the state of the rules is well defined
+by pipeline contexts, replicability of the returned values is ensured 
+when using the same pipeline context.
 
@@
 pipeline remotely and be assured that the right reference files will be used,
-and retrieved if necessary.
+and retrieved if necessary. Note that only files needed for the calibration
+of a particular dataset are retrieved. There is no need to download the whole
+set of reference files except in the extreme case that one is reprocessing all
+of the data in the archive.
 
@@
 for all datasets was repeated many times until CRDS went operational. This was
-further complicate by the fact that the database that contained the CDBS best
+further complicated by the fact that the database that contained the CDBS best
 references was not reliable. The differences that arose had to be further
@@
 than just for selecting appropriate reference files. It can act as a selector
-many uses so long as the number of selections is not enormous, and the set of
-selection parameter is reasonably consistent and bounded for all data
+for many uses as long as the number of selections is not enormous, and the set of
+selection parameters is reasonably consistent and bounded for all data
 sets. Other such uses are already envisioned for JWST. For example, it will be used

### 2016-02-27 docs/paper/response.txt
reviewer 2 minor comments
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2241 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
+Section 3 comments
+------------------
+
+Figures 1-6 have been boxed as requested (we do agree that this
+is a signficant improvement)
+
+Figures 7-12 xxxx
+
+Section 4 comments
+------------------
+
+These have all been fixed (we hope :-) We thank the reviewer for
+taking the time to detail these. After viewing the same or similar
+text repeatedly it is quite hard to look as closely as one would
+wish, so this is quite helpful.
+
 ****** To do
@@
 Reviewer 2
+
+Section 2
+We have reworded to be more explicit that all possible combinations of parameters
+must be represented as distinct rows.
+
+Section 3 point 2: "Could an 'is valid' boolean attribute in the database
+help out?"
+Not really. The file itself may be perfectly good, it is just associated with
+the wrong value of parameters. Possbily if coupled with a resubmission with the
+right values, but note that may mean many entries have to be so marked, and 
+replicated. But as implemented, it didn't have that option.
+
+Section 5: first sentence.
+Fixed.
+Section 5 submission typo
+Fixed
+Section 5 point 3
+todo****xxxx
+
+Section 6.3 paragraph 2
+reworded
+Section 6.3 par 4
+Made it clear that it is the version of the calibration pipeline that is 
+being referred to.
+Section 6.4.1 Relational Expressions typo
+Fixed
+Section 6.4.1 next to last par
+Joined two sentences properly.
+Section 6.5 par 3
+Fixed
+Section 7 par 2 punctuation
+Fixed
+Section 7.2 par 2 begains 
+Fixed

### 2016-02-27 docs/paper/crds.tex
boxed figures 1-6 as reviewer 1 requested
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2240 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3
reviewer 2 minor comments
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2241 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
+\usepackage{mdframed}
 %% The amssymb package provides various useful mathematical symbols
@@
 to match datasets to references, the number of distinct rows in the CDBS
-database was equal to the product of the number of specific values supported by
-a particular reference file for each parameter.
+database was equal to the number of all possible combinations of parameters.
 
@@
 The software for the Calibration Reference Data System (CRDS) 
-can be considered to be in one of three categories:
+can be considered to be in one of four categories:
 
@@
 \item Supporting the bestref functionality.
-\item Supporting the submittion of new reference files and all the issues that
+\item Supporting the submission of new reference files and all the issues that
 go with that.
@@
 
-The header permits attributes that allow specialized handling of the metadata 
-the dataset, including indicating when parameters are relevant or not (e.g., only 
+The header allows inclusion of attributes that enable specialized handling of the metadata 
+of the dataset, including indicating when parameters are relevant or not (e.g., only 
 care about its value if the value of another parameter is given as specified), 
@@
 \begin{figure*}
+\begin{mdframed}
 \begin{verbatim}
@@
 \end{verbatim}
+\end{mdframed}
 \caption{Example showing basic parameter matching rules coupled with date dependency.}
@@
 
-Figure~\ref{fig:example2} shows the use of the software selection mechanism (for brevity, the header is omitted in this and subsequent examples).
-In this case if the software version is less than 3.1 (using the typical version semantics) then the first file will be chosen, if less than 5 the second will be chosen, otherwise the last file will be used.
+Figure~\ref{fig:example2} shows the use of the software selection mechanism where a dependency is indicated for the version of the calibration pipeline (for brevity, the header is omitted in this and subsequent examples).
+In this case if the version of the calibration pipeline is less than 3.1 (using the typical version semantics) then the first file will be chosen, if less than 5 the second will be chosen, otherwise the last file will be used.
+
+\newpage
 
 \begin{figure*}
+\begin{mdframed}
 \begin{verbatim}
@@
 \end{verbatim}
+\end{mdframed}
 \caption{Example showing use of the software version selection mechanism.}
@@
 \end{verbatim}
+\end{mdframed}
 \caption{Example showing bracketing selection.}
@@
 \end{verbatim}
+\end{mdframed}
 \caption{An example showing matching specified ranges.}
@@
 special interpretation by CRDS, such as {\tt | and \*}.
-\item[Relational Expressions:] Relational expressions are braketed by {\tt \#}.
+\item[Relational Expressions:] Relational expressions are bracketed by {\tt \#}.
 These do numerical comparisons on the supplied parameter value to determine
@@
 for disambiguation in these situations have been developed. The basic idea
-is that. The precedence is handled by determining the specificity of the
+is that the precedence is handled by determining the specificity of the
 match. Use of specific values, wildcards, or regular expressions increase
@@
 \end{verbatim}
+\end{mdframed}
 \caption{An example of an instrument contex file (.imap)}
@@
 \end{verbatim}
+\end{mdframed}
 \caption{An example of a pipeline context file (.pmap)}
@@
 designed around the current levels of hierarchy. A possible generalization
-of this scheme would allow arbitrary levels of heirarchy, perhaps
+of this scheme would allow arbitrary levels of hierarchy, perhaps
 different in number depending on the branch taken. Achieving this would

### 2016-02-29 sources/interactive/versions.py
Rename pyasdf to asdf
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2242 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -12,23 +12,23 @@ MODULE_LIST = (
     'matplotlib',
     'numpy',
     # 'scipy',
-    
+
     'crds',
     'crds.server',
-    
+
     'pyodbc',
     'jsonrpc',
-    
+
     'astropy',
     'jwst_lib.models',
-    'pyasdf',
-    
+    'asdf',
+
     'parsley',
     'yaml'
     )
 
 def get_all_versions( mods = MODULE_LIST ):
-    """Return a dictionary of version dictionaries for all modules named 
+    """Return a dictionary of version dictionaries for all modules named
     in sequence `mods`.
     """
     # ... all the relevant python modules
@@ -57,7 +57,7 @@ def get_version(modname):
         mod = dynamic_import(modname)
     except ImportError:
         return { key:"missing" for key in ["str", "rev", "svnurl", "file"]}
-    
+
     # try all the "standard" ways for it to say a version number
     try:
         ans = mod.__version__

### 2016-02-29 sources/interactive/views.py

@@ -56,16 +56,16 @@ HERE = os.path.dirname(__file__) or "./"
 def check_value(value, pattern, msg):
     """Ensure that `value` satisifies the conditions implied by `pattern`,
     otherwise raise a FieldError containing `msg`.
-    
+
     If pattern is a function,  call it and trap for assertions, adjust value.
     If pattern is a list,  `value` must be in it.
     If pattern is a string, it is a regex which `value` must match.
-    
+
     Return `value` if it checks out OK.
     """
     value = str(value)
     if isinstance(pattern, type(check_value)):
-        try: 
+        try:
             return pattern(value)
         except AssertionError, exc:
             raise FieldError(format_html(msg + " : " + str(exc)))
@@ -210,7 +210,7 @@ def is_list_of_rmaps(text):
     return rmaps
 
 def is_match_tuple(tuple_str):
-    """Raise an AssertionError if `tuple_str` is does not literal eval to a 
+    """Raise an AssertionError if `tuple_str` is does not literal eval to a
     tuple.  Otherwise return the tuple.
     """
     try:
@@ -261,13 +261,13 @@ def get_rendering_dict(request, dict_=None, requires_pmaps=False):
 
     statuses = ["*"] + models.FILE_STATUS_MAP.keys()
     statuses.remove("uploaded")
-    
+
     locked = get_locked_instrument(request)
     locked = locked if locked else ""
-    
+
     rdict = {   # standard template variables
         "observatory" : models.OBSERVATORY,
-             
+
         "instrument" : "*",
         "instruments" : ["*"] + models.INSTRUMENTS,
 
@@ -286,7 +286,7 @@ def get_rendering_dict(request, dict_=None, requires_pmaps=False):
         "filename" : "*",
         "deliverer_user" : "*",
         "current_path" : request.get_full_path(),
-        
+
         "locked_instrument" : locked,
 
         "username" : str(request.user),
@@ -294,7 +294,7 @@ def get_rendering_dict(request, dict_=None, requires_pmaps=False):
         "auto_rename" : models.OBSERVATORY == "jwst",
         "server_usecase" :  sconfig.server_usecase.lower(),
     }
-    
+
     # echo escaped inputs.
     for key, value in request.GET.items():
         rdict[key] = safestring.mark_for_escaping(value)
@@ -310,7 +310,7 @@ def get_rendering_dict(request, dict_=None, requires_pmaps=False):
     if dict_ is not None:
[…]

### 2016-03-13 sources/urls.py
Removed Delete References page due to bug in selectors.py fixed in opus-2016.1/2 and jwst-build-6
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/branches/opus_2015.3-3@2247 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -57,8 +57,8 @@ urlpatterns = patterns('',
     
     (r'^upload/list/$', 'crds.server.interactive.views.upload_list', {}, 'upload-list'),
     (r'^upload/new/$', 'crds.server.interactive.views.upload_new', {}, 'upload-new'),
-    (r'^upload/delete/(?P<filename>{0})$'.format(FILE_RE_STR),
-     'crds.server.interactive.views.upload_delete', {}, 'upload-delete'),
+    # (r'^upload/delete/(?P<filename>{0})$'.format(FILE_RE_STR),
+    # 'crds.server.interactive.views.upload_delete', {}, 'upload-delete'),
               
     url(r'^batch_submit_references/$', 'crds.server.interactive.views.batch_submit_references'),
     url(r'^submit_confirm/$', 'crds.server.interactive.views.submit_confirm'),

### 2016-03-14 docs/paper/response.txt
updated all text except for pseudo-mode clarification
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2248 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
+General comment regarding databases and comparisions to other observatories.
+
+A section at the end has been added that briefly describes what Spitzer, 
+Chandra and Gemini use and notes some of the restrictions entailed in their
+approaches (Chandra's is most similar in approach but simpler).
+
+As far as the implications regarding databases go, we have not expanded on that.
+This is mainly because some issues are arguably self evident (distributing
+software that requires databases certainly does impose a significantly larger 
+burden on those installing and maintaining such a system; we doubt that is 
+controversial).
+
+We also think it is nearly self evident that SQL does not always represent 
+rules in a clear or easy to understand way (and many astronomers, the ones 
+that ultimately must provide those rules, are not experts in SQL, particularly
+complex SQL). We aren't saying it is impossible to use only SQL, just not 
+ideal. Indeed, Gemini's experience found it to be too constricting (as we did).
+Chandra doesn't use it at all, and it appears Spitzer's needs are not as complex.
+This is probably aided by the fact that they generally process the data in 
+large runs, i.e,. their updates are relatively infrequent as we understand 
+it.  Besides, they sometimes have special processing after the query (e.g., 
+interpolation between two reference files), so it isn't a pure database
+solution either. Accomodating new needs requires new software changes.
+To be fair, so does ours if a new kind of rule is required, but that
+is much less likely, and much more likely to be in adding a new module
+rather than changing existing code.
+
+As to the focus on STScI needs. It would be nice if we had the resources 
+to develop a system with a very broad reach and goals initially (well, perhaps,
+many very ambitious projects die for being too ambitious!). But with the
+reality of funding oversight, it's very difficult to do that. NASA gets 
+quite nervous when they see work being done that isn't specifically done
+for their mission. We do what we can to keep the project more broadly 
+useful within these constraints. That's even true when writing papers
+(i.e., can we justify spending much time doing a thorough survey of all
+systems out there?).
+
 Section 2
@@
 right values, but note that may mean many entries have to be so marked, and 
-replicated. But as implemented, it didn't have that option.
+replicated. But as implemented, it didn't have that option. If it had been 
+designed from the beginning to handle that, yes, it could have dealt with bad
+submissions that way.
 

### 2016-03-14 docs/paper/crds.tex
updated all text except for pseudo-mode clarification
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2248 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 %% \usepackage{epsfig}
-
-\usepackage{mdframed}
+\usepackage{float}
+\floatstyle{boxed} 
+\restylefloat{figure}
+%\usepackage{mdframed}
 %% The amssymb package provides various useful mathematical symbols
@@
 functionality of the Calibration Reference Data System is available under an
-Open Source license.
+Open Source license. CRDS is briefly constrasted with a selected 
+sampling of other similar systems used at other observatories.
 \end{abstract}
@@
 parameters could be difficult to undo. No reference file could be removed from
-the database for various reasons. In a number of cases, particularly if the
+the database for various reasons.
+(It is possible to address this easily by changing the schema;
+nevertheless, the existing design made 
+such a change difficult.)
+In a number of cases, particularly if the
 date that it was targeted for was incorrect, it could seriously corrupt the
@@
 how to handle cases where no match is found, and hooks to allow special preprocessing
-of parameter values. See the documentation for details on these cases.
+of parameter values. See the documentation for details on these 
+cases.
 \footnote{\url{https://jwst-crds.stsci.edu/static/users\_guide/rmap_syntax.html\#active-header-fields}}
@@
 
-\begin{figure*}
-\begin{mdframed}
+\begin{figure*}[ht!]
+%%\begin{mdframed}
 \begin{verbatim}
@@
     'observatory' : 'JWST',
-    'parkey' : (('META.INSTRUMENT.DETECTOR', 'META.EXPOSURE.READPATT', 'META.SUBARRAY.NAME'),),
+    'parkey' : (('META.INSTRUMENT.DETECTOR','META.EXPOSURE.READPATT',
+    'META.SUBARRAY.NAME'),),
     'sha1sum' : 'bd99f4960096de9ad39a9ce506d5ff985847c4a3',
@@
 \end{verbatim}
-\end{mdframed}
+%%\end{mdframed}
 \caption{Example showing basic parameter matching rules coupled with date dependency.}
@@
 \begin{figure*}
-\begin{mdframed}
+%\begin{mdframed}
 \begin{verbatim}
@@
 \end{verbatim}
-\end{mdframed}
+%\end{mdframed}
 \caption{Example showing use of the software version selection mechanism.}
@@
 \end{verbatim}
-\end{mdframed}
+%\end{mdframed}
 \caption{Example showing bracketing selection.}
@@
 \end{verbatim}
-\end{mdframed}
+%\end{mdframed}
 \caption{An example showing matching specified ranges.}
@@
 \end{verbatim}
-\end{mdframed}
+%\end{mdframed}
 \caption{An example of an instrument contex file (.imap)}
@@
 \end{verbatim}
-\end{mdframed}
+%\end{mdframed}
 \caption{An example of a pipeline context file (.pmap)}
@@
 
+\floatstyle{plain}
+\restylefloat{figure}
 \begin{figure*}[ht!]
@@
 
+\section{Comparison with Approaches Used at Selected Observatories}
+
+\subsection{Chandra}
+
+The approach Chandra uses is based on the CALDB approach developed by 
+HEASARC and used by most high-engergy missions 
+(\citealt{2006SPIE.6270E..1XG}). Despite
+the name, no database is involved. In fact, the approach is a simpler 
+version of what is described in this paper. Essentially, the rules for 
+selecting files is kept in index files that list all of the available 
+calibration reference files and the situations they should be used for. 
+It shares some of the advantages of our approach such as being able to 
+recreate past recommendations and being able to distribute the software, 
+though it isn’t as simple to set up.
+
+\subsection{Spitzer}
+
+Spitzer uses perhaps the purest database approach we are aware of, and 
+has been described in \citealt{2005ASPC..347..594L}. 
+While it does permit an easy undo of updates, 
+it is difficult to recreate past recommendations, and is not easy to 
+distribute and run elsewhere (besides, the code and the associate 
+database does not appear to be available to do so).
+The rules for selection of calibration reference 
+files are basically expressed as as SQL queries to the database.
+Special post query processing is sometimes done, such as generating
+a time-interpolated reference from two bracketing files.
+
+\subsection{Gemini}
+
+Gemini uses a hybrid approach, using a database to store much of the 
+information, but where much of the selection of calibration reference 
+files is performed by running Python code to generate the appropriate 
+SQL query to apply to the database (Paul Hirst, private communication). 
+The use of pure SQL queries did not capture all the needs of the 
+complex selection rules required; their hybrid approach allows arbitrarily
+complex rules to be constructed. It does not permit easy distribution of the 
+system though it does provide a web-based service to provide calibration 
+reference file selections to external users. The results rank multiple 
+possible files that may be used as to their applicability. It does try 
+to allow for multiple kinds of processing that may require different 
+versions of calibration files depending on the kind of processing used 
+(e.g., whether you have done an overscan subtraction will affect which 
+bias file you are given). As such, it isn’t easy to support multiple 
+versions of the rules (that requires multiple servers), nor can the 
+system be easily distributed or customized without a lot of expertise 
+(but it can be used remotely through the web, and there is consideration 
+being given to mechanisms to allow local customization to the web results). 
+Reversion is possible by using version control to reinstate the 
+appropriate Python modules, but has never been used in practice.
+
 \section{Acknowledgments}

### 2016-03-15 docs/paper/response.txt
updated all text except for pseudo-mode clarification
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2249 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 many very ambitious projects die for being too ambitious!). But with the
-reality of funding oversight, it's very difficult to do that. NASA gets 
+reality of funding oversight it's very difficult to do that. NASA gets 
 quite nervous when they see work being done that isn't specifically done
@@
 Section 5 point 3
-todo****xxxx
+This text has been made clearer by replacing pseudo-mode with more
+specific text.
 

### 2016-03-15 docs/paper/crds.tex
updated all text except for pseudo-mode clarification
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2249 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 Having the capability to analyze basic properties
-such as duplicate or deleted rows,  by pseudo-mode, for supported tables files.
+such as duplicate or deleted rows, as defined by critical row lookup parameters 
+for supported tables files.
 \item Providing utilities for making CRDS useful for operations, instrument
@@
 of values for those parameters. This is a very flexible selector, and 
-many options are provided for its use. (If only one parameteter is being,
+many options are provided for its use. (If only one parameter is being,
 matched, the tuple can be replaced by a simple string.)
@@
 \begin{description}
-\item[Lists of Allowable Alternatives:] Allowable values for parameteters
+\item[Lists of Allowable Alternatives:] Allowable values for parameters
 may be supplied as an \textquotesingle OR\textquotesingle
@@
 (e.g., whether you have done an overscan subtraction will affect which 
-bias file you are given). As such, it isn’t easy to support multiple 
+bias file you are given).
+
+As such, it isn’t easy to support multiple 
 versions of the rules (that requires multiple servers), nor can the 
@@
 being given to mechanisms to allow local customization to the web results). 
-Reversion is possible by using version control to reinstate the 
-appropriate Python modules, but has never been used in practice.
+Reversion may be possible by using version control to reinstate the 
+appropriate Python modules, but has never been used in practice; 
+for the results to be replicated accurately requires that none of the
+information in the database for files present at that time of the previous
+results has been changed since that time.
 

### 2016-03-16 docs/paper/response.txt
last version, I hope
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2250 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
-As to the focus on STScI needs. It would be nice if we had the resources 
+It really isn't our intent to argue that databases are not appropriate; rather 
+for the features we sought, that they did not appear to be the simplest
+solution. In things like this, proving it beyond any question is not
+something that projects have the resources to do. Indeed, practically 
+speaking, there never is proof, only indications by the absense of
+solutions using them. The only proof possible is proving that they
+are suitable by implementing a system that has the features we sought
+using a database. Doing that really is for someone else to do. We can 
+only note that we haven't found one in existance yet.
+
+As to the focus on STScI needs. We don't agree that only one page
+is devoted to generic needs. We would argue that the great majority
+of the discussion is directed to generic capabilities, with occasional
+references to how they relate to JWST or HST. Yes, the examples are for
+STScI systems, but it would be odd for us to use examples for other
+observatories for which we are not qualified to provide. We don't 
+believe that these examples in any way limit the generic aspects of
+the system.
+
+But even if it were the case it wasn't sufficiently generic enough, it's
+a question of having enough resources 
 to develop a system with a very broad reach and goals initially (well, perhaps,
@@
 for their mission. We do what we can to keep the project more broadly 
-useful within these constraints. That's even true when writing papers
-(i.e., can we justify spending much time doing a thorough survey of all
-systems out there?).
+useful within these constraints, and we think we have done as much as
+possibly can be expected along those lines. That's even true when writing
+papers (i.e., can we justify spending much time doing a thorough survey 
+of all systems out there?).
 

### 2016-03-16 docs/paper/crds.tex
last version, I hope
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2250 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 
+\hyphenation{bestref}
+
 %%\usepackage{draftwatermark}
@@
 functionality of the Calibration Reference Data System is available under an
-Open Source license. CRDS is briefly constrasted with a selected 
+Open Source license. CRDS is briefly constrasted with a 
 sampling of other similar systems used at other observatories.
@@
 In this case if the version of the calibration pipeline is less than 3.1 (using the typical version semantics) then the first file will be chosen, if less than 5 the second will be chosen, otherwise the last file will be used.
-
-\newpage
 
@@
 recreate past recommendations and being able to distribute the software, 
-though it isn’t as simple to set up.
+though it is not as simple to set up.
 
@@
 files are basically expressed as as SQL queries to the database.
-Special post query processing is sometimes done, such as generating
+Special post-query processing is sometimes done, such as generating
 a time-interpolated reference from two bracketing files.
@@
 
-As such, it isn’t easy to support multiple 
+As such, it is not easy to support multiple 
 versions of the rules (that requires multiple servers), nor can the 

### 2016-03-16 docs/paper/response.txt
minor update to response
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2251 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@
 is devoted to generic needs. We would argue that the great majority
-of the discussion is directed to generic capabilities, with occasional
+of the discussion is directed to generic capabilities, particularly
+with regard to the bestref core functionality, with occasional
 references to how they relate to JWST or HST. Yes, the examples are for

### 2016-03-16 sources/urls.py
Bugfix:  removed wrong "delete" URL,  file upload delete vs. delete references.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/branches/opus_2015.3-3@2252 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -57,13 +57,13 @@ urlpatterns = patterns('',
     
     (r'^upload/list/$', 'crds.server.interactive.views.upload_list', {}, 'upload-list'),
     (r'^upload/new/$', 'crds.server.interactive.views.upload_new', {}, 'upload-new'),
-    # (r'^upload/delete/(?P<filename>{0})$'.format(FILE_RE_STR),
-    # 'crds.server.interactive.views.upload_delete', {}, 'upload-delete'),
+    (r'^upload/delete/(?P<filename>{0})$'.format(FILE_RE_STR),
+     'crds.server.interactive.views.upload_delete', {}, 'upload-delete'),
               
     url(r'^batch_submit_references/$', 'crds.server.interactive.views.batch_submit_references'),
     url(r'^submit_confirm/$', 'crds.server.interactive.views.submit_confirm'),
 
-    url(r'^delete/reference/$', 'crds.server.interactive.views.delete_references'),
+    # url(r'^delete/reference/$', 'crds.server.interactive.views.delete_references'),
     url(r'^add_existing/reference/$', 'crds.server.interactive.views.add_existing_references'),
             
     url(r'^browse/(?P<filename>{0})$'.format(FILE_RE_STR), 

### 2016-03-20 sources/interactive/models.py
work on USEAFTER and HISTORY models repair and display
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2257 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -772,6 +772,8 @@ class FileBlobRepairMixin(object):
         "creator_name" : lambda self: not self.creator_name,
         "mapping_name_field": lambda self: rmap.is_mapping(self.name) and not self.name == rmap.fetch_mapping(self.name).name,
         "history" :  lambda self : self.type.lower() == "reference" and self.history in ["none","NONE","None", None],
+        # "history" :  lambda self : self.type.lower() == "reference",
+        "useafter_date" : lambda self: self.useafter_date in [self.delivery_date, DEFAULT_ACTIVATION_DATE] and self.type != "mapping"
     }
     
     def get_defects(self, verify_checksum=False, fields=None):
@@ -922,7 +924,6 @@ class FileBlobRepairMixin(object):
                 self.useafter_date = timestamp.parse_date(info["useafter_date"])
 
         bad_field_checks["aperture"] = lambda self: self.aperture=="none" and self.type != "mapping" and self.instrument != "wfpc2"
-        bad_field_checks["useafter_date"] = lambda self: self.useafter_date in [self.delivery_date, DEFAULT_ACTIVATION_DATE] and self.type != "mapping"
 
     elif OBSERVATORY == "jwst":  #===========================================================
 
@@ -933,6 +934,17 @@ class FileBlobRepairMixin(object):
                 if self.name in names:
                     self.activation_date = hist.start_date
                     break
+            return
+
+        def repair_useafter_date(self):
+            if self.type == "mapping":
+                return
+            name = self.name
+            with log.error_on_exception("Failed repairing JWST useafter date for", repr(name)):
+                header = data_file.getval("USEAFTER")
+                self.useafter_date = timestamp.parse_date(header["USEAFTER"])
+                return
+            self.useafter_date = timestamp.parse_date(DEFAULT_USEAFTER_DATE)
             return
 
 # ============================================================================
@@ -962,6 +974,7 @@ assert len(ALL_STATES) == len(set(ALL_STATES)), "Doubly-assigned or duplicate st
 assert len(FILE_STATES) >= len(ALL_STATES),  "Uncategorized state in FileBlob state declarations."
 
 DEFAULT_ACTIVATION_DATE =  datetime.datetime(2050, 1, 1, 0, 0)
+DEFAULT_USEAFTER_DATE = datetime.datetime(1900, 1, 1, 0, 0)
 START_OF_CRDS = datetime.datetime(2013, 8, 1, 0, 0)
 
[…]

### 2016-03-20 sources/interactive/views.py
Added fallback to get_fits_header_union for data model header failures.  This should probably be redesigned as a "primitive header fetch" OR by using the CRDS env var hooks ignoring data model errors with warnings.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2258 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -1751,6 +1751,9 @@ def browsify_header(filename, browsed_file):
     header2 = {}
     with log.error_on_exception("Failed getting extra keys for", repr(browsed_file)):
         header2 = data_file.get_unconditioned_header(browsed_file, needed_keys=["APERTURE","USEAFTER"])
+    if not header:
+        with log.error_on_exception("Fallback to FITS header union failed."):
+            header = data_file.get_fits_header_union(browsed_file)
     if header:
         header.update(header2)
         output  = "<b>Header Parameters</b>\n"

### 2016-03-20 sources/interactive/models.py
More work on repair_useafter,  incomplete.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2259 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@ -773,7 +773,7 @@ class FileBlobRepairMixin(object):
         "mapping_name_field": lambda self: rmap.is_mapping(self.name) and not self.name == rmap.fetch_mapping(self.name).name,
         "history" :  lambda self : self.type.lower() == "reference" and self.history in ["none","NONE","None", None],
         # "history" :  lambda self : self.type.lower() == "reference",
-        "useafter_date" : lambda self: self.useafter_date in [self.delivery_date, DEFAULT_ACTIVATION_DATE] and self.type != "mapping"
+        "useafter_date" : lambda self: self.useafter_date_str == str(DEFAULT_ACTIVATION_DATE).split(".")[0] and self.type != "mapping"
     }
     
     def get_defects(self, verify_checksum=False, fields=None):
@@ -873,7 +873,12 @@ class FileBlobRepairMixin(object):
         self.set_fits_field("aperture", self.aperture_keyword)  # aperture_keyword from FileBlobModel multiple inheritance
         
     def repair_useafter_date(self):
-        self.set_fits_field("useafter_date", "USEAFTER", timestamp.parse_date)
+        with log.error_on_exception("Failed setting USEAFTER from FITS"):
+            self.set_fits_field("useafter_date", "USEAFTER", timestamp.parse_date)
+            self.save()
+            return
+        self.useafter_date = DEFAULT_USEAFTER_DATE
+        self.save()
 
     def repair_reference_file_type(self):
         self.set_fits_field("reference_file_type", "REFTYPE")
@@ -934,17 +939,6 @@ class FileBlobRepairMixin(object):
                 if self.name in names:
                     self.activation_date = hist.start_date
                     break
-            return
-
-        def repair_useafter_date(self):
-            if self.type == "mapping":
-                return
-            name = self.name
-            with log.error_on_exception("Failed repairing JWST useafter date for", repr(name)):
-                header = data_file.getval("USEAFTER")
-                self.useafter_date = timestamp.parse_date(header["USEAFTER"])
-                return
-            self.useafter_date = timestamp.parse_date(DEFAULT_USEAFTER_DATE)
             return
 
 # ============================================================================
@@ -1185,7 +1179,7 @@ class FileBlob(BlobModel, FileBlobRepairMixin):
         try:
             setattr(self, model_field, sanitizer(value))
         except Exception as exc:
-            log.error("Setting field '%s' for '%s' failed: '%s'" % (model_field, filename, exc))
[…]
